### 2021-12-07 paper/interactnlmsample.tex
added LRA benchmark

% interactnlmsample.tex
% v1.05 - August 2017

\documentclass[]{interact}

\usepackage{epstopdf}% To incorporate .eps illustrations using PDFLaTeX, etc.
\usepackage[caption=false]{subfig}% Support for small, `sub' figures and tables
%\usepackage[nolists,tablesfirst]{endfloat}% To `separate' figures and tables from text if required
%\usepackage[doublespacing]{setspace}% To produce a `double spaced' document if required
%\setlength\parindent{24pt}% To increase paragraph indentation when line spacing is doubled

\usepackage{algorithm,algorithmic}
\usepackage{hyperref}
\usepackage{mathtools}
\usepackage{amssymb}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{tikz}
\usepackage{multirow}
\usepackage{booktabs,tabularx}

\usepackage[numbers,sort&compress]{natbib}% Citation support using natbib.sty
\bibpunct[, ]{[}{]}{,}{n}{,}{,}% Citation support using natbib.sty
\renewcommand\bibfont{\fontsize{10}{12}\selectfont}% Bibliography support using natbib.sty
\makeatletter% @ becomes a letter
\def\NAT@def@citea{\def\@citea{\NAT@separator}}% Suppress spaces between citations using natbib.sty
\makeatother% @ becomes a symbol again

\theoremstyle{plain}% Theorem-like structures provided by amsthm.sty
\newtheorem{theorem}{Theorem}[section]
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{proposition}[theorem]{Proposition}

\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{example}[theorem]{Example}

\theoremstyle{remark}
\newtheorem{remark}{Remark}
\newtheorem{notation}{Notation}

\begin{document}

\articletype{ARTICLE TEMPLATE}% Specify the article type or omit as appropriate

\title{Taylor \& Francis \LaTeX\ template for authors (\textsf{Interact} layout + NLM reference style)}

\author{
\name{A.~N. Author\textsuperscript{a}\thanks{CONTACT A.~N. Author. Email: latex.helpdesk@tandf.co.uk} and John Smith\textsuperscript{b}}
\affil{\textsuperscript{a}Taylor \& Francis, 4 Park Square, Milton Park, Abingdon, UK; \textsuperscript{b}Institut f\"{u}r Informatik, Albert-Ludwigs-Universit\"{a}t, Freiburg, Germany}
}

\maketitle

\begin{abstract}
This template is for authors who are preparing a manuscript for a Taylor \& Francis journal using the \LaTeX\ document preparation system and the \texttt{interact} class file, which is available via selected journals' home pages on the Taylor \& Francis website.
\end{abstract}

\begin{keywords}
Sections; lists; figures; tables; mathematics; fonts; references; appendices
\end{keywords}

\section{Introduction}

In order to assist authors in the process of preparing a manuscript for a journal, the Taylor \& Francis `\textsf{Interact}' layout style has been implemented as a \LaTeXe\ class file based on the \texttt{article} document class. A \textsc{Bib}\TeX\ bibliography style file and a sample bibliography are also provided in order to assist with the formatting of your references.

Commands that differ from or are provided in addition to standard \LaTeXe\ are described in this document, which is \emph{not} a substitute for a \LaTeXe\ tutorial.

The \texttt{interactnlmsample.tex} file can be used as a template for a manuscript by cutting, pasting, inserting and deleting text as appropriate, using the preamble and the \LaTeX\ environments provided (e.g.\ \verb"\begin{abstract}", \verb"\begin{keywords}").

\subsection{The \textsf{Interact} class file}\label{class}

The \texttt{interact} class file preserves the standard \LaTeXe\ interface such that any document that can be produced using \texttt{article.cls} can also be produced with minimal alteration using the \texttt{interact} class file as described in this document.

If your article is accepted for publication it will be typeset as the journal requires in Minion Pro and/or Myriad Pro. Since most authors will not have these fonts installed, the page make-up is liable to alter slightly with the change of font. Also, the \texttt{interact} class file produces only single-column format, which is preferred for peer review and will be converted to two-column format by the typesetter if necessary during preparation of the proofs. Please therefore do not try to match the typeset format exactly, but use the standard \LaTeX\ fonts instead and ignore details such as slightly long lines of text or figures/tables not appearing in exact synchronization with their citations in the text: these details will be dealt with by the typesetter. Similarly, it is unnecessary to spend time addressing warnings in the log file -- if your .tex file compiles to produce a PDF document that correctly shows how you wish your paper to appear, such warnings will not prevent your source files being imported into the typesetter's program.

\subsection{Submission of manuscripts prepared using \emph{\LaTeX}}

Manuscripts for possible publication should be submitted to the Editors for review as directed in the journal's Instructions for Authors, and in accordance with any technical instructions provided in the journal's ScholarOne Manuscripts or Editorial Manager site. Your \LaTeX\ source file(s), the class file and any graphics files will be required in addition to the final PDF version when final, revised versions of accepted manuscripts are submitted.

Please ensure that any author-defined macros used in your article are gathered together in the preamble of your .tex file, i.e.\ before the \verb"\begin{document}" command. Note that if serious problems are encountered in the coding of a document (missing author-defined macros, for example), the typesetter may resort to rekeying it.

\section{Benchmark Desription}
The LRA benchmark employs two energy groups and two delayed precursors and represents a 2-D quarter-core, BWR model subject to a control-rod ejection with adiabatic heating \cite{anl}.
Schematic layout of the problem is shown in Fig.~\ref{fig:lra core}, where region numbers indicate different materials and region R is the ejected rod.
%To produce time-dependent snapshots, the deterministic transport code Detran\footnote{https://github.com/robertsj/libdetran} was used to solve the time-dependent diffusion equations.
\begin{figure}[h!]
	\centering
	\begin{tikzpicture}[scale=0.6]	
	\begin{scope}<->;

	% GRID
	\draw[step=1.5cm,gray,very thin, dashed,opacity=0.4] (0, 0) grid (16.5,16.5);

	% AXES
	\draw[black, thick, ->] (0, 0) -- (17,  0) node[right] {$x$ (cm)};
	\draw[black, thick, ->] (0, 0) -- ( 0, 17) node[above] {$y$ (cm)};

	% Material 1 regions

	\node[font=\large] at (5.25, 5.25) {1};

	% Material 2 regions
	\draw[black, thick] (0, 1.5) -- (1.5, 1.5);
	\draw[black, thick] (1.5, 0) -- (1.5, 1.5);
	\node[font=\large] at (0.75, 0.75) {2};

	\draw[black, thick] ( 7.5, 0.0) -- ( 7.5, 1.5);
	\draw[black, thick] (10.5, 0.0) -- (10.5, 1.5);
	\draw[black, thick] ( 7.5, 1.5) -- (10.5, 1.5);
	\node[font=\large] at (9.0, 0.75) {2};

	\draw[black, thick] ( 0.0,  7.5) -- ( 1.5,  7.5);
	\draw[black, thick] ( 0.0, 10.5) -- ( 1.5, 10.5);
	\draw[black, thick] ( 1.5,  7.5) -- ( 1.5, 10.5);
	\node[font=\large] at ( 0.75, 9.0) {2};

	\draw[black, thick] ( 7.5,  7.5) -- ( 7.5, 10.5);
	\draw[black, thick] ( 7.5,  7.5) -- (10.5,  7.5);
	\draw[black, thick] (10.5, 10.5) -- ( 7.5, 10.5);
	\draw[black, thick] (10.5, 10.5) -- (10.5,  7.5);
	\node[font=\large] at ( 9.0, 9.0) {2};

	% Material 3 regions
	\draw[black, thick] (10.5,  0.0) -- (10.5, 10.5) -- (13.5, 10.5) --  (13.5,  0.0) -- (10.5,  0.0);
	\node[font=\large] at ( 12.0, 3.75) {3}; 
	\draw[black, thick] (0.0, 10.5) -- (10.5, 10.5) -- (10.5, 13.5) -- (0.0, 13.5) --  (0.0, 10.5);
	\node[font=\large] at ( 3.75, 12.0) {3};

	% Material 4 regions  
	\draw[black, thick] ( 12,  12) -- ( 12, 10.5) -- (10.5, 10.5) -- (10.5,  12) -- ( 12,  12);
	\node[font=\large] at ( 11.25,11.25) {4};

	% Material 5 regions
	\draw[black, thick] ( 16.5,  0.0) -- (16.5, 16.5);
	\draw[black, thick] (  0.0, 16.5) -- (16.5, 16.5);
	\node[font=\large] at (15.0, 15.0) {5};

	% Perturbed regions
	\def\eps{0.125}
	\draw[black, thick, dashed] (10.5+\eps, 7.5+\eps) -- (10.5+\eps, 10.5-\eps) -- (13.5-\eps, 10.5-\eps) -- (13.5-\eps, 7.5+\eps) --  (10.5+\eps, 7.5+\eps);

	\node[font=\large] at (12,9) {R};

	% ticks
	\foreach \x/\xtext in {15, 75, 105, 135, 165}
	\draw[black,xshift=0.1*\x cm] (0,.3) -- (0,0) node[below, font=\large] {$\xtext$};
	\foreach \y/\ytext in {15, 75, 105, 135, 165}
	\draw[black,yshift=0.1*\y cm] (.3,0) -- (0,0) node[left, font=\large] {$\ytext$};
	\end{scope}
	\end{tikzpicture}
	\caption{Schematic of LRA benchmark.}
	\label{fig:lra core}
\end{figure}
The transient is initiated by a control rod ejection with constant velocity over a period of 2 seconds leading to a super-critical prompt transient, in which the power increased by about 10 orders of magnitude in a very short time.
The control rod movement was simulated by changing the thermal absorption cross section of the control rod material.
\begin{equation}
\sigma 
\end{equation}

Thermal feedback is incorporated through adiabatic fuel heat-up defined by
\begin{equation}
\frac{\partial}{\partial t}T(x,t) = \alpha[\Sigma_{f1}(x,t)\phi_1(x,t)+\Sigma_{f2}(x,t)\phi_2(x,t)] \, ,
\label{eq:heatup}
\end{equation}
and corresponding Doppler feedback defined by
\begin{equation}
\Sigma_{a1}(x,t) = \Sigma_{a1}(x,t=0)[1+\gamma(\sqrt{(T(x,t)}-\sqrt{(T_0)})] \, ,
\label{eq:doppler}
\end{equation}
where $\Sigma_{f_i}$ is the fission cross section of group $i$, $T$ is the temperature,  $\Sigma_{a1}$ is the fast absorption cross section and  $T_0$ is the initial temperature which is $300 $ K,
$\alpha = 3.83\times 10^{-11}~\text{K}.\text{cm}^3$ and $\gamma = 3.034\times 10^{-3} ~\text{K}^{-0.5}$.\\
The power is computed as
\begin{equation}
P(x,t)=\kappa [\Sigma_{f1}(x,t)\phi_1(x,t)+\Sigma_{f2}(x,t)\phi_2(x,t)] \, ,
\end{equation}
where $\kappa = 3.204\times 10^{-11}~ \text{Ws/fission}$.
The model was implemented in the deterministic transport code Detran~\cite{roberts2014advanced}.  
A mesh-centered, finite-volume discretization was used for the spatial dicretization, while a first-order, backward-difference temporal discretization was used with a fixed 0.001 s step size.  
The initial condition for the transient was computed by solving the steady-state equation, for which the $k_{\text{eff}}$ was found to be 0.9975.
Note that at each time step the fast absorption cross section is a function of the solution itself, hence a fixed point non-linear iteration is employed.
A convergence criteria is used such that the $\text{L}_2$ norm  of the relative flux error between two consecutive iterations is less than $1\times 10^{-6}$,

\begin{equation}
\|\frac{\mathbf{\Phi}^{i+1} - \mathbf{\Phi}^{i}} {\mathbf{\Phi}^i}\| \le  1\times 10^{-6} \, , 
\end{equation}
where the superscript $i$ denotes the iteration number.
The transient was calculated for 3.0 seconds.
Figure~\ref{fig:lra fom power} shows the reference full-order model power along with the core average temperature, while Figure \ref{fig:lra ss flux} shows the steady state group flux distribution.
This reference solution is not numerically converged in either the space or the time but it represents the simulation response that one wish to approximate.
\begin{figure}[h!]
	\includegraphics[width=1.0\linewidth]{../figures/LRA_fom_power_temperature.pdf}
	\caption{LRA core power}
	\label{fig:lra fom power}
\end{figure}

\begin{figure}[H]
	\centering
	\begin{subfigure}[b]{0.7\textwidth}
		\includegraphics[width=1.0\linewidth]{../figures/ss_fom_fast_flux_image.pdf}
		\caption{Steady state fast flux.}
		\label{fig:ss fast flux}
	\end{subfigure}
	\begin{subfigure}[b]{0.7\textwidth}
		\includegraphics[width=1.0\linewidth]{../figures/ss_fom_thermal_flux_image.pdf}
		\caption{Steady state thermal flux.}
		\label{fig:ss thermal flux}
	\end{subfigure}
	\caption{Steady state group flux $(\text{neutrons}.\text{cm}^2/s)$}
	\label{fig:lra ss flux}
\end{figure}

\begin{table}[h!]
	\centering
	\begin{tabular}{l|l|l|l| l|l}
		material & group  & $D$ (cm) & $\Sigma_{a} ~ (\text{cm}^{-1})$ & $\Sigma_{s2\gets 1}~ (\text{cm}^{-1})$ & $\nu\Sigma_{f}~ (\text{cm}^{-1})$ \\\hline
		\multirow{2}{*}{1}& 1   & 1.255  &  0.008252   &  \multirow{2}{*}{0.02533} & 0.004602 \\	
		& 2   & 0.211  &  0.1003     &           & 0.1091  \\
		\hline

		\multirow{2}{*}{2}& 1   & 1.268  &  0.007181    & \multirow{2}{*}{0.02767} & 0.004609 \\	
		& 2   & 0.1902 &  0.07047     &           &  0.08675\\
		\hline

		\multirow{2}{*}{3}& 1   & 1.259  &  0.008002    & \multirow{2}{*}{0.02617}     & 0.004663 \\	
		& 2   & 0.2091 &  0.08344     &    &    0.1021 \\
		\hline
		\multirow{2}{*}{4}& 1   & 1.259  &  0.008002    & \multirow{2}{*}{0.02617}  &  0.004663 \\	
		& 2   & 0.2091 &  0.073324    &           &  0.1021   \\
		\hline
		\multirow{2}{*}{5}& 1   & 1.257  &  0.0006034   &  \multirow{2}{*}{0.04754}  & 0.0 \\	
		& 2   & 0.1592 &   0.01911    &        & 0.0 \\
		\hline
	\end{tabular}
	{\raggedright $v_1 = 3\times10^{7} ~\text{cm/sec}. $,  $v_2 = ~3\times10^{5} \text{cm.sec}.$  \par}
	\caption{Two-group diffusion constants}
	\label{tab:twogroup}
\end{table}

\begin{table}[h!]
	\centering
	\begin{tabular}{c|l|l}
		group & $\beta_i$  & $\lambda_i$ ($s^{-1}$)  \\
		\hline
		1    &  0.0054 & 0.00654 \\
		2    &  0.001087 & 1.35  \\
		\hline
	\end{tabular}
	\caption{Delayed neutron data.}
	\label{tab:precursor data}
\end{table}

\section{Using the \texttt{interact} class file}

For convenience, simply copy the \texttt{interact.cls} file into the same directory as your manuscript files (you do not need to install it in your \TeX\ distribution). In order to use the \texttt{interact} document class, replace the command \verb"\documentclass{article}" at the beginning of your document with the command \verb"\documentclass{interact}".

The following document-class options should \emph{not} be used with the \texttt{interact} class file:
\begin{itemize}
  \item \texttt{10pt}, \texttt{11pt}, \texttt{12pt} -- unavailable;
  \item \texttt{oneside}, \texttt{twoside} -- not necessary, \texttt{oneside} is the default;
  \item \texttt{leqno}, \texttt{titlepage} -- should not be used;
  \item \texttt{twocolumn} -- should not be used (see Subsection~\ref{class});
  \item \texttt{onecolumn} -- not necessary as it is the default style.
\end{itemize}
To prepare a manuscript for a journal that is printed in A4 (two column) format, use the \verb"largeformat" document-class option provided by \texttt{interact.cls}; otherwise the class file produces pages sized for B5 (single column) format by default. The \texttt{geometry} package should not be used to make any further adjustments to the page dimensions.

%If your manuscript has supplementary content you can also use the \verb"interact" class file to prepare all or part of it using the \verb"suppldata" document-class option, which will suppress the `article history' date. This option \emph{must not} be used on any primary content. Note that authors are solely responsible for the preparation of all supplemental material.

\section{Additional features of the \texttt{interact} class file}

\subsection{Title, authors' names and affiliations, abstracts and article types}

The title should be generated at the beginning of your article using the \verb"\maketitle" command.
In the final version the author name(s) and affiliation(s) must be followed immediately by \verb"\maketitle" as shown below in order for them to be displayed in your PDF document.
To prepare an anonymous version for double-blind peer review, you can put the \verb"\maketitle" between the \verb"\title" and the \verb"\author" in order to hide the author name(s) and affiliation(s) temporarily.
Next you should include the abstract if your article has one, enclosed within an \texttt{abstract} environment.
The \verb"\articletype" command is also provided as an \emph{optional} element which should \emph{only} be included if your article actually needs it.
For example, the titles for this document begin as follows:
\begin{verbatim}
\articletype{ARTICLE TEMPLATE}

\title{Taylor \& Francis \LaTeX\ template for authors (\textsf{Interact}
layout + NLM reference style)}

\author{
\name{A.~N. Author\textsuperscript{a}\thanks{CONTACT A.~N. Author.
Email: latex.helpdesk@tandf.co.uk} and John Smith\textsuperscript{b}}
\affil{\textsuperscript{a}Taylor \& Francis, 4 Park Square, Milton
Park, Abingdon, UK; \textsuperscript{b}Institut f\"{u}r Informatik,
Albert-Ludwigs-Universit\"{a}t, Freiburg, Germany} }

\maketitle

\begin{abstract}
This template is for authors who are preparing a manuscript for a
Taylor \& Francis journal using the \LaTeX\ document preparation system
and the \texttt{interact} class file, which is available via selected
journals' home pages on the Taylor \& Francis website.
\end{abstract}
\end{verbatim}

An additional abstract in another language (preceded by a translation of the article title) may be included within the \verb"abstract" environment if required.

A graphical abstract may also be included if required. Within the \verb"abstract" environment you can include the code
\begin{verbatim}
\\\resizebox{25pc}{!}{\includegraphics{abstract.eps}}
\end{verbatim}
where the graphical abstract is to appear, where \verb"abstract.eps" is the name of the file containing the graphic (note that \verb"25pc" is the recommended maximum width, expressed in pica, for the graphical abstract in your manuscript).

\subsection{Abbreviations}

A list of abbreviations may be included if required, enclosed within an \texttt{abbreviations} environment, i.e.\ \verb"\begin{abbreviations}"\ldots\verb"\end{abbreviations}", immediately following the \verb"abstract" environment.

\subsection{Keywords}

A list of keywords may be included if required, enclosed within a \texttt{keywords} environment, i.e.\ \verb"\begin{keywords}"\ldots\verb"\end{keywords}". Additional keywords in other languages (preceded by a translation of the word `keywords') may also be included within the \verb"keywords" environment if required.

\subsection{Subject classification codes}

AMS, JEL or PACS classification codes may be included if required. The \texttt{interact} class file provides an \texttt{amscode} environment, i.e.\ \verb"\begin{amscode}"\ldots\verb"\end{amscode}", a \texttt{jelcode} environment, i.e.\ \verb"\begin{jelcode}"\ldots\verb"\end{jelcode}", and a \texttt{pacscode} environment, i.e.\ \verb"\begin{pacscode}"\ldots\verb"\end{pacscode}" to assist with this.

\subsection{Additional footnotes to the title or authors' names}

The \verb"\thanks" command may be used to create additional footnotes to the title or authors' names if required. Footnote symbols for this purpose should be used in the order
$^\ast$~(coded as \verb"$^\ast$"), $\dagger$~(\verb"$\dagger$"), $\ddagger$~(\verb"$\ddagger$"), $\S$~(\verb"$\S$"), $\P$~(\verb"$\P$"), $\|$~(\verb"$\|$"),
$\dagger\dagger$~(\verb"$\dagger\dagger$"), $\ddagger\ddagger$~(\verb"$\ddagger\ddagger$"), $\S\S$~(\verb"$\S\S$"), $\P\P$~(\verb"$\P\P$").

Note that any \verb"footnote"s to the main text will automatically be assigned the superscript symbols 1, 2, 3, etc. by the class file.\footnote{If preferred, the \texttt{endnotes} package may be used to set the notes at the end of your text, before the bibliography. The symbols will be changed to match the style of the journal if necessary by the typesetter.}

\section{Some guidelines for using the standard features of \LaTeX}

\subsection{Sections}

The \textsf{Interact} layout style allows for five levels of section heading, all of which are provided in the \texttt{interact} class file using the standard \LaTeX\ commands \verb"\section", \verb"\subsection", \verb"\subsubsection", \verb"\paragraph" and \verb"\subparagraph". Numbering will be automatically generated for all these headings by default.

\subsection{Lists}

Numbered lists are produced using the \texttt{enumerate} environment, which will number each list item with arabic numerals by default. For example,
\begin{enumerate}
  \item first item
  \item second item
  \item third item
\end{enumerate}
was produced by
\begin{verbatim}
\begin{enumerate}
  \item first item
  \item second item
  \item third item
\end{enumerate}
\end{verbatim}
Alternative numbering styles can be achieved by inserting an optional argument in square brackets to each \verb"item", e.g.\ \verb"\item[(i)] first item"\, to create a list numbered with roman numerals at level one.

Bulleted lists are produced using the \texttt{itemize} environment. For example,
\begin{itemize}
  \item First bulleted item
  \item Second bulleted item
  \item Third bulleted item
\end{itemize}
was produced by
\begin{verbatim}
\begin{itemize}
  \item First bulleted item
  \item Second bulleted item
  \item Third bulleted item
\end{itemize}
\end{verbatim}

\subsection{Figures}

The \texttt{interact} class file will deal with positioning your figures in the same way as standard \LaTeX. It should not normally be necessary to use the optional \texttt{[htb]} location specifiers of the \texttt{figure} environment in your manuscript; you may, however, find the \verb"[p]" placement option or the \verb"endfloat" package useful if a journal insists on the need to separate figures from the text.

Figure captions appear below the figures themselves, therefore the \verb"\caption" command should appear after the body of the figure. For example, Figure~\ref{sample-figure} with caption and sub-captions is produced using the following commands:
\begin{verbatim}
\begin{figure}
\centering
\subfloat[An example of an individual figure sub-caption.]{%
\resizebox*{5cm}{!}{\includegraphics{graph1.eps}}}\hspace{5pt}
\subfloat[A slightly shorter sub-caption.]{%
\resizebox*{5cm}{!}{\includegraphics{graph2.eps}}}
\caption{Example of a two-part figure with individual sub-captions
 showing that captions are flush left and justified if greater
 than one line of text.} \label{sample-figure}
\end{figure}
\end{verbatim}
\begin{figure}
\centering
\subfloat[An example of an individual figure sub-caption.]{%
\resizebox*{5cm}{!}{\includegraphics{graph1.eps}}}\hspace{5pt}
\subfloat[A slightly shorter sub-caption.]{%
\resizebox*{5cm}{!}{\includegraphics{graph2.eps}}}
\caption{Example of a two-part figure with individual sub-captions
 showing that captions are flush left and justified if greater
 than one line of text.} \label{sample-figure}
\end{figure}

To ensure that figures are correctly numbered automatically, the \verb"\label" command should be included just after the \verb"\caption" command, or in its argument.

The \verb"\subfloat" command requires \verb"subfig.sty", which is called in the preamble of the \texttt{interactnlmsample.tex} file (to allow your choice of an alternative package if preferred) and included in the \textsf{Interact} \LaTeX\ bundle for convenience. Please supply any additional figure macros used with your article in the preamble of your .tex file.

The source files of any figures will be required when the final, revised version of a manuscript is submitted. Authors should ensure that these are suitable (in terms of lettering size, etc.) for the reductions they envisage.

The \texttt{epstopdf} package can be used to incorporate encapsulated PostScript (.eps) illustrations when using PDF\LaTeX, etc. Please provide the original .eps source files rather than the generated PDF images of those illustrations for production purposes.

\subsection{Tables}

The \texttt{interact} class file will deal with positioning your tables in the same way as standard \LaTeX. It should not normally be necessary to use the optional \texttt{[htb]} location specifiers of the \texttt{table} environment in your manuscript; you may, however, find the \verb"[p]" placement option or the \verb"endfloat" package useful if a journal insists on the need to separate tables from the text.

The \texttt{tabular} environment can be used as shown to create tables with single horizontal rules at the head, foot and elsewhere as appropriate. The captions appear above the tables in the \textsf{Interact} style, therefore the \verb"\tbl" command should be used before the body of the table. For example, Table~\ref{sample-table} is produced using the following commands:
\begin{table}
\tbl{Example of a table showing that its caption is as wide as
 the table itself and justified.}
{\begin{tabular}{lcccccc} \toprule
 & \multicolumn{2}{l}{Type} \\ \cmidrule{2-7}
 Class & One & Two & Three & Four & Five & Six \\ \midrule
 Alpha\textsuperscript{a} & A1 & A2 & A3 & A4 & A5 & A6 \\
 Beta & B2 & B2 & B3 & B4 & B5 & B6 \\
 Gamma & C2 & C2 & C3 & C4 & C5 & C6 \\ \bottomrule
\end{tabular}}
\tabnote{\textsuperscript{a}This footnote shows how to include
 footnotes to a table if required.}
\label{sample-table}
\end{table}
\begin{verbatim}
\begin{table}
\tbl{Example of a table showing that its caption is as wide as
 the table itself and justified.}
{\begin{tabular}{lcccccc} \toprule
 & \multicolumn{2}{l}{Type} \\ \cmidrule{2-7}
 Class & One & Two & Three & Four & Five & Six \\ \midrule
 Alpha\textsuperscript{a} & A1 & A2 & A3 & A4 & A5 & A6 \\
 Beta & B2 & B2 & B3 & B4 & B5 & B6 \\
 Gamma & C2 & C2 & C3 & C4 & C5 & C6 \\ \bottomrule
\end{tabular}}
\tabnote{\textsuperscript{a}This footnote shows how to include
 footnotes to a table if required.}
\label{sample-table}
\end{table}
\end{verbatim}

To ensure that tables are correctly numbered automatically, the \verb"\label" command should be included just before \verb"\end{table}".

The \verb"\toprule", \verb"\midrule", \verb"\bottomrule" and \verb"\cmidrule" commands are those used by \verb"booktabs.sty", which is called by the \texttt{interact} class file and included in the \textsf{Interact} \LaTeX\ bundle for convenience. Tables produced using the standard commands of the \texttt{tabular} environment are also compatible with the \texttt{interact} class file.

\subsection{Landscape pages}

If a figure or table is too wide to fit the page it will need to be rotated, along with its caption, through 90$^{\circ}$ anticlockwise. Landscape figures and tables can be produced using the \verb"rotating" package, which is called by the \texttt{interact} class file. The following commands (for example) can be used to produce such pages.
\begin{verbatim}
\setcounter{figure}{1}
\begin{sidewaysfigure}
\centerline{\epsfbox{figname.eps}}
\caption{Example landscape figure caption.}
\label{landfig}
\end{sidewaysfigure}
\end{verbatim}
\begin{verbatim}
\setcounter{table}{1}
\begin{sidewaystable}
 \tbl{Example landscape table caption.}
  {\begin{tabular}{@{}llllcll}
    .
    .
    .
  \end{tabular}}\label{landtab}
\end{sidewaystable}
\end{verbatim}
Before any such float environment, use the \verb"\setcounter" command as above to fix the numbering of the caption (the value of the counter being the number given to the preceding figure or table). Subsequent captions will then be automatically renumbered accordingly. The \verb"\epsfbox" command requires \verb"epsfig.sty", which is called by the \texttt{interact} class file and is also included in the \textsf{Interact} \LaTeX\ bundle for convenience.

Note that if the \verb"endfloat" package is used, one or both of the commands
\begin{verbatim}
\DeclareDelayedFloatFlavor{sidewaysfigure}{figure}
\DeclareDelayedFloatFlavor{sidewaystable}{table}
\end{verbatim}
will need to be included in the preamble of your .tex file, after the \verb"endfloat" package is loaded, in order to process any landscape figures and/or tables correctly.

\subsection{Theorem-like structures}

A predefined \verb"proof" environment is provided by the \texttt{amsthm} package (which is called by the \texttt{interact} class file), as follows:
\begin{proof}
More recent algorithms for solving the semidefinite programming relaxation are particularly efficient, because they explore the structure of the MAX-CUT problem.
\end{proof}
\noindent This was produced by simply typing:
\begin{verbatim}
\begin{proof}
More recent algorithms for solving the semidefinite programming
relaxation are particularly efficient, because they explore the
structure of the MAX-CUT problem.
\end{proof}
\end{verbatim}
Other theorem-like environments (theorem, definition, remark, etc.) need to be defined as required, e.g.\ using \verb"\newtheorem{theorem}{Theorem}" in the preamble of your .tex file (see the preamble of \verb"interactnlmsample.tex" for more examples). You can define the numbering scheme for these structures however suits your article best. Please note that the format of the text in these environments may be changed if necessary to match the style of individual journals by the typesetter during preparation of the proofs.

\subsection{Mathematics}

\subsubsection{Displayed mathematics}

The \texttt{interact} class file will set displayed mathematical formulas centred on the page without equation numbers if you use the \texttt{displaymath} environment or the equivalent \verb"\[...\]" construction. For example, the equation
\[
 \hat{\theta}_{w_i} = \hat{\theta}(s(t,\mathcal{U}_{w_i}))
\]
was typeset using the commands
\begin{verbatim}
\[
 \hat{\theta}_{w_i} = \hat{\theta}(s(t,\mathcal{U}_{w_i}))
\]
\end{verbatim}

For those of your equations that you wish to be automatically numbered sequentially throughout the text for future reference, use the \texttt{equation} environment, e.g.
\begin{equation}
 \hat{\theta}_{w_i} = \hat{\theta}(s(t,\mathcal{U}_{w_i}))
\end{equation}
was typeset using the commands
\begin{verbatim}
\begin{equation}
 \hat{\theta}_{w_i} = \hat{\theta}(s(t,\mathcal{U}_{w_i}))
\end{equation}
\end{verbatim}

Part numbers for sets of equations may be generated using the \texttt{subequations} environment, e.g.
\begin{subequations} \label{subeqnexample}
\begin{equation}
     \varepsilon \rho w_{tt}(s,t) = N[w_{s}(s,t),w_{st}(s,t)]_{s},
     \label{subeqnparta}
\end{equation}
\begin{equation}
     w_{tt}(1,t)+N[w_{s}(1,t),w_{st}(1,t)] = 0,   \label{subeqnpartb}
\end{equation}
\end{subequations}
which was typeset using the commands
\begin{verbatim}
\begin{subequations} \label{subeqnexample}
\begin{equation}
     \varepsilon \rho w_{tt}(s,t) = N[w_{s}(s,t),w_{st}(s,t)]_{s},
     \label{subeqnparta}
\end{equation}
\begin{equation}
     w_{tt}(1,t)+N[w_{s}(1,t),w_{st}(1,t)] = 0,   \label{subeqnpartb}
\end{equation}
\end{subequations}
\end{verbatim}
This is made possible by the \texttt{amsmath} package, which is called by the class file. If you put a \verb"\label" just after the \verb"\begin{subequations}" command, references can be made to the collection of equations, i.e.\ `(\ref{subeqnexample})' in the example above. Or, as the example also shows, you can label and refer to each equation individually -- i.e.\ `(\ref{subeqnparta})' and `(\ref{subeqnpartb})'.

Displayed mathematics should be given end-of-line punctuation appropriate to the running text sentence of which it forms a part, if required.

\subsubsection{Math fonts}

\paragraph{Superscripts and subscripts}
Superscripts and subscripts will automatically come out in the correct size in a math environment (i.e.\ enclosed within \verb"\(...\)" or \verb"$...$" commands in running text, or within \verb"\[...\]" or the \texttt{equation} environment for displayed equations). Sub/superscripts that are physical variables should be italic, whereas those that are labels should be roman (e.g.\ $C_p$, $T_\mathrm{eff}$). If the subscripts or superscripts need to be other than italic, they must be coded individually.

\paragraph{Upright Greek characters and the upright partial derivative sign}
Upright lowercase Greek characters can be obtained by inserting the letter `u' in the control code for the character, e.g.\ \verb"\umu" and \verb"\upi" produce $\umu$ (used, for example, in the symbol for the unit microns -- $\umu\mathrm{m}$) and $\upi$ (the ratio of the circumference of a circle to its diameter). Similarly, the control code for the upright partial derivative $\upartial$ is \verb"\upartial". Bold lowercase as well as uppercase Greek characters can be obtained by \verb"{\bm \gamma}", for example, which gives ${\bm \gamma}$, and \verb"{\bm \Gamma}", which gives ${\bm \Gamma}$.

\section*{Acknowledgement(s)}

An unnumbered section, e.g.\ \verb"\section*{Acknowledgements}", may be used for thanks, etc.\ if required and included \emph{in the non-anonymous version} before any Notes or References.

\section*{Disclosure statement}

An unnumbered section, e.g.\ \verb"\section*{Disclosure statement}", may be used to declare any potential conflict of interest and included \emph{in the non-anonymous version} before any Notes or References, after any Acknowledgements and before any Funding information.

\section*{Funding}

An unnumbered section, e.g.\ \verb"\section*{Funding}", may be used for grant details, etc.\ if required and included \emph{in the non-anonymous version} before any Notes or References.

\section*{Notes on contributor(s)}

An unnumbered section, e.g.\ \verb"\section*{Notes on contributors}", may be included \emph{in the non-anonymous version} if required. A photograph may be added if requested.

\section*{Nomenclature/Notation}

An unnumbered section, e.g.\ \verb"\section*{Nomenclature}" (or \verb"\section*{Notation}"), may be included if required, before any Notes or References.

\section*{Notes}

An unnumbered `Notes' section may be included before the References (if using the \verb"endnotes" package, use the command \verb"\theendnotes" where the notes are to appear, instead of creating a \verb"\section*").

\section{References}

\subsection{References cited in the text}

References should be cited in accordance with US National Library of Medicine (NLM) style. References are cited in the text by a number in square brackets (e.g. [1], [2,4,10], [11--15], \emph{not} [11]--[15]), in the order in which they first appear. For further details on this reference style, see the Instructions for Authors on the Taylor \& Francis website.

Each bibliographic entry has a key, which is assigned by the author and is used to refer to that entry in the text. In this document, the key \verb"Jen05" in the citation form \verb"\cite{Jen05}" produces `\cite{Jen05}', and the keys \verb"{Sch02,Wen95}" in the citation form \verb"\cite{Sch02,Wen95}" produce `\cite{Sch02,Wen95}'. The citation for a range of bibliographic entries (e.g.\ `\cite{Sha78,AG98,Smi75,Men05,DCK03,Hor98,Ant03,Zha05,Rog05,SRW05}') will automatically be produced by  \verb"\cite{Sha78,AG98,Smi75,Men05,DCK03,Hor98,Ant03,Zha05,Rog05,SRW05}". Optional notes may be included at the beginning and/or end of a citation by the use of square brackets, e.g.\ \verb"\cite[cf.][]{Gau05}" produces `\cite[cf.][]{Gau05}', \verb"\cite[p.356]{BGC04}" produces `\cite[p.356]{BGC04}', and \verb"\cite[see][p.73-–77]{PI51}" produces `\cite[see][p.73--77]{PI51}'.

\subsection{The list of references}

References should be listed at the end of the main text in the order in which they are first cited in the text. The following list shows some sample references prepared in the Taylor \& Francis NLM style.

\begin{thebibliography}{99}

\bibitem{Jen05}%1
Jenkins~PF. Making sense of the chest x-ray: a hands-on guide. New York (NY):
  Oxford University Press; 2005.

\bibitem{Sch02}%2
Schott~J, Priest~J. Leading antenatal classes: a practical guide. 2nd ed.
  Boston (MA): Books for Midwives; 2002.

\bibitem{Wen95}%3
Wenger~NK, Sivarajan~Froelicher~E, Smith~LK, et~al. Cardiac rehabilitation.
  Rockville (MD): Agency for Health Care Policy and Research (US); 1995.

\bibitem{Sha78}%4
Shakelford~RT. Surgery of the alimentary tract. Philadelphia (PA): W.B.
  Saunders; 1978. Chapter 2, Esophagoscopy; p. 29--40.

\bibitem{AG98}%5
Ambudkar~SV, Gottesman~MM, editors. {ABC} transporters: biomedical, cellular,
  and molecular aspects. San Diego (CA): Academic Press; 1998. (Methods in
  enzymology; vol. 292).

\bibitem{Smi75}%6
Smith~CE. The significance of mosquito longevity and blood-feeding behaviour in
  the dynamics of arbovirus infections. Med Biol. 1975;53:288--294.

\bibitem{Men05}%7
Meneton~P, Jeunemaitre~X, de~Wardener~HE, et~al. Links between dietary salt
  intake, renal salt handling, blood pressure, and cardiovascular diseases.
  Physiol Rev. 2005 Apr;85:679--715.

\bibitem{DCK03}%8
Dostorovsky~JO, Carr~DB, Koltzenburg~M, editors. Proceedings of the 10th World
  Congress on Pain; 2002 Aug~17--22; San Diego, CA. Seattle: IASP Press; c2003.

\bibitem{Hor98}%9
Horrobin~DF, Lampinskas~P. The commercial development of food plants used as
  medicines. In: Prendergast~HD, Etkin~NL, Harris~DR, et~al., editors. Plants
  for food and medicine. Proceedings of the Joint Conference of the Society for
  Economic Botany and the International Society for Ethnopharmacology; 1996
  Jul~1--6; London. Kew (UK): Royal Botanic Gardens; 1998. p. 75--81.

\bibitem{Ant03}%10
Antani~S, Long~LR, Thoma~GR, et~al. Anatomical shape representation in spine
  x-ray images. Paper presented at: VIIP 2003. Proceedings of the 3rd IASTED
  International Conference on Visualization, Imaging and Image Processing;
  2003 Sep~8--10; Benalmadena, Spain.

\bibitem{Zha05}%11
Zhao~C. Development of nanoelectrospray and application to protein research and
  drug discovery [dissertation]. Buffalo (NY): State University of New York at
  Buffalo; 2005.

\bibitem{Rog05}%12
Roguskie~JM. The role of \emph{Pseudomonas aeruginosa} 1244 pilin glycan in
  virulence [master's thesis]. [Pittsburgh (PA)]: Duquesne University; 2005.

\bibitem{SRW05}%13
Savage~E, Ramsay~M, White~J, et~al. Mumps outbreaks across England and Wales
  in 2004: Observational study. BMJ. 2005;330(7500):1119--1120 [cited 2005
  May~31]; Available from: http://bmj.bmjjournals.com/cgi/reprint/330/7500/1119.

\bibitem{Gau05}%14
Gaul~G. When geography influences treament options. Washington Post (Maryland
  Ed.). 2005 Jul~24;Sect.~A:12 (col.~1).

\bibitem{BGC04}%15
Berrino~F, Gatta~G, Crosignani~P. [Case-control evaluation of screening
  efficacy]. Epidemiol Prev. 2004 Nov--Dec;28:354--359. Italian.

\bibitem{PI51}%16
Piaget~J, Inhelder~B. La gen{\`e}se de l'id{\'e}e de hasard chez l'enfant
  [The origin of the idea of chance in the child]. Paris: Presses
  Universitaires de France; 1951.

\end{thebibliography}
\bigskip
\noindent This was produced by typing:
\begin{verbatim}
\begin{thebibliography}{99}

\bibitem{Jen05}%1
Jenkins~PF. Making sense of the chest x-ray: a hands-on guide. New York
 (NY): Oxford University Press; 2005.

\bibitem{Sch02}%2
Schott~J, Priest~J. Leading antenatal classes: a practical guide. 2nd
 ed. Boston (MA): Books for Midwives; 2002.

\bibitem{Wen95}%3
Wenger~NK, Sivarajan~Froelicher~E, Smith~LK, et~al. Cardiac
 rehabilitation. Rockville (MD): Agency for Health Care Policy and
 Research (US); 1995.

\bibitem{Sha78}%4
Shakelford~RT. Surgery of the alimentary tract. Philadelphia (PA):
 W.B. Saunders; 1978. Chapter 2, Esophagoscopy; p. 29--40.

\bibitem{AG98}%5
Ambudkar~SV, Gottesman~MM, editors. {ABC} transporters: biomedical,
 cellular, and molecular aspects. San Diego (CA): Academic Press; 1998.
 (Methods in enzymology; vol. 292).

\bibitem{Smi75}%6
Smith~CE. The significance of mosquito longevity and blood-feeding
 behaviour in the dynamics of arbovirus infections. Med Biol.
 1975;53:288--294.

\bibitem{Men05}%7
Meneton~P, Jeunemaitre~X, de~Wardener~HE, et~al. Links between dietary
 salt intake, renal salt handling, blood pressure, and cardiovascular
 diseases. Physiol Rev. 2005 Apr;85:679--715.

\bibitem{DCK03}%8
Dostorovsky~JO, Carr~DB, Koltzenburg~M, editors. Proceedings of the
 10th World Congress on Pain; 2002 Aug~17--22; San Diego, CA. Seattle:
 IASP Press; c2003.

\bibitem{Hor98}%9
Horrobin~DF, Lampinskas~P. The commercial development of food plants
 used as medicines. In: Prendergast~HD, Etkin~NL, Harris~DR, et~al.,
 editors. Plants for food and medicine. Proceedings of the Joint
 Conference of the Society for Economic Botany and the International
 Society for Ethnopharmacology; 1996 Jul~1--6; London. Kew (UK): Royal
 Botanic Gardens; 1998. p. 75--81.

\bibitem{Ant03}%10
Antani~S, Long~LR, Thoma~GR, et~al. Anatomical shape representation in
 spine x-ray images. Paper presented at: VIIP 2003. Proceedings of the
 3rd IASTED International Conference on Visualization, Imaging and
 Image Processing; 2003 Sep~8--10; Benalmadena, Spain.

\bibitem{Zha05}%11
Zhao~C. Development of nanoelectrospray and application to protein
 research and drug discovery [dissertation]. Buffalo (NY): State
 University of New York at Buffalo; 2005.

\bibitem{Rog05}%12
Roguskie~JM. The role of \emph{Pseudomonas aeruginosa} 1244 pilin
 glycan in virulence [master's thesis]. [Pittsburgh (PA)]: Duquesne
 University; 2005.

\bibitem{SRW05}%13
Savage~E, Ramsay~M, White~J, et~al. Mumps outbreaks across England and
 Wales in 2004: Observational study. BMJ. 2005;330(7500):1119--1120
 [cited 2005 May 31]; Available from:
 http://bmj.bmjjournals.com/cgi/reprint/330/7500/1119.

\bibitem{Gau05}%14
Gaul~G. When geography influences treament options. Washington Post
 (Maryland Ed.). 2005 Jul~24;Sect.~A:12 (col.~1).

\bibitem{BGC04}%15
Berrino~F, Gatta~G, Crosignani~P. [Case-control evaluation of screening
 efficacy]. Epidemiol Prev. 2004 Nov--Dec;28:354--359. Italian.

\bibitem{PI51}%16
Piaget~J, Inhelder~B. La gen{\`e}se de l'id{\'e}e de hasard chez
 l'enfant [The origin of the idea of chance in the child]. Paris:
 Presses Universitaires de France; 1951.

\end{thebibliography}
\end{verbatim}
\bigskip
\noindent Each entry takes the form:
\begin{verbatim}
\bibitem{key}%n Bibliography entry
\end{verbatim}
where `\texttt{key}' is the tag that is to be used as an argument for the \verb"\cite{}" commands in the text of the article and `\texttt{Bibliography entry}' is the material that is to appear in the list of references, suitably formatted. The commands
\begin{verbatim}
\usepackage[numbers,sort&compress]{natbib}
\bibpunct[, ]{[}{]}{,}{n}{,}{,}
\renewcommand\bibfont{\fontsize{10}{12}\selectfont}
\makeatletter
\def\NAT@def@citea{\def\@citea{\NAT@separator}}
\makeatother
\end{verbatim}
need to be included in the preamble of your .tex file in order to generate the citations and bibliography as described above.

Instead of typing the bibliography by hand, you may prefer to create the list of references using a \textsc{Bib}\TeX\ database. The \texttt{tfnlm.bst} file needs to be in your working folder or an appropriate directory, and the lines
\begin{verbatim}
\bibliographystyle{tfnlm}
\bibliography{interactnlmsample}
\end{verbatim}
included where the list of references is to appear, where \texttt{tfnlm.bst} is the name of the \textsc{Bib}\TeX\ bibliography style file for Taylor \& Francis' NLM reference style and \texttt{interactnlmsample.bib} is the bibliographic database included with the \textsf{Interact}-NLM \LaTeX\ bundle (to be replaced with the name of your own .bib file). \LaTeX/\textsc{Bib}\TeX\ will extract from your .bib file only those references that are cited in your .tex file and list them in the References section.

Please include a copy of your .bib file and/or the final generated .bbl file among your source files if your .tex file does not contain a reference list in a \texttt{thebibliography} environment.

\section{Appendices}

Any appendices should be placed after the list of references, beginning with the command \verb"\appendix" followed by the command \verb"\section" for each appendix title, e.g.
\begin{verbatim}
\appendix
\section{This is the title of the first appendix}
\section{This is the title of the second appendix}
\end{verbatim}
produces:\medskip

\noindent\textbf{Appendix A. This is the title of the first appendix}\medskip

\noindent\textbf{Appendix B. This is the title of the second appendix}\medskip

\noindent Subsections, equations, figures, tables, etc.\ within appendices will then be automatically numbered as appropriate. Some theorem-like environments may need to have their counters reset manually (e.g.\ if they are not numbered within sections in the main text). You can achieve this by using \verb"\numberwithin{remark}{section}" (for example) just after the \verb"\appendix" command.

Note that if the \verb"endfloat" package is used on a document containing any appendices, the \verb"\processdelayedfloats" command must be included immediately before the \verb"\appendix" command in order to ensure that the floats belonging to the main body of the text are numbered as such.

%\processdelayedfloats %%% See above for an explanation of why this command might be needed here.

\appendix

\section{Troubleshooting}

Authors may occasionally encounter problems with the preparation of a manuscript using \LaTeX. The appropriate action to take will depend on the nature of the problem:
\begin{enumerate}
\item[(i)] If the problem is with \LaTeX\ itself, rather than with the actual macros, please consult an appropriate \LaTeXe\ manual for initial advice. If the solution cannot be found, or if you suspect that the problem does lie with the macros, then please contact Taylor \& Francis for assistance (\texttt{latex.helpdesk@tandf.co.uk}), clearly stating the title of the journal to which you are submitting.
\item[(ii)] Problems with page make-up (e.g.\ occasional overlong lines of text; figures or tables appearing out of order): please do not try to fix these using `hard' page make-up commands -- the typesetter will deal with such problems. (You may, if you wish, draw attention to particular problems when submitting the final version of your manuscript.)
\item[(iii)] If a required font is not available on your system, allow \TeX\ to substitute the font and specify which font is required in a covering letter accompanying your files.
\end{enumerate}

\section{Obtaining the template and class file}

\subsection{Via the Taylor \& Francis website}

This article template and the \texttt{interact} class file may be obtained via the `Instructions for Authors' pages of selected Taylor \& Francis journals.

Please note that the class file calls up the open-source \LaTeX\ packages booktabs.sty, epsfig.sty and rotating.sty, which will, for convenience, unpack with the downloaded template and class file. The template calls for natbib.sty and subfig.sty, which are also supplied for convenience.

\subsection{Via e-mail}

This article template, the \texttt{interact} class file and the associated open-source \LaTeX\ packages are also available via e-mail. Requests should be addressed to \texttt{latex.helpdesk@tandf.co.uk}, clearly stating for which journal you require the template and class file.

\end{document}

### 2021-12-07 paper/interactnlmsample.tex
added ROM equation

@@
 \end{table}
+
+\section{ROM}
+\subsection{ROM Implementation}
+
+Using the POD-Galerkin projection, a ROM was constructed to approximate the group flux and the core power of the LRA benchmark.
+As discussed in the previous chapter, the time-dependent diffusion equation coupled with the precursors group equation can be cast into a compact form as in Eq.~\ref{eq:transient fom}.
+Similar to the TWIGL benchmark ROM, POD basis set was generated for each group flux while one basis set was generated for both precursors groups, i.e, 
+$\mathbf{\Phi}_1(t) = \mathbf{U}_1\mathbf{a}_1(t)$, $\mathbf{\Phi}(t)_2 = \mathbf{U}_2\mathbf{a}_2(t)$ and $\mathbf{C}(t) = \mathbf{U}_c\mathbf{a}_c(t)$, where the $\mathbf{U}_1$, $\mathbf{U}_2$  and $\mathbf{U}_c$ are the POD bases of the fast group, thermal group and precursor concentration respectively, and $\mathbf{a}_1$, $\mathbf{a}_2$ and $\mathbf{a}_c$ are their respective temporal coefficients.
+The first 100 normalized singular values \footnote{The normalization is done be dividing each singular value by the sum of all singular values.} of the group flux are shown in Fig.~\ref{fig:lra singular values}.
+\begin{figure}[h!]
+	\includegraphics[width=1.0\linewidth]{figures/LRA/LRA_singular_values.pdf}
+	\caption{flux normalized singular value.}
+	\label{fig:lra singular values}
+\end{figure}
+Since the focus of this application is on treating the non-linearity, rather than trying different ranks of the POD basis, rank 30 was chosen for each group flux and for the precursor concentration.
+Also, the temperature field was approximated by projecting it onto a lower dimensional POD space
+\begin{equation}
+\mathbf{T}(t) = \mathbf{U}_{\text{temp}}\mathbf{a}_T(t) \, ,
+\label{eq:temp pod}
+\end{equation}
+where $\mathbf{U}_{\text{temp}}\in\mathbb{R}^{n \times r_T} $ is the POD subspace of rank $r_T$ and $\mathbf{a}_T\in \mathbb{R}^{r_T}$ is a vector of the corresponding temporal coefficients. 
+To obtain the subspace, snapshots of the temperature were collected at different times for which the SVD was computed.
+Shown in Fig.~\ref{fig:lra T singular values} are the first 100 normalized singular values, based on which a POD of rank $10$ was selected for approximating the temperature.
+\begin{figure}[H]
+	\centering
+	\includegraphics[width=1.0\linewidth]{figures/LRA/LRA_T_singular_values.pdf}
+	\caption{temperature normalized singular value.}
+	\label{fig:lra T singular values}
+\end{figure}
+Inserting Eq.~\ref{eq:temp pod} into Eq.~\ref{eq:heatup} and multiplying on the left by $\mathbf{U}_T^T$ \footnote{The superscript T denotes the matrix transpose.} yields
+\begin{equation}
+\frac{d\mathbf{a}_T(t)}{dt}  = \alpha [\underbrace{\mathbf{U}_{\text{temp}}^T \boldsymbol{\Sigma}_{f1}\mathbf{U}_1}_{\mathbf{U}_{T1}}\mathbf{a_1}(t) + \underbrace{\mathbf{U}_{\text{temp}}^T\boldsymbol{\Sigma}_{f2}\mathbf{U}_2}_{\mathbf{U}_{T2}}\mathbf{a_2}(t)] \, .
+\label{eq:reduced temp}
+\end{equation}
+Note that $\mathbf{U}_{T1}$ and $\mathbf{U}_{T2}$ are time-independent, so they can be precomputed once and stored.
+Thus, at each time step the flux temporal coefficients (i.e, $\mathbf{a_1}(t)$ and $\mathbf{a_2}(t)$) are computed by solving the reduced system and then used to compute the temperature coefficients by employing a first-order, backward-difference scheme to Eq.~\ref{eq:reduced temp}.
+Similar to the full-order model, a fixed point iteration is used to treat the flux non-linearity.
+However, it was observed that the reduced model needed more iterations to converge which could be due to the small value of some of the flux coefficients, hence a convergence criteria was employed based on the relative $\text{L}_2$ norm of the error of flux coefficients between two consecutive iterations
+\begin{equation}
+\frac{\| \mathbf{a}^{i-1} - \mathbf{a}^{i}\|}{\|\mathbf{a}_i \|} \le 1\times 10^{-6}  \, , 
+\end{equation}
+Note that the fast absorption cross section needs to be updated at each time step using Eq.~\ref{eq:doppler} in which the core temperature distribution is required.
+In order to avoid reconstructing the full order temperature, 
+the DEIM was used to approximate the absorption cross section.
+For this purpose, snapshots of which were collected in order to generate a POD subspace that is used to approximate its space and to find a set of interpolation indices as illustrated in Algorithm~\ref{alg:DEIM}.
+DEIM of order $10$ was used and hence, the cross section was reconstructed at each time step at only 10 points in the spatial space.
+Moreover, since the reactivity insertion was simulated by changing the absorption cross section, the operator $\mathbf{A}$ in Eq.~\ref{Eq:transient rom} exhibits time dependence, 
+The MDEIM was used to decompose the operator and hence avoid performing the expensive projection at each time step.
+Shown in Fig.~\ref{fig:lra L singular values} are the singular values resulting from the SVD of the serialized operator snapshots. 
+Based on the shown plot, a DEIM of order $15$ was used.
+\begin{figure}[H]
+	\includegraphics[width=1.0\linewidth]{figures/LRA/LRA_L_singular_values.pdf}
+	\caption{Operator normalized singular value.}
+	\label{fig:lra L singular values}
+\end{figure}
+
+%------------------------------------------------------------------------%
+\subsection{Results}
+
+\subsubsection{ROM results}
+ROMs were constructed for FOMs models with increasing the spatial fidelity, i.e, spatial grids of $22\times 22$, $44\times44$ and $55 \times 55$.
+For brevity, we show the POD modes with their temporal coefficients of only the $55 \times 55$  grid in Fig.~\ref{fig:lra flux modes}.
+\begin{figure}[H]
+	\centering
+	\begin{subfigure}[b]{0.45\textwidth}
+		\includegraphics[width=1.0\linewidth]{../figures/LRA_fast_modes.pdf}
+		\caption{Fast flux modes.}
+		\label{fig:ss fast flux}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.45\textwidth}
+		\includegraphics[width=1.0\linewidth]{../figures/LRA_thermal_modes.pdf}
+		\caption{Thermal flux modes.}
+		\label{fig:ss thermal flux}
+	\end{subfigure}
+	\caption{Flux POD modes and their temporal coefficient.}
+	\label{fig:lra flux modes}
+\end{figure}
+Using ROMs with the specifications given in the previous section, the absolute relative error in the predicted powers are computed as shown in Fig.~\ref{fig:deim power error}.
+\begin{figure}[H]
+	\includegraphics[width=1.0\linewidth]{../figures/LRA_power_deim_relative_error.pdf}
+	\caption{Relative error of the power predicted by MDEIM ROM}
+	\label{fig:deim power error}
+\end{figure}
+The maximum flux errors for both groups are shown in Table \ref{tab:lra flux errors}.
+
+\begin{table*}[H]
+	\centering
+	\begin{tabular}{c|c|c}  
+		grid &	fast flux  &  thermal flux \\
+		\hline
+		$22\times 22$ &    &  1     \\
+		$44\times 44$ &    &       \\
+		$55\times 55$ &    &       \\
+		\hline
+	\end{tabular}
+	\caption{\bf maximum flux error of the fast and thermal flux (\%)}
+	\label{tab:lra flux errors}
+\end{table*}
+It was interesting to compare the power error with that of a ROM without MDEIM, i.e, with performing the operator projection at each time step.
+The power error is shown in Fig.~\ref{fig:rom power error} and apparently, the accuracy is comparable to that in Fig.~\ref{fig:deim power error}, implying an accurate approximation of the problem operator via the MDEIM.
+\begin{figure}[H]
+	\includegraphics[width=1.0\linewidth]{../figures/LRA_power_rom_relative_error.pdf}
+	\caption{Relative error of the power predicted by ROM.}
+	\label{fig:rom power error}
+\end{figure}
+Also, the spatial-averaged relative error in the approximated temperature was computed and is shown in Fig.~\ref{fig:deim tempearture error}.
+\begin{figure}[H]
+	\includegraphics[width=1.0\linewidth]{../figures/temperature_relative_error.pdf}
+	\caption{Relative error of the temperature predicted by ROM.}
+	\label{fig:deim tempearture error}
+\end{figure}
+
+As mentioned earlier, the non-linearity of the fast absorption cross section was approximated using DEIM of rank 10.
+Shown in Fig.~\ref{fig:cross-section deim indices} are the 10 selected interpolation points on the absorption cross section map at the last time step. i.e, $t=3$ s.
+Thus, the temperature is constructed only at these locations from which the cross section is evaluated using Eq.~\ref{eq:doppler}.
+
+\begin{figure}[H]
+	\includegraphics[width=1.0\linewidth]{../figures/LRA_XS_interpolation_points_XS_map.pdf}
+	\caption{The fast cross section at t=3 with the selected interpolation indices in red color.}
+	\label{fig:cross section deim indices}
+\end{figure}
+
+The power assembly relative errors are computed and shown in Fig.~\ref{fig:assembly power error fm=5} for the $55\times 55$ grid.
+The same errors for the other two grids are given in appendix?.
+\begin{figure}[H]
+	\includegraphics[width=0.9\linewidth]{../figures/lra_assemb_fm=5.pdf}
+	\caption{Assembley power relative error for the $55\times 55$ grid}
+	\label{fig:assembly power error fm=5}
+\end{figure}
+
+The computational time for the FOM and the ROMS are given in Table~\ref{table:cpu time}.
+
+\begin{table*}[h!]
+	\centering
+	\caption{\bf computational time of the FOM and the ROMs}
+	\label{table:cpu time}
+	\begin{tabular}{c|c|c|c}  
+		grid &	FOM (s)   &  ROM (s) & MDEIM-ROM (s)    \\
+		\hline
+		$22\times 22$ & 426   & 140   & 101   \\
+		$44\times 44$ &  1652  &   283 &  106  \\
+		$55\times 55$ &  2539  & 398   & 110   \\
+		\hline
+	\end{tabular}
+\end{table*}
 

### 2022-02-22 paper/interactnlmsample.tex
working on the introduction

@@
 \usepackage{caption}
-\usepackage{subcaption}
+%\usepackage{subcaption}
 \usepackage{tikz}
@@
 \usepackage{booktabs,tabularx}
+\DeclareMathOperator{\argmaxH}{argmax} 
+\DeclareMathOperator*{\argmin}{argmin}
+\renewcommand{\algorithmicrequire}{\textbf{Input:}}
+\renewcommand{\algorithmicensure}{\textbf{Output:}}
+\newcommand\abs[1]{\left|#1\right|}
 
@@
 
-\title{Taylor \& Francis \LaTeX\ template for authors (\textsf{Interact} layout + NLM reference style)}
-
+\title{Model-order reduction of non-linear time dependent neutronics via Galerkin projection and DEIM}
 \author{
-\name{A.~N. Author\textsuperscript{a}\thanks{CONTACT A.~N. Author. Email: latex.helpdesk@tandf.co.uk} and John Smith\textsuperscript{b}}
-\affil{\textsuperscript{a}Taylor \& Francis, 4 Park Square, Milton Park, Abingdon, UK; \textsuperscript{b}Institut f\"{u}r Informatik, Albert-Ludwigs-Universit\"{a}t, Freiburg, Germany}
+\name{Rabab Elzohery \thanks{CONTACT A.~N. Author. Email: rababelzohery@ksu.edu} and Jeremy Roberts}
+\affil{Department of Mechanical and Nuclear Engineering,
+	Kansas State University \\
+	3002 Rathbone Hall, Manhattan, KS 66506, US \\ rababelzohery@ksu.edu, jaroberts@ksu.edu}
 }
@@
 \begin{abstract}
-This template is for authors who are preparing a manuscript for a Taylor \& Francis journal using the \LaTeX\ document preparation system and the \texttt{interact} class file, which is available via selected journals' home pages on the Taylor \& Francis website.
+
 \end{abstract}
@@
 \begin{keywords}
-Sections; lists; figures; tables; mathematics; fonts; references; appendices
+Galerkin projection; POD; ROM; Neutronic Transient
 \end{keywords}
@@
 
-In order to assist authors in the process of preparing a manuscript for a journal, the Taylor \& Francis `\textsf{Interact}' layout style has been implemented as a \LaTeXe\ class file based on the \texttt{article} document class.
-A \textsc{Bib}\TeX\ bibliography style file and a sample bibliography are also provided in order to assist with the formatting of your references.
-
-Commands that differ from or are provided in addition to standard \LaTeXe\ are described in this document, which is \emph{not} a substitute for a \LaTeXe\ tutorial.
-
-The \texttt{interactnlmsample.tex} file can be used as a template for a manuscript by cutting, pasting, inserting and deleting text as appropriate, using the preamble and the \LaTeX\ environments provided (e.g.\ \verb"\begin{abstract}", \verb"\begin{keywords}").
-
-\subsection{The \textsf{Interact} class file}\label{class}
-
-The \texttt{interact} class file preserves the standard \LaTeXe\ interface such that any document that can be produced using \texttt{article.cls} can also be produced with minimal alteration using the \texttt{interact} class file as described in this document.
-
-If your article is accepted for publication it will be typeset as the journal requires in Minion Pro and/or Myriad Pro.
-Since most authors will not have these fonts installed, the page make-up is liable to alter slightly with the change of font.
-Also, the \texttt{interact} class file produces only single-column format, which is preferred for peer review and will be converted to two-column format by the typesetter if necessary during preparation of the proofs.
-Please therefore do not try to match the typeset format exactly, but use the standard \LaTeX\ fonts instead and ignore details such as slightly long lines of text or figures/tables not appearing in exact synchronization with their citations in the text: these details will be dealt with by the typesetter.
-Similarly, it is unnecessary to spend time addressing warnings in the log file -- if your .tex file compiles to produce a PDF document that correctly shows how you wish your paper to appear, such warnings will not prevent your source files being imported into the typesetter's program.
-
-\subsection{Submission of manuscripts prepared using \emph{\LaTeX}}
-
-Manuscripts for possible publication should be submitted to the Editors for review as directed in the journal's Instructions for Authors, and in accordance with any technical instructions provided in the journal's ScholarOne Manuscripts or Editorial Manager site.
-Your \LaTeX\ source file(s), the class file and any graphics files will be required in addition to the final PDF version when final, revised versions of accepted manuscripts are submitted.
-
-Please ensure that any author-defined macros used in your article are gathered together in the preamble of your .tex file, i.e.\ before the \verb"\begin{document}" command.
-Note that if serious problems are encountered in the coding of a document (missing author-defined macros, for example), the typesetter may resort to rekeying it.
+Modeling and simulation of nuclear reactors is crucial to predict their behavior under different conditions and scenarios and hence ensure reliable design and safety limits.
+The mathematical models are described by a set of equations that is challenging to solve analytically due to the geometric complexity of nuclear reactors except for simplified cases.
+Alternatively, these systems are solved by employing numerical discretization that rely on discretizing the system along each independent variable and the solution is provided only on these discrete points.
+To improve the method accuracy, the system needs to be solved over a very fine mesh.
+Although this results in a more reliable solution, it leads to a growing space dimension and accordingly large computational cost.
+This problem of the computational cost becomes inevitably prohibitive with applications that require repetitive execution of the simulation such as uncertainty quantification, and design optimization.
+In such studies, the high-fidelity model has to be solved at multiple parameter points which could be very large.
+Hence, surrogate models that are cheap, yet accurate, are sought to provide a rapid and reliable approximation of the solution of these systems.
+The premise is that this lower-order model will capture the essential features of the system  and preserve the input-output mapping as much as possible.
+
+In the application of our interest here, neutronic transients, the mathematical models are based on the diffusion approximation and the Boltzmann transport equation.
+For realistic modeling, these neutron transport model need to be coupled with different physics models to account for the feedback.
+For example, thermal-hydraulics feedback plays an essential role in reactor operation.
+Changes in the fuel temperature alter the cross sections due to Doppler broadening \cite{stacey2018nuclear}, which in turn impacts the neutron population and hence the fission rate and the rate of heat generation.
+Multi-physics modeling accounts for these different feedbacks mechanisms; however, it poses a challenge in terms of the computational cost,
+since it entails solving coupled systems for different fields such as neutron flux, temperature, and flow rate.
+Moreover, the neutron transport (or diffusion) equation is no longer a linear one due to the indirect dependence of the cross section on the neutron flux.
+Two approaches are used to solve such systems.
+The most commonly used one is a serial coupling of two or more separate codes in such a way that the output of one at a given time step, such as the flux distribution, is used as an input to the other, e.g., the temperature (which can be used then to update the cross section and so on).
+This procedure is commonly referred to as operator splitting or explicit coupling.
+One drawback of operator splitting is that time integration requires small steps to avoid stability issues, thus leading to high computational time. 
+Alternatively, tight coupling in time between the physics can be maintained by using an implicit scheme that solves a non-linear iteration in each time step, also increasing the computational time.
+A modern algorithm such as Jacobian free Newton-Krylov (JFNK) \cite{gaston2009parallel} can be used to perform this implicit coupling.
+Another popular approach is to use fixed-point iteration, with an implicit time scheme to iterate between difference physics within a time step until convergence is satisfied, which is compitationaly taxing.
+The aim of this work is to use a reduce-order model to overcome the high computational expense of these non-linear models.
+In particular, the ROM was developed using the POD-Galerkin projection.
+The method belongs to the projection-based family, and can be described as an physics-driven method since it requires knowlege of the original governing equation as will be shown in sec.  .
+In a previous work, \cite{elzohery-greedyPOD}, we applied the method to time dependent diffusion equation where there was no coupling with other models and hence the application was linear.
+In this study, the developed ROM was extended to treat non-linearity problem induced by multi physics modeling.
+The LRA benchmark was used as a demonstrative application where coupling the diffusion equation is coupled with a simplified thermal model.
+
+To improve the computational efficiency of the developed ROM, a hyper-reduction technique known as the Discrete Empirical Interpolation Method (DEIM) was used in conjunction of the POD-Galerkin projection.
+The primary purpose of using the DEIM is to obtain an offline-online decomposition of the ROM to avoid repetitive projection of the problem operator at each iteration with each time step.
+The offline stage occurs only once and it comprises the expensive step of the ROM, where the online stage is cheaper and involves solving a reduced number of equation at each time step.
+The following discussion include a general overview of the methods and algorithms, then the specific application was described.
+Results are presented and conclusion was given.
+
+\section{Methods Overview}
+\subsection{POD-Galerkin Projection}\label{class}
+
+Consider the following dynamic system that results from discretizing a partial differential equation using a numerical scheme such as the finite difference method:
+\begin{equation}
+\frac{d\mathbf{y}(t)}{dt} = \mathbf{A}\mathbf{y}(t) + \mathbf{f}(\mathbf{y}(t)),  \quad\quad \mathbf{y(0) = \mathbf{y_0}} \, ,
+\label{eq:FOM}
+\end{equation}
+where $\mathbf{y} \in \mathbb{R}^{n}$ is the state variable and $\mathbf{A} \in \mathbb{R}^{n\times n}$ is the operator resulting from the system discretization.
+In general, this method involves two main steps. 
+First, the state variable $\mathbf{y}$ is expanded in terms of a trial subspace basis, which is the POD space in this case, where each basis vector is weighted by a temporal coefficient
+\begin{equation}
+\mathbf{y} \approx \mathbf{\Phi} \hat{\mathbf{y}}(t) \, ,
+\label{eq:galerkin expansion}
+\end{equation}
+where $\mathbf{\hat{y}(t)} \in \mathbb{R}^{r}$ is a vector of the temporal coefficients.
+Second, the system is projected onto a test subspace, which is the same as the trial subspace in the Galerkin projection procedures.
+By multiplying the system on the left by $\mathbf{\Phi}^T$ and making use of the orthogonality of the POD basis (i.e, $\mathbf{\Phi}^T\mathbf{\Phi} = \mathbf{I}$), we end up with 
+\begin{equation}
+\frac{d\mathbf{\hat{y}}}{dt} = \mathbf{A}_r\mathbf{\hat{y}} + \mathbf{\Phi}^T\mathbf{f}(\mathbf{\Phi}\mathbf{\hat{y}}) \qquad \mathbf{\hat{y}}(0) = \mathbf{\Phi}^T\mathbf{y}_0 \, ,
+\label{eq:ROM}
+\end{equation}
+where $\mathbf{A}_r \in \mathbb{R}^{r\times r} = \mathbf{\Phi}^T\mathbf{A}\mathbf{\Phi}.$
+Thus, we are left with  $r$ ODE's instead of $n$ ODE's, which makes the resulting ROM more computationally efficien, and, once it is solved for $\mathbf{\hat{y}}$, the full order solution can be computed by Eq.~\ref{eq:galerkin expansion}.
+Note that the POD basis is chosen here for its optimality property.
+However, different methods have been used in the literature, such as the eigenmodes analysis and the reduced-basis method \cite{rozza2008reduced, hesthaven2016certified, veroy2003posteriori}.
+Moreover, the test basis and the trial basis could be different, in which case the method is called Petrov-Galerkin projection.
+In such cases, unless the test and the trial basis are bi-orthogonal, there will be an additional computational cost associated with inverting the matrix resulting from multiplying the left hand side of Eq.~\ref{eq:FOM} by the test basis.
+
+\subsection{Discrete Impricical Interpolation Method \emph{\LaTeX}}
+
+\label{sec:DEIM}
+Recently, the DEIM \cite{chaturantabut2010nonlinear} was proposed to approximate the non-linearity in model order reduction.
+The method is a discrete variant of the Empirical Interpolation Method (EIM) \cite{barrault2004empirical} that was originally proposed to approximate
+non-affine coefficient functions using a reduced-basis expansion to facilitate the online/offline decomposition in finite element methods.
+The DEIM is proposed for the same goal for different discretizations of the full-order model.
+The method relies on two main ingredients: (1) a reduced space that approximates the nonlinear function, and (2) a set of spatial interpolation indices.
+To illustrate the method, let $\tau$ denote time or a model parameter.
+The nonlinear function $\mathbf{f}(\textbf{y}(\tau))$ is approximated by projecting it onto a subspace that approximates the function space
+\begin{equation}
+\mathbf{f}(\textbf{y}(\tau)) = \mathbf{\Psi}\boldsymbol{\theta}(\tau)\, ,
+\end{equation}
+where $\mathbf{\Psi} \in \mathbb{R}^{n\times k}$ is a low-dimensional subspace with $k \ll n$, and $\boldsymbol{\theta}(\tau) \in \mathbb{R}^k$ is a vector of the corresponding coefficients.
+POD is used to find the subspace $\mathbf{\Psi}$ using snapshots of the function (i.e, $[\textbf{y}(\tau_1), ....., \textbf{y}(\tau_m)]$).
+Note that these snapshots are computed at the same points used for the state variable snapshots required for the reduced model; hence this step will not introduce any additional cost other than computing the SVD.
+In order to compute $\theta(\tau)$, a few spatial indices are selected iteratively using a greedy search following Algorithm \ref{alg:DEIM}.
+The basic idea is to select $k$ rows of the basis matrix $\mathbf{\Psi}$.
+The algorithm takes as an input the basis vectors of the subspace $\mathbf{\Psi}$.
+The first index is selected where the entry of the first input basis has the largest magnitude.
+Each other index $\mathcal{I}_i$ is selected where the approximation of the corresponding input basis vector $\mathbf{\Psi_i}$ in the subspace constructed by interpolating the basis $[\mathbf{\Psi}_1, ....\mathbf{\Psi}_{i-1}]$ at the previously selected indices is worst.
+Once the indices are selected, the matrix $\mathbf{\Psi}_k \in \mathbb{R}^{k\times k}$ is formed such that
+\begin{equation}
+\mathbf{\Psi}_k = \mathbf{P}^T\mathbf{\Psi}\, ,
+\end{equation}
+where $\mathbf{P} = [e_{z1}, e_{z2}, ....,e_{zk}] \in \mathbb{R}^{n\times k}$ and $e_{zi} = [0,.., 0, \underbrace{1}_{{zi}}, 0..., 0]^\text{T} \in \mathbb{R}^{n}$
+is the  ${zi}$th column of the identity matrix.
+The coefficients can be computed by solving
+\begin{equation}
+\mathbf{P}^T\mathbf{f(\tau)}=\mathbf{\Psi}_k \boldsymbol{\theta}(\tau)\, ,
+\label{eq:DEIM coefficients}
+\end{equation}
+and the final function approximation is given by
+\begin{equation}
+\hat{\mathbf{f}}(\tau)\approx\mathbf{\Psi}( \mathbf{\Psi}_k)^{-1}\mathbf{P}^T\mathbf{f} (\tau)\, .
+\end{equation}
+Note that the matrix $\mathbf{P}$ does not need to be constructed explicitly, since the term $\mathbf{P}^T\mathbf{f}$ extracts only the elements of $\mathbf{f}$ that correspond to the interpolation indices.
+Thus, at each time step, only $k$ elements $\mathbf{f}$ need to be evaluated.
+The approximation error can be bounded as 
+\begin{equation}
+\|\mathbf{f} - \hat{\mathbf{f}} \| \le \|(\mathbf{P}\mathbf{\Psi})^{-1} \| \epsilon \, ,
+\end{equation}
+where
+\begin{equation*}
+\epsilon \approx \sigma_{k+1} \, .
+\end{equation*}
+Note that $\sigma_{k+1}$ is the $(k+1)th$ singular value coming from the SVD of the function snapshots matrix.
+Full derivation of the error bound is given in Ref.~\cite{chaturantabut2010nonlinear}.
+
+As explained in the previous section, the projection can be performed by computing the term $\mathbf{U}^T \mathbf{\Psi}$ once in an offline stage, while in the online stage, the vector $\boldsymbol{\theta}$ is computed by solving the linear system of dimension $k$ in Eq.~\ref{eq:DEIM coefficients}.
+The key point is that the cost of the online computation depends on the reduced dimension $k$, not the original, high dimension $n$.
+\noindent\begin{minipage}{\textwidth}
+	\renewcommand\footnoterule{}
+	\begin{algorithm}[H]
+		\caption{DEIM}
+		\label{alg:DEIM}
+		\begin{algorithmic}[1]
+			\REQUIRE Snapshots matrix: $\mathbf{X} = [\mathbf{f}_1, \mathbf{f}_2,  ...., \mathbf{f}_m] \in \mathbb{R}^{n\times m}$
+			\ENSURE A reduced space $\mathbf{\Psi}$, set of indices $\mathcal{I}$
+			\STATE $[\mathbf{\Psi}_1, \mathbf{\Psi}_2, ..., \mathbf{\Psi}_k ]$ = POD(${\mathbf{X}}, \epsilon$)\footnote{POD refers to Algorithm \ref{alg:pod}}
+			\STATE $\mathcal{I}_1 = \argmaxH(\abs{\mathbf{\Psi}_1})$, $\mathcal{I}$ = $\{\mathcal{I}_1\}$
+			\STATE $\mathbf{\Psi} = [\mathbf{\Psi}_1]$, $\mathbf{P} =[e_{I_1}]$
+			\FOR {i=2 \TO i=k }
+			\STATE Solve $(\mathbf{P}^T\mathbf{\Psi})\mathbf{c} = \mathbf{P}^T\mathbf{\Psi}_i$;
+			\STATE $\mathcal{I}_i = \argmaxH{\abs{\mathbf{\Psi}_i - \mathbf{\Psi}\mathbf{c}}}$
+			\STATE $\mathcal{I} = \mathcal{I} \cup \mathcal{I}_i$, $\mathbf{P} = \mathbf{P} \cup e_{I_i}$, ${\Psi = \Psi \cup \Psi_i}$
+			\ENDFOR
+		\end{algorithmic}
+	\end{algorithm}
+\end{minipage}
+
+\subsection{Greedy POD}
+A greedy sampling in the parameter space \cite{nguyen2009reduced} can be combined with POD to construct a global subspace that can be used in the framework of parametric ROMs.
+The primary goal is to ensure that the parameter domain of interest (i.e, $\mathbb P$) is efficiently sampled and includes enough information such that it can be used or wide range of parameters including those of higher dimensions.
+To construct this subspace, a training parameters dataset, $P_{train} \subset \mathbb P$, is prepared. 
+The greedy subspace is initialized with the first $r_1$ POD basis computed from a randomly selected sample of the training data.
+Next, this subspace is used to compute the ROM prediction error of the state variable for the rest of the training samples.
+The sample at which the error is worst is selected, and the subspace is enriched by adding the first $r_1$ POD basis computed from the selected sample snapshots.
+Selecting the samples with the worst errors ensures efficient sampling of the parameter space.
+Intuitively, samples that are close to the previously chosen parameter points will have a smaller ROM error.
+On the other hand, one expects that the ROM will fail to give an accurate prediction at samples that are far from the included points in the current subspace.
+Thus, we keep adding new basis vectors until a maximum size of the subspace is reached or a user-specified error tolerance at a reference parameter point $\boldsymbol{\mu}_{\text{ref}}$ is met.
+Note that each time a new basis vector is added, the subspace is orthonormalized.
+Regarding the error criteria based on which a new sample is selected, there are two approaches. 
+Ideally, the true error can be used leading to ``strong POD-greedy'' \cite{benner2017model}.
+Alternatively, an error indicator can be used to alleviate the computational burden associated with evaluating the full-order-model. 
+Here, we used the strong-POD greedy approach. 
+The algorithm steps are shown in Algorithm \ref{alg:greedy pod}. 
+The term $\Delta(\textbf{U},\boldsymbol{\mu}_\text{ref})$  is the error measure using the current reduced subspace at $\boldsymbol{\mu}_\text{ref}$, and $r$ is the maximum size of the greedy basis.
+
+\begin{algorithm}[H]
+
+	\begin{algorithmic}
+
+		\REQUIRE $\epsilon_{tol}, r, r_1, P_{train} \subset \mathbb P$
+
+		\ENSURE A reduced space $\textbf{U}$
+
+		\STATE set n=0
+
+		\WHILE {$\epsilon:= \Delta(\textbf{U}, \boldsymbol{\mu}_\text{ref}) > \epsilon_{tol}$ or $n < r$}
+
+		\STATE $\boldsymbol{\mu} := \argmaxH_{\boldsymbol{\mu}_\in P_{train}} \Delta(\textbf{U}, \boldsymbol{\mu)}$
+
+		\STATE evaluate the FOM at $\boldsymbol{\mu}$, $\textbf Y(\boldsymbol{\mu})$:= $\{\textbf{y}^1, \textbf{y}^2, ..... \textbf{y}^k\}$
+
+		\STATE compute the POD modes of the FOM snapshots, $\{\zeta_1, \zeta_2, ......,\zeta_{r1}\} := \text{POD}(\textbf{Y}(\boldsymbol{\mu}), r_1)$
+
+		\STATE Compute the SVD of $\textbf Y(\mu)$ and keep the first $r_1$ POD modes:$\{\zeta_1, \zeta_2, ......,\zeta_{r1}\}= \text{POD}(\textbf{y}^1, \textbf{y}^2, ..... \textbf{y}^k\}, r_1) $
+
+		\STATE $Z = \{Z, \{\zeta_1, \zeta_2, ....,\zeta_{r1}\}\}$ \text{and set} $n = n+r_1$
+
+		\STATE update the reduced space, $\textbf{U} := \textbf{U} \cup \{\zeta_1, \zeta_2, ..,\zeta_{r1}\} $ and orthonormalize
+
+		\STATE $n:=n+r_1$
+
+		\STATE $ \textbf{compute} ~\epsilon = \Delta(\textbf{U}, \mu_0)$
+
+		\ENDWHILE
+
+	\end{algorithmic}
+
+	\caption{POD-greedy sampling procedures}
+
+	\label{alg:greedy pod}
+
+\end{algorithm}
 
@@
 
-\begin{figure}[H]
-	\centering
-	\begin{subfigure}[b]{0.7\textwidth}
-		\includegraphics[width=1.0\linewidth]{../figures/ss_fom_fast_flux_image.pdf}
-		\caption{Steady state fast flux.}
-		\label{fig:ss fast flux}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.7\textwidth}
-		\includegraphics[width=1.0\linewidth]{../figures/ss_fom_thermal_flux_image.pdf}
-		\caption{Steady state thermal flux.}
-		\label{fig:ss thermal flux}
-	\end{subfigure}
-	\caption{Steady state group flux $(\text{neutrons}.\text{cm}^2/s)$}
-	\label{fig:lra ss flux}
-\end{figure}
+%\begin{figure}[H]
+%	\centering
+%	\begin{subfigure}[b]{0.7\textwidth}
+%		\includegraphics[width=1.0\linewidth]{../figures/ss_fom_fast_flux_image.pdf}
+%		\caption{Steady state fast flux.}
+%		\label{fig:ss fast flux}
+%	\end{subfigure}
+%	\begin{subfigure}[b]{0.7\textwidth}
+%		\includegraphics[width=1.0\linewidth]{../figures/ss_fom_thermal_flux_image.pdf}
+%		\caption{Steady state thermal flux.}
+%		\label{fig:ss thermal flux}
+%	\end{subfigure}
+%	\caption{Steady state group flux $(\text{neutrons}.\text{cm}^2/s)$}
+%	\label{fig:lra ss flux}
+%\end{figure}
 
@@
 	{\raggedright $v_1 = 3\times10^{7} ~\text{cm/sec}. $,  $v_2 = ~3\times10^{5} \text{cm.sec}.$  \par}
-	\caption{Two-group diffusion constants}
+	\caption{Two group constants of the TWIGL benchmark.}
 	\label{tab:twogroup}
@@
 \begin{figure}[h!]
-	\includegraphics[width=1.0\linewidth]{figures/LRA/LRA_singular_values.pdf}
+	\includegraphics[width=1.0\linewidth]{../figures/LRA_singular_values.pdf}
 	\caption{flux normalized singular value.}
@@
 	\centering
-	\includegraphics[width=1.0\linewidth]{figures/LRA/LRA_T_singular_values.pdf}
+	\includegraphics[width=1.0\linewidth]{../figures/LRA_T_singular_values.pdf}
 	\caption{temperature normalized singular value.}
@@
 \begin{figure}[H]
-	\includegraphics[width=1.0\linewidth]{figures/LRA/LRA_L_singular_values.pdf}
+	\includegraphics[width=1.0\linewidth]{../figures/LRA_L_singular_values.pdf}
 	\caption{Operator normalized singular value.}
@@
 For brevity, we show the POD modes with their temporal coefficients of only the $55 \times 55$  grid in Fig.~\ref{fig:lra flux modes}.
-\begin{figure}[H]
-	\centering
-	\begin{subfigure}[b]{0.45\textwidth}
-		\includegraphics[width=1.0\linewidth]{../figures/LRA_fast_modes.pdf}
-		\caption{Fast flux modes.}
-		\label{fig:ss fast flux}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.45\textwidth}
-		\includegraphics[width=1.0\linewidth]{../figures/LRA_thermal_modes.pdf}
-		\caption{Thermal flux modes.}
-		\label{fig:ss thermal flux}
-	\end{subfigure}
-	\caption{Flux POD modes and their temporal coefficient.}
-	\label{fig:lra flux modes}
-\end{figure}
+%\begin{figure}[H]
+%	\centering
+%	\begin{subfigure}[b]{0.45\textwidth}
+%		\includegraphics[width=1.0\linewidth]{../figures/LRA_fast_modes.pdf}
+%		\caption{Fast flux modes.}
+%		\label{fig:ss fast flux}
+%	\end{subfigure}
+%	\begin{subfigure}[b]{0.45\textwidth}
+%		\includegraphics[width=1.0\linewidth]{../figures/LRA_thermal_modes.pdf}
+%		\caption{Thermal flux modes.}
+%		\label{fig:ss thermal flux}
+%	\end{subfigure}
+%	\caption{Flux POD modes and their temporal coefficient.}
+%	\label{fig:lra flux modes}
+%\end{figure}
 Using ROMs with the specifications given in the previous section, the absolute relative error in the predicted powers are computed as shown in Fig.~\ref{fig:deim power error}.
@@
 
+ \bibitem{elzohery-greedyPOD}
+ Elzohery, Rabab and Roberts, Jeremy [Modeling neutronic transients with Galerkin projection onto a greedy-sampled, POD subspace]. Annals of Nuclear Energy; 2021.
+
 \end{thebibliography}

### 2022-02-24 paper/interactnlmsample.tex
updated text

@@
 \usepackage{caption}
-%\usepackage{subcaption}
+\usepackage{subcaption}
+\usepackage{threeparttable}
 \usepackage{tikz}
@@
 
-Modeling and simulation of nuclear reactors is crucial to predict their behavior under different conditions and scenarios and hence ensure reliable design and safety limits.
+Modeling and simulation of reactor physics is crucial to understand the nuclear reactors behavior under different conditions and scenarios and hence ensure reliable design and well established safety limits.
 The mathematical models are described by a set of equations that is challenging to solve analytically due to the geometric complexity of nuclear reactors except for simplified cases.
@@
 
+%--------------------------------------------------------------------------------------------------%
 \section{Methods Overview}
+
 \subsection{POD-Galerkin Projection}\label{class}
@@
 In general, this method involves two main steps.
-First, the state variable $\mathbf{y}$ is expanded in terms of a trial subspace basis, which is the POD space in this case, where each basis vector is weighted by a temporal coefficient
-\begin{equation}
-\mathbf{y} \approx \mathbf{\Phi} \hat{\mathbf{y}}(t) \, ,
+First, a subspace is obtained using the POD which is a widely used reduction technique.
+Commonly, the POD subspace is generated using the snapshots method \cite. 
+A data matrix $\mathbf{Y}$ is constructed by collecting the system solutions at different time instances, then the singular value decomposition (SVD) is computed, i.e $\mathbf{Y} = \mathbf{U}\mathbf{\Sigma}\mathbf{V}$.
+The POD subspace is the one spanned by the first $r$ vector of $\mathbf{U}$, where $r \ll n$.
+There is no general \textit{a priori} rule based on which the rank is chosen; however one can set a threshold $\epsilon$  such that
+\begin{equation}
+\frac{\sum_{i=0}^r S_i}{\sum_{i=0}^m S_i} \ge \epsilon \, ,
+\end{equation}
+where S$i$ is the $i$th singular value.
+For more details the reader might consult \cite{bibid}, 
+Upon obtaining the reduced space, the state variable $\mathbf{y}$ is expanded in terms of its basis, where each basis vector is weighted by a temporal coefficient
+\begin{equation}
+	\mathbf{y} \approx \mathbf{U} \hat{\mathbf{y}}(t) \, ,
 	\label{eq:galerkin expansion}
@@
 where $\mathbf{\hat{y}(t)} \in \mathbb{R}^{r}$ is a vector of the temporal coefficients.
-Second, the system is projected onto a test subspace, which is the same as the trial subspace in the Galerkin projection procedures.
-By multiplying the system on the left by $\mathbf{\Phi}^T$ and making use of the orthogonality of the POD basis (i.e, $\mathbf{\Phi}^T\mathbf{\Phi} = \mathbf{I}$), we end up with 
-\begin{equation}
-\frac{d\mathbf{\hat{y}}}{dt} = \mathbf{A}_r\mathbf{\hat{y}} + \mathbf{\Phi}^T\mathbf{f}(\mathbf{\Phi}\mathbf{\hat{y}}) \qquad \mathbf{\hat{y}}(0) = \mathbf{\Phi}^T\mathbf{y}_0 \, ,
+Second, the system is projected onto a POD subspace by multiplying the system on the left by $\mathbf{\Phi}^T$ and making use of the orthogonality of the POD basis (i.e, $\mathbf{U}^T\mathbf{U} = \mathbf{I}$), we end up with
+\begin{equation}
+	\frac{d\mathbf{\hat{y}}}{dt} = \mathbf{A}_r\mathbf{\hat{y}} + \mathbf{\Phi}^T\mathbf{f}(\mathbf{U}\mathbf{\hat{y}}) \qquad \mathbf{\hat{y}}(0) = \mathbf{U}^T\mathbf{y}_0 \, ,
 	\label{eq:ROM}
@@
 Thus, we are left with  $r$ ODE's instead of $n$ ODE's, which makes the resulting ROM more computationally efficien, and, once it is solved for $\mathbf{\hat{y}}$, the full order solution can be computed by Eq.~\ref{eq:galerkin expansion}.
-Note that the POD basis is chosen here for its optimality property.
-However, different methods have been used in the literature, such as the eigenmodes analysis and the reduced-basis method \cite{rozza2008reduced, hesthaven2016certified, veroy2003posteriori}.
-Moreover, the test basis and the trial basis could be different, in which case the method is called Petrov-Galerkin projection.
-In such cases, unless the test and the trial basis are bi-orthogonal, there will be an additional computational cost associated with inverting the matrix resulting from multiplying the left hand side of Eq.~\ref{eq:FOM} by the test basis.
-
-\subsection{Discrete Impricical Interpolation Method \emph{\LaTeX}}
+
+%--------------------------------------------------------------------------------------------------%
+
+\subsection{Discrete Empirical Interpolation Method}
 
@@
 Recently, the DEIM \cite{chaturantabut2010nonlinear} was proposed to approximate the non-linearity in model order reduction.
-The method is a discrete variant of the Empirical Interpolation Method (EIM) \cite{barrault2004empirical} that was originally proposed to approximate
-non-affine coefficient functions using a reduced-basis expansion to facilitate the online/offline decomposition in finite element methods.
-The DEIM is proposed for the same goal for different discretizations of the full-order model.
+%The method is a discrete variant of the Empirical Interpolation Method (EIM) \cite{barrault2004empirical} that was originally proposed to approximate
+%non-affine coefficient functions using a reduced-basis expansion to facilitate the online/offline decomposition in finite element methods.
+The DEIM is proposed to facilitate the online/offline decomposition of ROMs.
 The method relies on two main ingredients: (1) a reduced space that approximates the nonlinear function, and (2) a set of spatial interpolation indices.
@@
 The key point is that the cost of the online computation depends on the reduced dimension $k$, not the original, high dimension $n$.
+The matrix version of the DEIM (MDEIM) is suggested in \cite{carlberg2012efficient, benner2015survey} to approximate parameter/time-dependent operators.
+Consider a parameterized matrix $\mathbf{A}(\boldsymbol{\mu}) \in \mathbb{R}^{n\times n}$, the goal is to find a decomposition similar to Eq.~\ref{Eq:matrix decomposition} so that an offline-online ROM splitting is attainable.
+The DEIM procedures can be exploited to find such decomposition. First, the matrix can be cast in a vector form by stacking all of its columns in one vector $\mathbf{a}(\mu) \in \mathbb{R}^{n^2}$.
+This vector can be treated in the same exact way as the function $\mathbf{f}(t)$ in the previous section, i.e, $\mathbf{a}(\mu) = \mathbf{\Psi}\boldsymbol{\theta}(\mu)$.
+Snapshots of the serialized matrix are collected at different parameter values and the reduced subspace $\mathbf{\Psi}$ and the interpolation indices are computed following algorithm \ref{alg:DEIM}.
+Again, the corresponding coefficients are obtained by solving Eq.~\ref{eq:DEIM coefficients}. 
+Next, each vector in $\mathbf{\Psi}$ can be mapped back to an $n \times n$ matrix, i.e, $\textbf{A}_i$.
+Hence, the matrix is approximated as $\mathbf{\hat{A}}(t)=\sum_{i=0}^k \theta_i(t) \mathbf{A}_i$ and the projection term is computed as in Eq.~\ref{Eq:deim matrix projection}.
+As pointed out in Ref.\cite{negri2015efficient}, the Weyl\textendash Mirsky theorem \cite{weyl1912asymptotische} ensures that the singular values of the approximated matrix approach that of the original as $k$ increases
+\begin{equation}
+	|\sigma_i - \hat{\sigma_i}  |\ \le \|\mathbf{A} - \hat{\mathbf{A}}\|_\text{F}
+\end{equation}
+where $\sigma_i$ and $\hat{\sigma_i}$ denote the $i$th singular value of $\mathbf{A}$ and $\hat{\mathbf{A}}$ respectively.
+Moreover, some properties of the original matrix such as positive definiteness can be preserved \cite{carlberg2015preserving}, if necessary, by imposing some constrains to the problem in Eq.~\ref{eq:DEIM coefficients}.
+
+%In the practical implementations, the method efficiency can be improved, as suggested in Ref. \cite{negri2015efficient}.
+%First, the matrix $\mathbf{A}$ is, generally, largely sparse, which leads to a snapshots matrix that is sparse, too.
+%Consequently, it is more convenient to store only the nonzero elements ($nz$) in $\mathbf{a}$, 
+%which should be appreciably more efficient in terms of memory and computational expense.
+%In addition, to obtain the expansion coefficients ($\boldsymbol{\theta}$), the term $\mathbf{P}^T\mathbf{a(\tau)}$ needs to be computed at each new parameter value.
+%In fact, this term only extracts the elements of $\mathbf{a(\tau)}$ that corresponds to the selected  interpolation indices.
+In the offline stage, a mapping can be done between these interpolation indices and the corresponding row-column pairs in $\mathbf{A}$.
+When the matrix is formed in the online stage, only these entries are evaluated by restricting a \textit{for loop } over these row-column pairs, leading to more reduction in the computational cost.
+
 \noindent\begin{minipage}{\textwidth}
@@
 \subsection{Greedy POD}
+
 A greedy sampling in the parameter space \cite{nguyen2009reduced} can be combined with POD to construct a global subspace that can be used in the framework of parametric ROMs.
@@
 
-\section{Benchmark Desription}
-The LRA benchmark employs two energy groups and two delayed precursors and represents a 2-D quarter-core, BWR model subject to a control-rod ejection with adiabatic heating \cite{anl}.
-Schematic layout of the problem is shown in Fig.~\ref{fig:lra core}, where region numbers indicate different materials and region R is the ejected rod.
+%-----------------------------------------------------------------------------------------------------%
+\section{Application}
+
+\subsection{Time Dependent Diffusion Equation}
+\label{sec:fom}
+The time dependent diffusion equation was used as the mathematical model describing the neutronic transient in a nuclear reactor, i.e FOM and for which a an approximate ROM is sought.
+It is represented as
+\begin{equation}
+	\begin{split}
+	\frac{1}{v_g} \frac{\partial\phi_g}{\partial t} &= 
+	\nabla. D_g\nabla\phi_g - \Sigma_{tg}\phi_g + \sum_{g^\prime=1}^{G}{\Sigma_{sg^\prime g}}\phi_{g^\prime} \\
+	&+ \chi_g(1-\beta)\sum_{g^\prime = 1}^{G}\nu\Sigma_{fg^\prime}\phi_{g^\prime}  
+	+ \chi_g\sum_{i=1}^{P} \lambda_i C_i \, ,
+	\end{split}
+	\label{time_diff}
+\end{equation}
+where 
+\begin{equation*}
+	\frac{\partial C_i}{\partial t} = -\lambda_i C_i + \beta_i \sum_{g^\prime=1}^{G} \nu\Sigma_{fg^\prime} \phi_{g^\prime} \, ,
+\end{equation*}
+and $\phi_g$, $D_g$, $\Sigma_{ag}$, $\nu\Sigma_{fg}$ and $v_g$ are the neutron flux, diffusion coefficient, the absorption cross section, the production cross section and the average neutron velocity in group g, respectively.
+$\Sigma_{sg^\prime g}$ is the scattering cross section from group $g^\prime$ to group $g$
+and $\chi_g$ is the probability that a fission neutron will be born in group $g$.
+$C_i$ is the $i$th precursor concentration, $\beta_i$ is the fraction of delayed neutrons in group $i$, $\lambda_i$ is the $i$th group decay constant.
+The system can be represented compactly in a matrix form as 
+\begin{equation}
+\frac{\partial{y}(r, t)}{\partial{t}} = \mathcal{A}{y}(r, t) \, ,
+\end{equation}
+where the stacked unknowns are
+\begin{equation*}
+	{y} = 
+	\begin{pmatrix}
+	\phi_1(r, t) \\
+	\vdots \\
+	\phi_G(r, t)  \\
+	{C}_1(r, t) \\
+	\vdots \\
+	{C}_I(r, t) \\
+	\end{pmatrix} \, .
+\end{equation*}
+
+%\begin{equation*}
+%\mathcal{A} = \left(\begin{array}{@{}c|c@{}}
+%\begin{matrix}
+%v_1(\nabla \cdot D_1\nabla +\Sigma_{11}) & v_1\Sigma_{12} & \hdots  &v_1\Sigma_{1G} \\
+%v_2\Sigma_{21}        &    v_2(\nabla\cdot D_2\nabla +\Sigma_{22})            & \hdots  &v_2\Sigma_{2G} \\
+%\vdots   &   \vdots   &  \ddots  &\vdots  \\
+%v_G\Sigma_{G1}        &  v_G\Sigma_{G2} & \hdots &  v_G(\nabla \cdot D_G\nabla +\Sigma_{GG})     \\
+%\end{matrix}
+%&\begin{matrix}
+%v_1 f_{11} & \hdots &   v_1 f_{1I} \\
+%\vdots   & \ddots & \vdots \\
+%v_G f_{G1} & \hdots &   v_G f_{GI}
+%\end{matrix}
+%\\
+%\hline
+%\begin{matrix}
+%p_{11} &  &  & p_{12} & & & & \hdots  &   & p_{1G} \\
+%\vdots &  &  & & \ddots & & & \vdots&   & \vdots \\
+%p_{I1} &  &  & p_{I2} &  &   & & \hdots&  & p_{IG} 
+%\end{matrix}
+%&
+%\begin{matrix}
+%-\lambda_1 & \hdots & 0 \\
+%\vdots & \ddots  &  \vdots \\
+%0  &  \hdots  & -\lambda_I
+%\end{matrix}
+%\end{array}\right)
+%\end{equation*}
+%where 
+%\begin{subequations}
+%	\begin{equation*}
+%	\Sigma{gg^\prime} = (1 -\beta)\chi_g\nu\Sigma{fg^\prime} + \Sigma_{s_{gg^\prime}} \, ,
+%	\end{equation*}
+%	\begin{equation*}
+%	f_{ig^\prime} = \chi_g\lambda_i \, ,
+%	\end{equation*}
+%\end{subequations}
+%\vspace{-2 pt}
+%and
+%\vspace{-2 pt}
+%\begin{equation*}
+%p_{ig} = \beta_i \nu\Sigma_{fg} \, .
+%\end{equation*}
+Upon spatial discretization, the system of ODEs can be compactly represented in a block matrix form as  
+\begin{equation}
+	\frac{d\mathbf{y}(t)}{dt} = \mathbf{A}\mathbf{y}(t) \, ,
+	\label{eq:transient fom}
+\end{equation}
+where $\mathbf{y}\in\mathbb{R}^{N}$ is stacked vector of the flux and the precursors concentration, $\mathbf{A}\in\mathbb{R}^{N\times N}$ and $N = (I + G)\times n$ with $n$ is the number of spatial unknowns arising from discretization.
+The discretized block matrix $\mathbf{A}$ is written as 
+\begin{equation}
+	\mathbf{A} =  \left(\begin{array}{@{}c|c@{}}
+	\mathbf{L} & \mathbf{D} \\
+	\hline
+	\mathbf{F} & \mathbf{P}
+	\end{array}\right) \, .
+\end{equation} 
+where $\mathbf{L} \in \mathbb{R}^{(n\times G)\times (n\times G)}$ represents the diffusion operator, $\mathbf{D} \in \mathbb{R}^{(n\times G)\times (n\times I)}$ represents the delayed neutrons production operator , $\mathbf{P} \in \mathbb{R}^{(n\times I)\times ((n\times G)}$ represents the precursors loss operator and $\mathbf{F}\in \mathbb{R}^{(n\times I)\times ((n\times I)}$ represents the precursors production operator.
+%Thus, the system in Eq.~\ref{eq:transient fom} is the full-order model and it can be solved using a suitable time-scheme.
+%However, it is expensive to solve such systems for fine spatial and time grids, since a linear system of a size proportional to the spatial discretization has to be solved for each time step.
+%Hence, a reduced-order model to approximate it is justified.
+
+%--------------------------------------------------------------------------------------%
+\subsection{Benchmark Desription}
+
+The LRA benchmark employs two energy groups and two delayed precursor groups and represents a 2-D quarter-core, BWR model subject to a control-rod ejection with adiabatic heating \cite{anl}.
+A schematic layout of the problem is shown in Fig.~\ref{fig:lra core}, where region numbers indicate different materials and region R is the ejected rod.
 %To produce time-dependent snapshots, the deterministic transport code Detran\footnote{https://github.com/robertsj/libdetran} was used to solve the time-dependent diffusion equations.
@@
 	\begin{tikzpicture}[scale=0.6]
+
 	\begin{scope}<->;
@@
 \end{figure}
-The transient is initiated by a control rod ejection with constant velocity over a period of 2 seconds leading to a super-critical prompt transient, in which the power increased by about 10 orders of magnitude in a very short time.
-The control rod movement was simulated by changing the thermal absorption cross section of the control rod material.
-\begin{equation}
-\sigma 
-\end{equation}
-
-Thermal feedback is incorporated through adiabatic fuel heat-up defined by
+The transient is initiated by a control rod ejection with constant velocity over a period of 2 seconds leading to a super-critical, prompt transient, in which the power increases by about 10 orders of magnitude in a very short time.
+The control rod movement is represented by changing the thermal absorption cross section of the control rod material.
+In this application, the two-group diffusion equation represented in sec.\ref{sec:fom}, is coupled with thermal feedback through adiabatic fuel heat-up defined by
 \begin{equation}
@@
 where $\Sigma_{f_i}$ is the fission cross section of group $i$, $T$ is the temperature, $\Sigma_{a1}$ is the fast absorption cross section and $T_0$ is the initial temperature which is $300 $ K,
-$\alpha = 3.83\times 10^{-11}~\text{K}.\text{cm}^3$ and $\gamma = 3.034\times 10^{-3} ~\text{K}^{-0.5}$.\\
-The power is computed as
+$\alpha = 3.83\times 10^{-11}~\text{K}~\text{cm}^3$ and $\gamma = 3.034\times 10^{-3} ~\text{K}^{-0.5}$.
+The power local is computed as
 \begin{equation}
@@
 \end{equation}
-where $\kappa = 3.204\times 10^{-11}~ \text{Ws/fission}$.
+where $\kappa = 3.204\times 10^{-11}~ \text{W/fission}$.
 The model was implemented in the deterministic transport code Detran~\cite{roberts2014advanced}.
-A mesh-centered, finite-volume discretization was used for the spatial dicretization, while a first-order, backward-difference temporal discretization was used with a fixed 0.001 s step size.  
-The initial condition for the transient was computed by solving the steady-state equation, for which the $k_{\text{eff}}$ was found to be 0.9975.
-Note that at each time step the fast absorption cross section is a function of the solution itself, hence a fixed point non-linear iteration is employed.
-A convergence criteria is used such that the $\text{L}_2$ norm  of the relative flux error between two consecutive iterations is less than $1\times 10^{-6}$,
-
+A mesh-centered, finite-difference discretization was used in space, while a first-order, backward-difference temporal discretization was used with a fixed 0.001 s step size.  
+The initial condition for the transient was computed by solving the steady-state equation, for which $k_{\text{eff}}$ was found to be 0.9975.
+Note that at each time step the fast absorption cross section is a function of the solution itself.
+The convergence criterion used to reduce the $\text{L}_2$ norm  of the relative flux error between two consecutive iterations to less than $1\times 10^{-6}$, or
 \begin{equation}
 	\|\frac{\mathbf{\Phi}^{i+1} - \mathbf{\Phi}^{i}} {\mathbf{\Phi}^i}\| \le  1\times 10^{-6} \, ,
+	\label{eq:convergance criteria} 
 \end{equation}
@@
 The transient was calculated for 3.0 seconds.
-Figure~\ref{fig:lra fom power} shows the reference full-order model power along with the core average temperature, while Figure \ref{fig:lra ss flux} shows the steady state group flux distribution.
-This reference solution is not numerically converged in either the space or the time but it represents the simulation response that one wish to approximate.
+Figure~\ref{fig:lra fom power} shows the reference full-order model power along with the core average temperature, while Figure \ref{fig:lra ss flux} shows the steady-state group flux distribution.
+This reference solution is not necessarily numerically converged in either space or time but represents the simulation response that one wishes to approximate.
 \begin{figure}[h!]
@@
 %	\end{subfigure}
-%	\caption{Steady state group flux $(\text{neutrons}.\text{cm}^2/s)$}
+%	\caption{Steady state group flux $(\text{neutrons} ~\text{cm}^2/s)$}
 %	\label{fig:lra ss flux}
@@
 
-\begin{table}[h!]
+\begin{table}[H]
+	\begin{threeparttable}	
 		\centering
-	\begin{tabular}{l|l|l|l| l|l}
-		material & group  & $D$ (cm) & $\Sigma_{a} ~ (\text{cm}^{-1})$ & $\Sigma_{s2\gets 1}~ (\text{cm}^{-1})$ & $\nu\Sigma_{f}~ (\text{cm}^{-1})$ \\\hline
-		\multirow{2}{*}{1}& 1   & 1.255  &  0.008252   &  \multirow{2}{*}{0.02533} & 0.004602 \\	
-		& 2   & 0.211  &  0.1003     &           & 0.1091  \\
+		\begin{tabular}{c|l|l|l|l|l}
+			material & group  & $D$ (cm) & $\Sigma_{a} ~ (\text{cm}^{-1})$ & $\Sigma_{s2\gets 1}~ (\text{cm}^{-1})$ & $\nu\Sigma_{f}~ (\text{cm}^{-1})$ \\
 			\hline
-
-		\multirow{2}{*}{2}& 1   & 1.268  &  0.007181    & \multirow{2}{*}{0.02767} & 0.004609 \\	
-		& 2   & 0.1902 &  0.07047     &           &  0.08675\\
+			\multirow{2}{*}{1}& 1   & 1.255  &  0.008252   & 0.004602 &  \multirow{2}{*}{0.02533} 	\\
+			& 2   & 0.211  &  0.1003     &  0.1091  &  \\
 			\hline
-
-		\multirow{2}{*}{3}& 1   & 1.259  &  0.008002    & \multirow{2}{*}{0.02617}     & 0.004663 \\	
-		& 2   & 0.2091 &  0.08344     &    &    0.1021 \\
+			\multirow{2}{*}{2}& 1   & 1.268  &  0.007181    & 0.004609  & \multirow{2}{*}{0.02767}  \\	
+			& 2   & 0.1902 &  0.07047     & 0.08675   &  \\
 			\hline
-		\multirow{2}{*}{4}& 1   & 1.259  &  0.008002    & \multirow{2}{*}{0.02617}  &  0.004663 \\	
-		& 2   & 0.2091 &  0.073324    &           &  0.1021   \\
+
+			\multirow{2}{*}{3}& 1   & 1.259  &  0.008002    & 0.004663 & \multirow{2}{*}{0.02617} \\	
+			& 2   & 0.2091 &  0.08344     &   0.1021 &                          \\
 			\hline
-		\multirow{2}{*}{5}& 1   & 1.257  &  0.0006034   &  \multirow{2}{*}{0.04754}  & 0.0 \\	
-		& 2   & 0.1592 &   0.01911    &        & 0.0 \\
+			\multirow{2}{*}{4}& 1   & 1.259  &  0.008002    & 0.004663 &  \multirow{2}{*}{0.02617} \\	
+			& 2   & 0.2091 &  0.073324    & 0.1021   &                           \\
+			\hline
+			\multirow{2}{*}{5}& 1   & 1.257  &  0.0006034   &   0.0    & \multirow{2}{*}{0.04754}\\	
+			& 2   & 0.1592 &   0.01911    &   0.0    &  \\
 			\hline
 		\end{tabular}
-	{\raggedright $v_1 = 3\times10^{7} ~\text{cm/sec}. $,  $v_2 = ~3\times10^{5} \text{cm.sec}.$  \par}
-	\caption{Two group constants of the TWIGL benchmark.}
-	\label{tab:twogroup}
+		\begin{tablenotes}
+			\item $v_1 = 3\times10^{7} ~\text{cm/s} $,  $v_2 = ~3\times10^{5} \text{cm/s}.$.
+		\end{tablenotes}
+	\end{threeparttable}
+	\caption{Two group constants of the LRA benchmark.}
 \end{table}
 
-\begin{table}[h!]
+\begin{table}[H]
 	\centering
@@
 	\end{tabular}
-	\caption{Delayed neutron data.}
+	\caption{Delayed neutron data of the LRA benchmark.}
 	\label{tab:precursor data}
@@
 
-\section{ROM}
+%--------------------------------------------------------------------------------------------------------------%
+
+\section{ROM }
 \subsection{ROM Implementation}
@@
 
-\subsection{The list of references}
-
-References should be listed at the end of the main text in the order in which they are first cited in the text.
+%\subsection{The list of references}
+%
+%References should be listed at the end of the main text in the order in which they are first cited in the text.
 The following list shows some sample references prepared in the Taylor \& Francis NLM style.
-
-\begin{thebibliography}{99}
-
-\bibitem{Jen05}%1
-Jenkins~PF. Making sense of the chest x-ray: a hands-on guide. New York (NY):
-  Oxford University Press; 2005.
-
-\bibitem{Sch02}%2
-Schott~J, Priest~J. Leading antenatal classes: a practical guide. 2nd ed.
-  Boston (MA): Books for Midwives; 2002.
-
-\bibitem{Wen95}%3
-Wenger~NK, Sivarajan~Froelicher~E, Smith~LK, et~al. Cardiac rehabilitation.
-  Rockville (MD): Agency for Health Care Policy and Research (US); 1995.
-
-\bibitem{Sha78}%4
-Shakelford~RT. Surgery of the alimentary tract. Philadelphia (PA): W.B.
-  Saunders; 1978. Chapter 2, Esophagoscopy; p. 29--40.
-
-\bibitem{AG98}%5
-Ambudkar~SV, Gottesman~MM, editors. {ABC} transporters: biomedical, cellular,
-  and molecular aspects. San Diego (CA): Academic Press; 1998. (Methods in
-  enzymology; vol. 292).
-
-\bibitem{Smi75}%6
-Smith~CE. The significance of mosquito longevity and blood-feeding behaviour in
-  the dynamics of arbovirus infections. Med Biol. 1975;53:288--294.
-
-\bibitem{Men05}%7
-Meneton~P, Jeunemaitre~X, de~Wardener~HE, et~al. Links between dietary salt
-  intake, renal salt handling, blood pressure, and cardiovascular diseases.
-  Physiol Rev. 2005 Apr;85:679--715.
-
-\bibitem{DCK03}%8
-Dostorovsky~JO, Carr~DB, Koltzenburg~M, editors. Proceedings of the 10th World
-  Congress on Pain; 2002 Aug~17--22; San Diego, CA. Seattle: IASP Press; c2003.
-
-\bibitem{Hor98}%9
-Horrobin~DF, Lampinskas~P. The commercial development of food plants used as
-  medicines. In: Prendergast~HD, Etkin~NL, Harris~DR, et~al., editors. Plants
-  for food and medicine. Proceedings of the Joint Conference of the Society for
-  Economic Botany and the International Society for Ethnopharmacology; 1996
-  Jul~1--6; London. Kew (UK): Royal Botanic Gardens; 1998. p. 75--81.
-
-\bibitem{Ant03}%10
-Antani~S, Long~LR, Thoma~GR, et~al. Anatomical shape representation in spine
-  x-ray images. Paper presented at: VIIP 2003. Proceedings of the 3rd IASTED
-  International Conference on Visualization, Imaging and Image Processing;
-  2003 Sep~8--10; Benalmadena, Spain.
-
-\bibitem{Zha05}%11
-Zhao~C. Development of nanoelectrospray and application to protein research and
-  drug discovery [dissertation]. Buffalo (NY): State University of New York at
-  Buffalo; 2005.
-
-\bibitem{Rog05}%12
-Roguskie~JM. The role of \emph{Pseudomonas aeruginosa} 1244 pilin glycan in
-  virulence [master's thesis]. [Pittsburgh (PA)]: Duquesne University; 2005.
-
-\bibitem{SRW05}%13
-Savage~E, Ramsay~M, White~J, et~al. Mumps outbreaks across England and Wales
-  in 2004: Observational study. BMJ. 2005;330(7500):1119--1120 [cited 2005
-  May~31]; Available from: http://bmj.bmjjournals.com/cgi/reprint/330/7500/1119.
-
-\bibitem{Gau05}%14
-Gaul~G. When geography influences treament options. Washington Post (Maryland
-  Ed.). 2005 Jul~24;Sect.~A:12 (col.~1).
-
-\bibitem{BGC04}%15
-Berrino~F, Gatta~G, Crosignani~P. [Case-control evaluation of screening
-  efficacy]. Epidemiol Prev. 2004 Nov--Dec;28:354--359. Italian.
-
-\bibitem{PI51}%16
-Piaget~J, Inhelder~B. La gen{\`e}se de l'id{\'e}e de hasard chez l'enfant
-  [The origin of the idea of chance in the child]. Paris: Presses
-  Universitaires de France; 1951.
-
- \bibitem{elzohery-greedyPOD}
- Elzohery, Rabab and Roberts, Jeremy [Modeling neutronic transients with Galerkin projection onto a greedy-sampled, POD subspace]. Annals of Nuclear Energy; 2021.
-
-\end{thebibliography}
-\bigskip
-\noindent This was produced by typing:
-\begin{verbatim}
-\begin{thebibliography}{99}
-
-\bibitem{Jen05}%1
-Jenkins~PF. Making sense of the chest x-ray: a hands-on guide. New York
- (NY): Oxford University Press; 2005.
-
-\bibitem{Sch02}%2
-Schott~J, Priest~J. Leading antenatal classes: a practical guide. 2nd
- ed. Boston (MA): Books for Midwives; 2002.
-
-\bibitem{Wen95}%3
-Wenger~NK, Sivarajan~Froelicher~E, Smith~LK, et~al. Cardiac
- rehabilitation. Rockville (MD): Agency for Health Care Policy and
- Research (US); 1995.
-
-\bibitem{Sha78}%4
-Shakelford~RT. Surgery of the alimentary tract. Philadelphia (PA):
- W.B. Saunders; 1978. Chapter 2, Esophagoscopy; p. 29--40.
-
-\bibitem{AG98}%5
-Ambudkar~SV, Gottesman~MM, editors. {ABC} transporters: biomedical,
- cellular, and molecular aspects. San Diego (CA): Academic Press; 1998.
- (Methods in enzymology; vol. 292).
-
-\bibitem{Smi75}%6
-Smith~CE. The significance of mosquito longevity and blood-feeding
- behaviour in the dynamics of arbovirus infections. Med Biol.
- 1975;53:288--294.
-
-\bibitem{Men05}%7
-Meneton~P, Jeunemaitre~X, de~Wardener~HE, et~al. Links between dietary
- salt intake, renal salt handling, blood pressure, and cardiovascular
- diseases. Physiol Rev. 2005 Apr;85:679--715.
-
-\bibitem{DCK03}%8
-Dostorovsky~JO, Carr~DB, Koltzenburg~M, editors. Proceedings of the
- 10th World Congress on Pain; 2002 Aug~17--22; San Diego, CA. Seattle:
- IASP Press; c2003.
-
-\bibitem{Hor98}%9
-Horrobin~DF, Lampinskas~P. The commercial development of food plants
- used as medicines. In: Prendergast~HD, Etkin~NL, Harris~DR, et~al.,
- editors. Plants for food and medicine. Proceedings of the Joint
- Conference of the Society for Economic Botany and the International
- Society for Ethnopharmacology; 1996 Jul~1--6; London. Kew (UK): Royal
- Botanic Gardens; 1998. p. 75--81.
-
-\bibitem{Ant03}%10
-Antani~S, Long~LR, Thoma~GR, et~al. Anatomical shape representation in
- spine x-ray images. Paper presented at: VIIP 2003. Proceedings of the
- 3rd IASTED International Conference on Visualization, Imaging and
- Image Processing; 2003 Sep~8--10; Benalmadena, Spain.
-
-\bibitem{Zha05}%11
-Zhao~C. Development of nanoelectrospray and application to protein
- research and drug discovery [dissertation]. Buffalo (NY): State
- University of New York at Buffalo; 2005.
-
-\bibitem{Rog05}%12
-Roguskie~JM. The role of \emph{Pseudomonas aeruginosa} 1244 pilin
- glycan in virulence [master's thesis]. [Pittsburgh (PA)]: Duquesne
- University; 2005.
-
-\bibitem{SRW05}%13
-Savage~E, Ramsay~M, White~J, et~al. Mumps outbreaks across England and
- Wales in 2004: Observational study. BMJ. 2005;330(7500):1119--1120
- [cited 2005 May 31]; Available from:
- http://bmj.bmjjournals.com/cgi/reprint/330/7500/1119.
-
-\bibitem{Gau05}%14
-Gaul~G. When geography influences treament options. Washington Post
- (Maryland Ed.). 2005 Jul~24;Sect.~A:12 (col.~1).
-
-\bibitem{BGC04}%15
-Berrino~F, Gatta~G, Crosignani~P. [Case-control evaluation of screening
- efficacy]. Epidemiol Prev. 2004 Nov--Dec;28:354--359. Italian.
-
-\bibitem{PI51}%16
-Piaget~J, Inhelder~B. La gen{\`e}se de l'id{\'e}e de hasard chez
- l'enfant [The origin of the idea of chance in the child]. Paris:
- Presses Universitaires de France; 1951.
-
-\end{thebibliography}
-\end{verbatim}
-\bigskip
-\noindent Each entry takes the form:
-\begin{verbatim}
-\bibitem{key}%n Bibliography entry
-\end{verbatim}
-where `\texttt{key}' is the tag that is to be used as an argument for the \verb"\cite{}" commands in the text of the article and `\texttt{Bibliography entry}' is the material that is to appear in the list of references, suitably formatted.
+%
+%\bibliography{references}
+%
+%\begin{thebibliography}{99}
+%
+%\bibitem{Jen05}%1
+%Jenkins~PF. Making sense of the chest x-ray: a hands-on guide. New York (NY):
+%  Oxford University Press; 2005.
+%
+%\bibitem{Sch02}%2
+%Schott~J, Priest~J. Leading antenatal classes: a practical guide. 2nd ed.
+%  Boston (MA): Books for Midwives; 2002.
+%
+%\bibitem{Wen95}%3
+%Wenger~NK, Sivarajan~Froelicher~E, Smith~LK, et~al. Cardiac rehabilitation.
+%  Rockville (MD): Agency for Health Care Policy and Research (US); 1995.
+%
+%\bibitem{Sha78}%4
+%Shakelford~RT. Surgery of the alimentary tract. Philadelphia (PA): W.B.
+%  Saunders; 1978. Chapter 2, Esophagoscopy; p. 29--40.
+%
+%\bibitem{AG98}%5
+%Ambudkar~SV, Gottesman~MM, editors. {ABC} transporters: biomedical, cellular,
+%  and molecular aspects. San Diego (CA): Academic Press; 1998. (Methods in
+%  enzymology; vol. 292).
+%
+%\bibitem{Smi75}%6
+%Smith~CE. The significance of mosquito longevity and blood-feeding behaviour in
+%  the dynamics of arbovirus infections. Med Biol. 1975;53:288--294.
+%
+%\bibitem{Men05}%7
+%Meneton~P, Jeunemaitre~X, de~Wardener~HE, et~al. Links between dietary salt
+%  intake, renal salt handling, blood pressure, and cardiovascular diseases.
+%  Physiol Rev. 2005 Apr;85:679--715.
+%
+%\bibitem{DCK03}%8
+%Dostorovsky~JO, Carr~DB, Koltzenburg~M, editors. Proceedings of the 10th World
+%  Congress on Pain; 2002 Aug~17--22; San Diego, CA. Seattle: IASP Press; c2003.
+%
+%\bibitem{Hor98}%9
+%Horrobin~DF, Lampinskas~P. The commercial development of food plants used as
+%  medicines. In: Prendergast~HD, Etkin~NL, Harris~DR, et~al., editors. Plants
+%  for food and medicine. Proceedings of the Joint Conference of the Society for
+%  Economic Botany and the International Society for Ethnopharmacology; 1996
+%  Jul~1--6; London. Kew (UK): Royal Botanic Gardens; 1998. p. 75--81.
+%
+%\bibitem{Ant03}%10
+%Antani~S, Long~LR, Thoma~GR, et~al. Anatomical shape representation in spine
+%  x-ray images. Paper presented at: VIIP 2003. Proceedings of the 3rd IASTED
+%  International Conference on Visualization, Imaging and Image Processing;
+%  2003 Sep~8--10; Benalmadena, Spain.
+%
+%\bibitem{Zha05}%11
+%Zhao~C. Development of nanoelectrospray and application to protein research and
+%  drug discovery [dissertation]. Buffalo (NY): State University of New York at
+%  Buffalo; 2005.
+%
+%\bibitem{Rog05}%12
+%Roguskie~JM. The role of \emph{Pseudomonas aeruginosa} 1244 pilin glycan in
+%  virulence [master's thesis]. [Pittsburgh (PA)]: Duquesne University; 2005.
+%
+%\bibitem{SRW05}%13
+%Savage~E, Ramsay~M, White~J, et~al. Mumps outbreaks across England and Wales
+%  in 2004: Observational study. BMJ. 2005;330(7500):1119--1120 [cited 2005
+%  May~31]; Available from: http://bmj.bmjjournals.com/cgi/reprint/330/7500/1119.
+%
+%\bibitem{Gau05}%14
+%Gaul~G. When geography influences treament options. Washington Post (Maryland
+%  Ed.). 2005 Jul~24;Sect.~A:12 (col.~1).
+%
+%\bibitem{BGC04}%15
+%Berrino~F, Gatta~G, Crosignani~P. [Case-control evaluation of screening
+%  efficacy]. Epidemiol Prev. 2004 Nov--Dec;28:354--359. Italian.
+%
+%\bibitem{PI51}%16
+%Piaget~J, Inhelder~B. La gen{\`e}se de l'id{\'e}e de hasard chez l'enfant
+%  [The origin of the idea of chance in the child]. Paris: Presses
+%  Universitaires de France; 1951.
+%  
+% \bibitem{elzohery-greedyPOD}
+% Elzohery, Rabab and Roberts, Jeremy [Modeling neutronic transients with Galerkin projection onto a greedy-sampled, POD subspace]. Annals of Nuclear Energy; 2021.
+
+%\end{thebibliography}
+%\bigskip
+%\noindent This was produced by typing:
+%\begin{verbatim}
+%\begin{thebibliography}{99}
+%
+%\bibitem{Jen05}%1
+%Jenkins~PF. Making sense of the chest x-ray: a hands-on guide. New York
+% (NY): Oxford University Press; 2005.
+%
+%\bibitem{Sch02}%2
+%Schott~J, Priest~J. Leading antenatal classes: a practical guide. 2nd
+% ed. Boston (MA): Books for Midwives; 2002.
+%
+%\bibitem{Wen95}%3
+%Wenger~NK, Sivarajan~Froelicher~E, Smith~LK, et~al. Cardiac
+% rehabilitation. Rockville (MD): Agency for Health Care Policy and
+% Research (US); 1995.
+%
+%\bibitem{Sha78}%4
+%Shakelford~RT. Surgery of the alimentary tract. Philadelphia (PA):
+% W.B. Saunders; 1978. Chapter 2, Esophagoscopy; p. 29--40.
+%
+%\bibitem{AG98}%5
+%Ambudkar~SV, Gottesman~MM, editors. {ABC} transporters: biomedical,
+% cellular, and molecular aspects. San Diego (CA): Academic Press; 1998.
+% (Methods in enzymology; vol. 292).
+%
+%\bibitem{Smi75}%6
+%Smith~CE. The significance of mosquito longevity and blood-feeding
+% behaviour in the dynamics of arbovirus infections. Med Biol.
+% 1975;53:288--294.
+%
+%\bibitem{Men05}%7
+%Meneton~P, Jeunemaitre~X, de~Wardener~HE, et~al. Links between dietary
+% salt intake, renal salt handling, blood pressure, and cardiovascular
+% diseases. Physiol Rev. 2005 Apr;85:679--715.
+%
+%\bibitem{DCK03}%8
+%Dostorovsky~JO, Carr~DB, Koltzenburg~M, editors. Proceedings of the
+% 10th World Congress on Pain; 2002 Aug~17--22; San Diego, CA. Seattle:
+% IASP Press; c2003.
+%
+%\bibitem{Hor98}%9
+%Horrobin~DF, Lampinskas~P. The commercial development of food plants
+% used as medicines. In: Prendergast~HD, Etkin~NL, Harris~DR, et~al.,
+% editors. Plants for food and medicine. Proceedings of the Joint
+% Conference of the Society for Economic Botany and the International
+% Society for Ethnopharmacology; 1996 Jul~1--6; London. Kew (UK): Royal
+% Botanic Gardens; 1998. p. 75--81.
+%
+%\bibitem{Ant03}%10
+%Antani~S, Long~LR, Thoma~GR, et~al. Anatomical shape representation in
+% spine x-ray images. Paper presented at: VIIP 2003. Proceedings of the
+% 3rd IASTED International Conference on Visualization, Imaging and
+% Image Processing; 2003 Sep~8--10; Benalmadena, Spain.
+%
+%\bibitem{Zha05}%11
+%Zhao~C. Development of nanoelectrospray and application to protein
+% research and drug discovery [dissertation]. Buffalo (NY): State
+% University of New York at Buffalo; 2005.
+%
+%\bibitem{Rog05}%12
+%Roguskie~JM. The role of \emph{Pseudomonas aeruginosa} 1244 pilin
+% glycan in virulence [master's thesis]. [Pittsburgh (PA)]: Duquesne
+% University; 2005.
+%
+%\bibitem{SRW05}%13
+%Savage~E, Ramsay~M, White~J, et~al. Mumps outbreaks across England and
+% Wales in 2004: Observational study. BMJ. 2005;330(7500):1119--1120
+% [cited 2005 May 31]; Available from:
+% http://bmj.bmjjournals.com/cgi/reprint/330/7500/1119.
+%
+%\bibitem{Gau05}%14
+%Gaul~G. When geography influences treament options. Washington Post
+% (Maryland Ed.). 2005 Jul~24;Sect.~A:12 (col.~1).
+%
+%\bibitem{BGC04}%15
+%Berrino~F, Gatta~G, Crosignani~P. [Case-control evaluation of screening
+% efficacy]. Epidemiol Prev. 2004 Nov--Dec;28:354--359. Italian.
+%
+%\bibitem{PI51}%16
+%Piaget~J, Inhelder~B. La gen{\`e}se de l'id{\'e}e de hasard chez
+% l'enfant [The origin of the idea of chance in the child]. Paris:
+% Presses Universitaires de France; 1951.
+%
+%\end{thebibliography}
+%\end{verbatim}
+%\bigskip
+%\noindent Each entry takes the form:
+%\begin{verbatim}
+%\bibitem{key}%n Bibliography entry
+%\end{verbatim}
+%where `\texttt{key}' is the tag that is to be used as an argument for the \verb"\cite{}" commands in the text of the article and `\texttt{Bibliography entry}' is the material that is to appear in the list of references, suitably formatted.
 The commands
-\begin{verbatim}
-\usepackage[numbers,sort&compress]{natbib}
-\bibpunct[, ]{[}{]}{,}{n}{,}{,}
-\renewcommand\bibfont{\fontsize{10}{12}\selectfont}
-\makeatletter
-\def\NAT@def@citea{\def\@citea{\NAT@separator}}
-\makeatother
-\end{verbatim}
-need to be included in the preamble of your .tex file in order to generate the citations and bibliography as described above.
-
-Instead of typing the bibliography by hand, you may prefer to create the list of references using a \textsc{Bib}\TeX\ database.
+%\begin{verbatim}
+%\usepackage[numbers,sort&compress]{natbib}
+%\bibpunct[, ]{[}{]}{,}{n}{,}{,}
+%\renewcommand\bibfont{\fontsize{10}{12}\selectfont}
+%\makeatletter
+%\def\NAT@def@citea{\def\@citea{\NAT@separator}}
+%\makeatother
+%\end{verbatim}
+%need to be included in the preamble of your .tex file in order to generate the citations and bibliography as described above.
+%
+%Instead of typing the bibliography by hand, you may prefer to create the list of references using a \textsc{Bib}\TeX\ database.
 The \texttt{tfnlm.bst} file needs to be in your working folder or an appropriate directory, and the lines
-\begin{verbatim}
-\bibliographystyle{tfnlm}
-\bibliography{interactnlmsample}
-\end{verbatim}
-included where the list of references is to appear, where \texttt{tfnlm.bst} is the name of the \textsc{Bib}\TeX\ bibliography style file for Taylor \& Francis' NLM reference style and \texttt{interactnlmsample.bib} is the bibliographic database included with the \textsf{Interact}-NLM \LaTeX\ bundle (to be replaced with the name of your own .bib file).
+%\begin{verbatim}
+%\bibliographystyle{tfnlm}
+%\bibliography{interactnlmsample}
+%\end{verbatim}
+%included where the list of references is to appear, where \texttt{tfnlm.bst} is the name of the \textsc{Bib}\TeX\ bibliography style file for Taylor \& Francis' NLM reference style and \texttt{interactnlmsample.bib} is the bibliographic database included with the \textsf{Interact}-NLM \LaTeX\ bundle (to be replaced with the name of your own .bib file).
 \LaTeX/\textsc{Bib}\TeX\ will extract from your .bib file only those references that are cited in your .tex file and list them in the References section.
-
-Please include a copy of your .bib file and/or the final generated .bbl file among your source files if your .tex file does not contain a reference list in a \texttt{thebibliography} environment.
+%
+%Please include a copy of your .bib file and/or the final generated .bbl file among your source files if your .tex file does not contain a reference list in a \texttt{thebibliography} environment.
 

### 2022-03-03 paper/interactnlmsample.tex
almost done

@@
 \usepackage{caption}
-\usepackage{subcaption}
 \usepackage{threeparttable}
@@
 \usepackage{booktabs,tabularx}
+\usepackage{subcaption}
 \DeclareMathOperator{\argmaxH}{argmax} 
@@
 \newtheorem{notation}{Notation}
+\bibliographystyle{plain}
 
@@
 
-\articletype{ARTICLE TEMPLATE}% Specify the article type or omit as appropriate
-
-\title{Model-order reduction of non-linear time dependent neutronics via Galerkin projection and DEIM}
+\articletype{Journal of Nuclear Science and Technology}% Specify the article type or omit as appropriate
+
+\title{Model-order reduction of non-linear time dependent neutronics via POD-Galerkin projection and DEIM}
 \author{
-\name{Rabab Elzohery \thanks{CONTACT A.~N. Author. Email: rababelzohery@ksu.edu} and Jeremy Roberts}
+\name{Rabab Elzohery\thanks{CONTACT A.~N. Author. Email: rababelzohery@ksu.edu} and Jeremy Roberts}
 \affil{Department of Mechanical and Nuclear Engineering,
@@
 \begin{abstract}
+Presented here is an application of model-order reduction to non-linear neutronic transients, where reduced-order models (ROMs) are generally sought to provide a rapid and accurate approximation of a particular simulation solution.
+The ROM was built with the use of the POD-Galerkin projection method, where the main contribution of this work is the employment of the matrix version of the Discrete Empirical Interpolation Method (MDEIM) to improve the ROM efficiency.
+The MDEIM is used to approximate the projection of the problem operator that otherwise is required to be computed at each non-linear iteration within each time step, increasing the ROM cost.
+By using the MDEIM, an offline-online ROM decomposition was obtained, which is favored from a computational perspective since the expensive projection operation can take place only once in the offline stage.
+The online stage, which involves solving a linear system  at each time step, depends only on the reduced dimension and is therefore cheap, making it possible to increase the solution time resolution, and accordingly accuracy, without introducing significant cost.
+By applying the method to the LRA benchmark, speeds up that range from 6 to 40 was achieved depending on the full-order model (FOM) spatial fidelity.
+The maximum relative error in the assemblies power was in the order of $1\times10^{-5}$\%.
+Moreover, the ROM was parameterized by using a POD-greedy sampling and a case study was tested where the kinetic data.
+i.e, the precursors decay constant and delayed neutron fraction, are assumed to be the parameters of interest.
+For the parameterized ROM, the maximum relative error in the assembly power was  \% ., which indicates that the developed ROM can be reliably used in parametric and uncertainty quantification studies.
+The computational gain from the MDEIM-ROM was compared with that of a direct projection ROM and showed that employing the MDEIM is computationally advantageous and becomes even more appreciable with higher-dimensional problems.
+The method was implemented in the open-source deterministic transport code Detran where only access to the system operator was needed to construct the ROM, and hence the method is considered trivially invasive and could be implemented in modern deterministic transport codes.
 
@@
 \begin{keywords}
-Galerkin projection; POD; ROM; Neutronic Transient
+Galerkin projection; POD; Non-linear reduced-order models; Neutronic Transient; Discrete Empirical Interpolation Method
 \end{keywords}
@@
 
-Modeling and simulation of reactor physics is crucial to understand the nuclear reactors behavior under different conditions and scenarios and hence ensure reliable design and well established safety limits.
-The mathematical models are described by a set of equations that is challenging to solve analytically due to the geometric complexity of nuclear reactors except for simplified cases.
+Modeling and simulation of reactor physics is crucial to understand nuclear reactors behavior under different conditions and scenarios and hence ensure reliable design and well established safety limits.
+The mathematical models governing the reactor physics are described by a set of equations that is challenging to solve analytically due to the geometric complexity of nuclear reactors except for simplified cases.
 Alternatively, these systems are solved by employing numerical discretization that rely on discretizing the system along each independent variable and the solution is provided only on these discrete points.
@@
 In the application of our interest here, neutronic transients, the mathematical models are based on the diffusion approximation and the Boltzmann transport equation.
-For realistic modeling, these neutron transport model need to be coupled with different physics models to account for the feedback.
+For realistic modeling, these neutron transport models need to be coupled with different physics models to account for their feedback.
 For example, thermal-hydraulics feedback plays an essential role in reactor operation.
 Changes in the fuel temperature alter the cross sections due to Doppler broadening \cite{stacey2018nuclear}, which in turn impacts the neutron population and hence the fission rate and the rate of heat generation.
-Multi-physics modeling accounts for these different feedbacks mechanisms; however, it poses a challenge in terms of the computational cost,
+Multi-physics modeling accounts for these different feedback mechanisms; however, it poses a challenge in terms of the computational cost,
 since it entails solving coupled systems for different fields such as neutron flux, temperature, and flow rate.
@@
 A modern algorithm such as Jacobian free Newton-Krylov (JFNK) \cite{gaston2009parallel} can be used to perform this implicit coupling.
-Another popular approach is to use fixed-point iteration, with an implicit time scheme to iterate between difference physics within a time step until convergence is satisfied, which is compitationaly taxing.
+Another popular approach is to use fixed-point iteration, with an implicit time scheme to iterate between difference physics within a time step until convergence is satisfied, which is computationally taxing.
 The aim of this work is to use a reduce-order model to overcome the high computational expense of these non-linear models.
 In particular, the ROM was developed using the POD-Galerkin projection.
-The method belongs to the projection-based family, and can be described as an physics-driven method since it requires knowlege of the original governing equation as will be shown in sec.  .
-In a previous work, \cite{elzohery-greedyPOD}, we applied the method to time dependent diffusion equation where there was no coupling with other models and hence the application was linear.
-In this study, the developed ROM was extended to treat non-linearity problem induced by multi physics modeling.
-The LRA benchmark was used as a demonstrative application where coupling the diffusion equation is coupled with a simplified thermal model.
-
+The method belongs to the projection-based family, and can be described as a physics-driven method since it requires knowledge of the original governing equation as will be shown in Sec.\ref{sec:POD}.
+In a previous work \cite{elzohery2021modeling}, we applied the method to time dependent diffusion equation where there was no coupling with other models and hence the application was linear.
+In this study, the developed ROM was extended to treat the non-linearity induced by multi-physics modeling.
 To improve the computational efficiency of the developed ROM, a hyper-reduction technique known as the Discrete Empirical Interpolation Method (DEIM) was used in conjunction of the POD-Galerkin projection.
-The primary purpose of using the DEIM is to obtain an offline-online decomposition of the ROM to avoid repetitive projection of the problem operator at each iteration with each time step.
+The primary purpose of using the DEIM is to obtain an offline-online decomposition of the ROM to avoid repetitive projection of the problem operator at each iteration within the time step.
 The offline stage occurs only once and it comprises the expensive step of the ROM, where the online stage is cheaper and involves solving a reduced number of equation at each time step.
-The following discussion include a general overview of the methods and algorithms, then the specific application was described.
-Results are presented and conclusion was given.
+The LRA benchmark was used as a demonstrative application where the diffusion equation is coupled with a simplified thermal feedback model.
+
+%The following discussion include a general overview of the methods and algorithms, then the specific application was described after which its results are presented.
 
@@
 
+In this section, the methods used throughout the study are described, including the POD-Galerkin projection used to build the ROM, DEIM used to improve the computational efficiency of the ROM, and greedy POD sampling used to parameterize the ROM.
+
+%--------------------------------------------------------------------------------------------------%
+
 \subsection{POD-Galerkin Projection}\label{class}
@@
 In general, this method involves two main steps.
-First, a subspace is obtained using the POD which is a widely used reduction technique.
-Commonly, the POD subspace is generated using the snapshots method \cite. 
-A data matrix $\mathbf{Y}$ is constructed by collecting the system solutions at different time instances, then the singular value decomposition (SVD) is computed, i.e $\mathbf{Y} = \mathbf{U}\mathbf{\Sigma}\mathbf{V}$.
-The POD subspace is the one spanned by the first $r$ vector of $\mathbf{U}$, where $r \ll n$.
-There is no general \textit{a priori} rule based on which the rank is chosen; however one can set a threshold $\epsilon$  such that
+First, a subspace is obtained using the proper orthogonal decomposition, i.e, POD \cite{}, a widely used reduction technique.
+Commonly, the POD subspace is generated using the snapshots method \cite{} by constructing a data matrix $\mathbf{Y}$ containing the system solutions at different time instances, then the singular value decomposition (SVD) is computed, i.e $\mathbf{Y} = \mathbf{U}\mathbf{\Sigma}\mathbf{V}$.
+The POD subspace is the one spanned by the first $r$ vectors of $\mathbf{U}$, where $r \ll n$.
+There is no general \textit{a priori} rule based on which the rank $r$ is chosen; however one can set a threshold $\epsilon$  such that
 \begin{equation}
@@
 where S$i$ is the $i$th singular value.
-For more details the reader might consult \cite{bibid}, 
-Upon obtaining the reduced space, the state variable $\mathbf{y}$ is expanded in terms of its basis, where each basis vector is weighted by a temporal coefficient
+Upon obtaining the reduced space, the state variable $\mathbf{y}$ is expanded in terms of its basis
 \begin{equation}
@@
 where $\mathbf{\hat{y}(t)} \in \mathbb{R}^{r}$ is a vector of the temporal coefficients.
-Second, the system is projected onto a POD subspace by multiplying the system on the left by $\mathbf{\Phi}^T$ and making use of the orthogonality of the POD basis (i.e, $\mathbf{U}^T\mathbf{U} = \mathbf{I}$), we end up with
-\begin{equation}
-	\frac{d\mathbf{\hat{y}}}{dt} = \mathbf{A}_r\mathbf{\hat{y}} + \mathbf{\Phi}^T\mathbf{f}(\mathbf{U}\mathbf{\hat{y}}) \qquad \mathbf{\hat{y}}(0) = \mathbf{U}^T\mathbf{y}_0 \, ,
+Second, the system is projected onto a POD subspace by multiplying the system on the left by $\mathbf{U}^T$ and making use of the orthogonality of the POD basis (i.e, $\mathbf{U}^T\mathbf{U} = \mathbf{I}$), we end up with
+\begin{equation}
+	\frac{d\mathbf{\hat{y}}}{dt} = \mathbf{A}_r\mathbf{\hat{y}} + \mathbf{U}^T\mathbf{f}(\mathbf{U}\mathbf{\hat{y}}) \qquad \mathbf{\hat{y}}(0) = \mathbf{U}^T\mathbf{y}_0 \, ,
 	\label{eq:ROM}
 \end{equation}
-where $\mathbf{A}_r \in \mathbb{R}^{r\times r} = \mathbf{\Phi}^T\mathbf{A}\mathbf{\Phi}.$
-Thus, we are left with  $r$ ODE's instead of $n$ ODE's, which makes the resulting ROM more computationally efficien, and, once it is solved for $\mathbf{\hat{y}}$, the full order solution can be computed by Eq.~\ref{eq:galerkin expansion}.
+where $\mathbf{A}_r \in \mathbb{R}^{r\times r} = \mathbf{U}^T\mathbf{A}\mathbf{U}.$
+Thus, we are left with $r$ ODE's instead of $n$ ODE's, which makes the resulting ROM cheaper to solve, and once it is solved for $\mathbf{\hat{y}}$, the full order solution can be computed by Eq.~\ref{eq:galerkin expansion}.
 
@@
 \label{sec:DEIM}
-Recently, the DEIM \cite{chaturantabut2010nonlinear} was proposed to approximate the non-linearity in model order reduction.
-%The method is a discrete variant of the Empirical Interpolation Method (EIM) \cite{barrault2004empirical} that was originally proposed to approximate
-%non-affine coefficient functions using a reduced-basis expansion to facilitate the online/offline decomposition in finite element methods.
-The DEIM is proposed to facilitate the online/offline decomposition of ROMs.
+Recently, the DEIM \cite{chaturantabut2010nonlinear} was proposed to approximate the non-linearity in the context of model-order reduction and to facilitate the online/offline decomposition of ROMs.
+The method is a discrete variant of the Empirical Interpolation Method (EIM) \cite{barrault2004empirical} that was originally proposed to approximate
+non-affine coefficient functions using a reduced-basis expansion to facilitate the online/offline decomposition in finite element methods.
+To illustrate the method, consider the model in Eq.\ref{eq:FOM} for which we seek an approximate ROM.
+The non-linear term $\mathbf{f}(\textbf{y}(t))$ introduces computational complexity to the ROM since computing the projected term $\mathbf{U}^T\mathbf{f}(\textbf{y}(t))$ requires reconstructing the full-order  solution first.
+The reconstruction and the projection steps have cost dependent on the dimension of the system, i.e $n$.
+The goal of using the DEIM is to avoid performing these operations at each time step and split the cost of the ROM into two steps,
+offline step where the expensive operations dependent on $n$ take place, and online step that depends only on the reduced dimension.
 The method relies on two main ingredients: (1) a reduced space that approximates the nonlinear function, and (2) a set of spatial interpolation indices.
-To illustrate the method, let $\tau$ denote time or a model parameter.
-The nonlinear function $\mathbf{f}(\textbf{y}(\tau))$ is approximated by projecting it onto a subspace that approximates the function space
+The nonlinear function $\mathbf{f}(\textbf{y}(t))$ is approximated by projecting it onto a subspace that approximates the function space
 \begin{equation}
@@
 where $\mathbf{\Psi} \in \mathbb{R}^{n\times k}$ is a low-dimensional subspace with $k \ll n$, and $\boldsymbol{\theta}(\tau) \in \mathbb{R}^k$ is a vector of the corresponding coefficients.
-POD is used to find the subspace $\mathbf{\Psi}$ using snapshots of the function (i.e, $[\textbf{y}(\tau_1), ....., \textbf{y}(\tau_m)]$).
-Note that these snapshots are computed at the same points used for the state variable snapshots required for the reduced model; hence this step will not introduce any additional cost other than computing the SVD.
-In order to compute $\theta(\tau)$, a few spatial indices are selected iteratively using a greedy search following Algorithm \ref{alg:DEIM}.
+POD is used to find the subspace $\mathbf{\Psi}$ using snapshots of the function (i.e, $[\textbf{y}(t_1), ....., \textbf{y}(t_m)]$).
+In order to compute $\theta(t)$, a few spatial indices are selected iteratively using a greedy search following Algorithm \ref{alg:DEIM}.
 The basic idea is to select $k$ rows of the basis matrix $\mathbf{\Psi}$.
@@
 \end{equation}
-Note that the matrix $\mathbf{P}$ does not need to be constructed explicitly, since the term $\mathbf{P}^T\mathbf{f}$ extracts only the elements of $\mathbf{f}$ that correspond to the interpolation indices.
+A key point relevant to the computational efficiency of the method is that the matrix $\mathbf{P}$ does not need to be constructed explicitly, since the term $\mathbf{P}^T\mathbf{f}$ extracts only the elements of $\mathbf{f}$ that correspond to the interpolation indices.
 Thus, at each time step, only $k$ elements $\mathbf{f}$ need to be evaluated.
-The approximation error can be bounded as 
-\begin{equation}
-	\|\mathbf{f} - \hat{\mathbf{f}} \| \le \|(\mathbf{P}\mathbf{\Psi})^{-1} \| \epsilon \, ,
-\end{equation}
-where
-\begin{equation*}
-	\epsilon \approx \sigma_{k+1} \, .
-\end{equation*}
-Note that $\sigma_{k+1}$ is the $(k+1)th$ singular value coming from the SVD of the function snapshots matrix.
-Full derivation of the error bound is given in Ref.~\cite{chaturantabut2010nonlinear}.
-
-As explained in the previous section, the projection can be performed by computing the term $\mathbf{U}^T \mathbf{\Psi}$ once in an offline stage, while in the online stage, the vector $\boldsymbol{\theta}$ is computed by solving the linear system of dimension $k$ in Eq.~\ref{eq:DEIM coefficients}.
-The key point is that the cost of the online computation depends on the reduced dimension $k$, not the original, high dimension $n$.
-The matrix version of the DEIM (MDEIM) is suggested in \cite{carlberg2012efficient, benner2015survey} to approximate parameter/time-dependent operators.
-Consider a parameterized matrix $\mathbf{A}(\boldsymbol{\mu}) \in \mathbb{R}^{n\times n}$, the goal is to find a decomposition similar to Eq.~\ref{Eq:matrix decomposition} so that an offline-online ROM splitting is attainable.
-The DEIM procedures can be exploited to find such decomposition. First, the matrix can be cast in a vector form by stacking all of its columns in one vector $\mathbf{a}(\mu) \in \mathbb{R}^{n^2}$.
-This vector can be treated in the same exact way as the function $\mathbf{f}(t)$ in the previous section, i.e, $\mathbf{a}(\mu) = \mathbf{\Psi}\boldsymbol{\theta}(\mu)$.
-Snapshots of the serialized matrix are collected at different parameter values and the reduced subspace $\mathbf{\Psi}$ and the interpolation indices are computed following algorithm \ref{alg:DEIM}.
+%The approximation error can be bounded as 
+%\begin{equation}
+%	\|\mathbf{f} - \hat{\mathbf{f}} \| \le \|(\mathbf{P}\mathbf{\Psi})^{-1} \| \epsilon \, ,
+%\end{equation}
+%where
+%\begin{equation*}
+%	\epsilon \approx \sigma_{k+1} \, .
+%\end{equation*}
+%Note that $\sigma_{k+1}$ is the $(k+1)th$ singular value coming from the SVD of the function snapshots matrix.
+%Full derivation of the error bound is given in Ref.~\cite{chaturantabut2010nonlinear}.
+
+Now, the projection can be performed by computing the term $\mathbf{U}^T \mathbf{\Psi}$ once in an offline stage, while in the online stage, the vector $\boldsymbol{\theta}$ is computed by solving the linear system of dimension $k$ in Eq.~\ref{eq:DEIM coefficients}.
+Thus, the cost of the online computation depends on the reduced dimension $k$, not the original, high dimension $n$.
+
+Although the problem tackled here does not include a non-linear term, the DEIM idea is exploited to approximate time-dependent operators to avoid computing the projected operator $\mathbf{A}_r(t)$ at each time step, which requires number of FLOPS dependent on $n$.
+This is known as the matrix version of the DEIM, i.e, MDEIM and it was suggested in \cite{carlberg2012efficient, benner2015survey}.
+To illustrate, consider the operator $\mathbf{A}(\boldsymbol{t}) \in \mathbb{R}^{n\times n}$.
+The DEIM procedures can be used to approximate the operator by a summation of few time independent matrices, each weighted by a temporal coefficient.
+First, the matrix can be cast in a vector form by stacking all of its nonzero elements in one vector $\mathbf{a}(t) \in \mathbb{R}^{n^2}$.
+This vector can be treated in the same exact way as the function $\mathbf{f}(t)$ in the previous section, i.e, $\mathbf{a}(\mu) = \mathbf{\Psi}\boldsymbol{\theta}(t)$.
+Snapshots of the serialized matrix are collected at different time instances and the reduced subspace $\mathbf{\Psi}$ and the interpolation indices are computed following algorithm \ref{alg:DEIM}.
 Again, the corresponding coefficients are obtained by solving Eq.~\ref{eq:DEIM coefficients}. 
 Next, each vector in $\mathbf{\Psi}$ can be mapped back to an $n \times n$ matrix, i.e, $\textbf{A}_i$.
-Hence, the matrix is approximated as $\mathbf{\hat{A}}(t)=\sum_{i=0}^k \theta_i(t) \mathbf{A}_i$ and the projection term is computed as in Eq.~\ref{Eq:deim matrix projection}.
+Hence, the matrix is approximated as $\mathbf{\hat{A}}(t)=\sum_{i=0}^k \theta_i(t) \mathbf{A}_i$ and the projection term is computed as
+\begin{equation}
+	\mathbf{U}^T\mathbf{A}\mathbf{U} = \sum_{i=0}^k \mathbf{\theta}_i(t)\mathbf{U}^T\mathbf{A}_i\mathbf{U} \, .
+	\label{Eq:deim matrix projection}
+\end{equation}
 As pointed out in Ref.\cite{negri2015efficient}, the Weyl\textendash Mirsky theorem \cite{weyl1912asymptotische} ensures that the singular values of the approximated matrix approach that of the original as $k$ increases
@@
 where $\sigma_i$ and $\hat{\sigma_i}$ denote the $i$th singular value of $\mathbf{A}$ and $\hat{\mathbf{A}}$ respectively.
-Moreover, some properties of the original matrix such as positive definiteness can be preserved \cite{carlberg2015preserving}, if necessary, by imposing some constrains to the problem in Eq.~\ref{eq:DEIM coefficients}.
-
-%In the practical implementations, the method efficiency can be improved, as suggested in Ref. \cite{negri2015efficient}.
-%First, the matrix $\mathbf{A}$ is, generally, largely sparse, which leads to a snapshots matrix that is sparse, too.
-%Consequently, it is more convenient to store only the nonzero elements ($nz$) in $\mathbf{a}$, 
-%which should be appreciably more efficient in terms of memory and computational expense.
-%In addition, to obtain the expansion coefficients ($\boldsymbol{\theta}$), the term $\mathbf{P}^T\mathbf{a(\tau)}$ needs to be computed at each new parameter value.
-%In fact, this term only extracts the elements of $\mathbf{a(\tau)}$ that corresponds to the selected  interpolation indices.
+%Moreover, some properties of the original matrix such as positive definiteness can be preserved \cite{carlberg2015preserving}, if necessary, by imposing some constrains to the problem in Eq.~\ref{eq:DEIM coefficients}.
+
+In the practical implementations, the method efficiency can be improved, as suggested in Ref. \cite{negri2015efficient}.
+First, the matrix $\mathbf{A}$ is, generally, largely sparse, which leads to a snapshots matrix that is sparse, too.
+Consequently, it is more convenient to store only the nonzero elements ($nz$) in $\mathbf{a}$, 
+which should be appreciably more efficient in terms of memory and computational expense.
+In addition, to obtain the expansion coefficients ($\boldsymbol{\theta}$), the term $\mathbf{P}^T\mathbf{a(t)}$ needs to be computed at each new parameter value.
+In fact, this term only extracts the elements of $\mathbf{a(t)}$ that corresponds to the selected  interpolation indices.
 In the offline stage, a mapping can be done between these interpolation indices and the corresponding row-column pairs in $\mathbf{A}$.
-When the matrix is formed in the online stage, only these entries are evaluated by restricting a \textit{for loop } over these row-column pairs, leading to more reduction in the computational cost.
+When the matrix is formed in the online stage, only these entries are evaluated by restricting a \textit{for loop} over these row-column pairs, leading to more reduction in the computational cost.
 
@@
 
+%-----------------------------------------------------------------------------------------%
+
 \subsection{Greedy POD}
+\label{sec:POD}
 
@@
 \label{sec:fom}
-The time dependent diffusion equation was used as the mathematical model describing the neutronic transient in a nuclear reactor, i.e FOM and for which a an approximate ROM is sought.
-It is represented as
+In this work, the time dependent diffusion equation was used as the mathematical model of neutronic transients in nuclear reactors, i.e FOM, and for which an approximate ROM is sought.
+The multi-group version of the equation is represented as
 \begin{equation}
@@
 $C_i$ is the $i$th precursor concentration, $\beta_i$ is the fraction of delayed neutrons in group $i$, $\lambda_i$ is the $i$th group decay constant.
-The system can be represented compactly in a matrix form as 
-\begin{equation}
-\frac{\partial{y}(r, t)}{\partial{t}} = \mathcal{A}{y}(r, t) \, ,
-\end{equation}
-where the stacked unknowns are
-\begin{equation*}
-	{y} = 
-	\begin{pmatrix}
-	\phi_1(r, t) \\
-	\vdots \\
-	\phi_G(r, t)  \\
-	{C}_1(r, t) \\
-	\vdots \\
-	{C}_I(r, t) \\
-	\end{pmatrix} \, .
-\end{equation*}
+%The system can be represented compactly in a matrix form as 
+%\begin{equation}
+%\frac{\partial{y}(r, t)}{\partial{t}} = \mathcal{A}{y}(r, t) \, ,
+%\end{equation}
+%where the stacked unknowns are
+%\begin{equation*}
+%	{y} = 
+%	\begin{pmatrix}
+%	\phi_1(r, t) \\
+%	\vdots \\
+%	\phi_G(r, t)  \\
+%	{C}_1(r, t) \\
+%	\vdots \\
+%	{C}_I(r, t) \\
+%	\end{pmatrix} \, .
+%\end{equation*}
 
@@
 %\end{equation*}
-Upon spatial discretization, the system of ODEs can be compactly represented in a block matrix form as  
+Upon spatial discretization, the resulting system of ODEs can be compactly represented in a matrix form as  
 \begin{equation}
@@
 \end{equation}
-where $\mathbf{y}\in\mathbb{R}^{N}$ is stacked vector of the flux and the precursors concentration, $\mathbf{A}\in\mathbb{R}^{N\times N}$ and $N = (I + G)\times n$ with $n$ is the number of spatial unknowns arising from discretization.
-The discretized block matrix $\mathbf{A}$ is written as 
+where $\mathbf{y}\in\mathbb{R}^{N}$ is stacked vector of the flux and the precursors concentration, $\mathbf{A}\in\mathbb{R}^{N\times N}$ and $N = (I + G)\times n$ with $n$ is the number of spatial unknowns arising from discretization, $G$ is the number of energy groups, and $I$ is the number of precursors groups.
+The operator $\mathbf{A}$ can be written in a block matrix form as
 \begin{equation}
@@
 \end{equation} 
-where $\mathbf{L} \in \mathbb{R}^{(n\times G)\times (n\times G)}$ represents the diffusion operator, $\mathbf{D} \in \mathbb{R}^{(n\times G)\times (n\times I)}$ represents the delayed neutrons production operator , $\mathbf{P} \in \mathbb{R}^{(n\times I)\times ((n\times G)}$ represents the precursors loss operator and $\mathbf{F}\in \mathbb{R}^{(n\times I)\times ((n\times I)}$ represents the precursors production operator.
+where $\mathbf{L} \in \mathbb{R}^{(n\times G)\times (n\times G)}$ represents the diffusion operator,
+$\mathbf{D} \in \mathbb{R}^{(n\times G)\times (n\times I)}$ is a block diagonal matrix representing the delayed neutrons production operator,
+$\mathbf{P} \in \mathbb{R}^{(n\times I)\times ((n\times G)}$ is a diagonal matrix represents the precursors concentration loss operator, 
+and $\mathbf{F}\in \mathbb{R}^{(n\times I)\times ((n\times I)}$ represents the precursors production operator.
 %Thus, the system in Eq.~\ref{eq:transient fom} is the full-order model and it can be solved using a suitable time-scheme.
@@
 %--------------------------------------------------------------------------------------%
-\subsection{Benchmark Desription}
-
-The LRA benchmark employs two energy groups and two delayed precursor groups and represents a 2-D quarter-core, BWR model subject to a control-rod ejection with adiabatic heating \cite{anl}.
+\subsection{Problem Description}
+
+The LRA benchmark was used as an illustrative application for non-linear problems.
+It employs two energy groups and two delayed precursor groups and represents a 2-D quarter-core, BWR model subject to a control-rod ejection with adiabatic heating \cite{anl}.
 A schematic layout of the problem is shown in Fig.~\ref{fig:lra core}, where region numbers indicate different materials and region R is the ejected rod.
@@
 The transient was calculated for 3.0 seconds.
-Figure~\ref{fig:lra fom power} shows the reference full-order model power along with the core average temperature, while Figure \ref{fig:lra ss flux} shows the steady-state group flux distribution.
+Figure~\ref{fig:lra fom power} shows the reference full-order model power along with the core average temperature.
 This reference solution is not necessarily numerically converged in either space or time but represents the simulation response that one wishes to approximate.
@@
 
-Using the POD-Galerkin projection, a ROM was constructed to approximate the group flux and the core power of the LRA benchmark.
-As discussed in the previous chapter, the time-dependent diffusion equation coupled with the precursors group equation can be cast into a compact form as in Eq.~\ref{eq:transient fom}.
-Similar to the TWIGL benchmark ROM, POD basis set was generated for each group flux while one basis set was generated for both precursors groups, i.e, 
+Using the POD-Galerkin projection procedures described in Sec.~\ref{sec:POD}, a ROM was constructed to approximate the group flux and the core power of the LRA benchmark with increasing the spatial fidelity, i.e, spatial grids of $22\times 22$, $44\times44$ and $55 \times 55$ were used.\\
+POD basis set was generated for each group flux while one basis set was generated for both precursors groups, i.e, 
 $\mathbf{\Phi}_1(t) = \mathbf{U}_1\mathbf{a}_1(t)$, $\mathbf{\Phi}(t)_2 = \mathbf{U}_2\mathbf{a}_2(t)$ and $\mathbf{C}(t) = \mathbf{U}_c\mathbf{a}_c(t)$, where the $\mathbf{U}_1$, $\mathbf{U}_2$  and $\mathbf{U}_c$ are the POD bases of the fast group, thermal group and precursor concentration respectively, and $\mathbf{a}_1$, $\mathbf{a}_2$ and $\mathbf{a}_c$ are their respective temporal coefficients.
-The first 100 normalized singular values \footnote{The normalization is done be dividing each singular value by the sum of all singular values.} of the group flux are shown in Fig.~\ref{fig:lra singular values}.
+The resulting ROM can be represented as 
+\begin{equation}
+	\frac{d\mathbf{\hat{y}}}{dt} = \mathbf{A}_r\mathbf{\hat{y}}\, , 
+	\label{eq:ROM}
+\end{equation}
+where
+ \begin{equation*}
+	\mathbf{\hat{y}} = \begin{pmatrix}
+	\mathbf{a}_1\\
+	\mathbf{a}_2 \\
+	\mathbf{a}_c \\
+	\end{pmatrix} \,.
+ \end{equation*}
+%The first 100 normalized singular values \footnote{The normalization is done be dividing each singular value by the sum of all singular values.} of the group flux are shown in Fig.~\ref{fig:lra singular values}.
+
+For POD rank selection, the ROM was solved with different flux ranks and the relative L$_2$ norm of the flux errors are computed and are shown in Fig.~\ref{fig:POD flux rank}.
 \begin{figure}[h!]
-	\includegraphics[width=1.0\linewidth]{../figures/LRA_singular_values.pdf}
+	\includegraphics[width=1.0\linewidth]{../figures/flux_rank_convergence.pdf}
 	\caption{flux normalized singular value.}
-	\label{fig:lra singular values}
-\end{figure}
-Since the focus of this application is on treating the non-linearity, rather than trying different ranks of the POD basis, rank 30 was chosen for each group flux and for the precursor concentration.
-Also, the temperature field was approximated by projecting it onto a lower dimensional POD space
+	\label{fig:POD flux rank}
+\end{figure}
+A POD rank of 30 was selected fore each group flux since it results in an error less than   \% and the same rank was used for approximating the precursors concentration.
+Higher ranks can be selected if a better ROM accuracy is desired.
+
+Furthermore, a ROM was constructed for the coupled thermal feedback model and the temperature field was approximated by projecting it onto a lower dimensional POD space
 \begin{equation}
@@
 where $\mathbf{U}_{\text{temp}}\in\mathbb{R}^{n \times r_T} $ is the POD subspace of rank $r_T$ and $\mathbf{a}_T\in \mathbb{R}^{r_T}$ is a vector of the corresponding temporal coefficients. 
-To obtain the subspace, snapshots of the temperature were collected at different times for which the SVD was computed.
-Shown in Fig.~\ref{fig:lra T singular values} are the first 100 normalized singular values, based on which a POD of rank $10$ was selected for approximating the temperature.
-\begin{figure}[H]
-	\centering
-	\includegraphics[width=1.0\linewidth]{../figures/LRA_T_singular_values.pdf}
-	\caption{temperature normalized singular value.}
-	\label{fig:lra T singular values}
-\end{figure}
+%To obtain the subspace, snapshots of the temperature were collected at different times for which the SVD was computed.
+%Shown in Fig.~\ref{fig:lra T singular values} are the first 100 normalized singular values.
 Inserting Eq.~\ref{eq:temp pod} into Eq.~\ref{eq:heatup} and multiplying on the left by $\mathbf{U}_T^T$ \footnote{The superscript T denotes the matrix transpose.} yields
@@
 Note that $\mathbf{U}_{T1}$ and $\mathbf{U}_{T2}$ are time-independent, so they can be precomputed once and stored.
-Thus, at each time step the flux temporal coefficients (i.e, $\mathbf{a_1}(t)$ and $\mathbf{a_2}(t)$) are computed by solving the reduced system and then used to compute the temperature coefficients by employing a first-order, backward-difference scheme to Eq.~\ref{eq:reduced temp}.
+For selecting the temperature rank, i.e, $r_T$, the ROM was solved with different temperature ranks and the selected flux and precursors ranks.
+The core power relative error was computed in each case and is shown in Fig.~\ref{fig:temperature rank} based on which a POD of rank $10$ was selected for approximating the temperature.
+
+\begin{figure}[H]
+	\centering
+	\includegraphics[width=1.0\linewidth]{../figures/temperature_rank_convergence.pdf}
+	\caption{temperature normalized singular value.}
+	\label{fig:temperature rank}
+\end{figure}
+
+Now to solve for the quantities of interest, the flux temporal coefficients (i.e, $\mathbf{a_1}(t)$ and $\mathbf{a_2}(t)$) are computed at each time step by solving the reduced system in Eq.~\ref{eq:ROM} and then used to compute the temperature coefficients by employing a first-order, backward-difference scheme to Eq.~\ref{eq:reduced temp}.
 Similar to the full-order model, a fixed point iteration is used to treat the flux non-linearity.
@@
 \begin{equation}
-\frac{\| \mathbf{a}^{i-1} - \mathbf{a}^{i}\|}{\|\mathbf{a}_i \|} \le 1\times 10^{-6}  \, , 
-\end{equation}
-Note that the fast absorption cross section needs to be updated at each time step using Eq.~\ref{eq:doppler} in which the core temperature distribution is required.
-In order to avoid reconstructing the full order temperature, 
-the DEIM was used to approximate the absorption cross section.
-For this purpose, snapshots of which were collected in order to generate a POD subspace that is used to approximate its space and to find a set of interpolation indices as illustrated in Algorithm~\ref{alg:DEIM}.
-DEIM of order $10$ was used and hence, the cross section was reconstructed at each time step at only 10 points in the spatial space.
-Moreover, since the reactivity insertion was simulated by changing the absorption cross section, the operator $\mathbf{A}$ in Eq.~\ref{Eq:transient rom} exhibits time dependence, 
-The MDEIM was used to decompose the operator and hence avoid performing the expensive projection at each time step.
+	\frac{\|\mathbf{a}^{i-1} - \mathbf{a}^{i}\|}{\|\mathbf{a}_i \|} \le 1\times 10^{-6}  \, , 
+\end{equation}
+
+%Note that the fast absorption cross section needs to be updated at each time step using Eq.~\ref{eq:doppler} in which the core temperature distribution is required.
+%In order to avoid reconstructing the full order temperature, 
+%the DEIM was used to approximate the absorption cross section.
+%For this purpose, snapshots of which were collected in order to generate a POD subspace that is used to approximate its space and to find a set of interpolation indices as illustrated in Algorithm~\ref{alg:DEIM}.
+%DEIM of order $10$ was used and hence, the cross section was reconstructed at each time step at only 10 points in the spatial space.
+Since the reactivity insertion was simulated by changing the absorption cross section, the operator $\mathbf{A}$ in Eq.~\ref{eq:transient fom} exhibits time dependence.
+In particular, the submatrix $\mathbf{L}$ of $\mathbf{A}$ is the one that changes with time.
+Thus, to avoid performing the expensive projection at each time step, 
+The MDEIM was used to decompose the matrix $\mathbf{L}$.
 Shown in Fig.~\ref{fig:lra L singular values} are the singular values resulting from the SVD of the serialized operator snapshots. 
-Based on the shown plot, a DEIM of order $15$ was used.
+Based on the shown plot, a MDEIM of order $15$ was used.
+
 \begin{figure}[H]
 	\includegraphics[width=1.0\linewidth]{../figures/LRA_L_singular_values.pdf}
-	\caption{Operator normalized singular value.}
+	\caption{The normalized singular values of the serializes operator $\mathbf{L}$.}
 	\label{fig:lra L singular values}
 \end{figure}
-
-%------------------------------------------------------------------------%
-\subsection{Results}
-
-\subsubsection{ROM results}
-ROMs were constructed for FOMs models with increasing the spatial fidelity, i.e, spatial grids of $22\times 22$, $44\times44$ and $55 \times 55$.
-For brevity, we show the POD modes with their temporal coefficients of only the $55 \times 55$  grid in Fig.~\ref{fig:lra flux modes}.
+%----------------------------------------------------------------------------------------------------%
+
+\subsection{ROM results}
+
+Using the selected ranks in the previous subsection, MDEIM-ROMs were developed for full-order models of spatial grids $22\times 22$, $44\times44$ and $55 \times 55$.
+For brevity, we show the first four POD modes with their temporal coefficients of only the $55 \times 55$ grid in Fig.~\ref{fig:lra flux modes}.
 %\begin{figure}[H]
@@
 %		\caption{Fast flux modes.}
-%		\label{fig:ss fast flux}
+%		\label{fig:ss fast flux 2}
 %	\end{subfigure}
@@
 %		\caption{Thermal flux modes.}
-%		\label{fig:ss thermal flux}
+%		\label{fig:ss thermal flux 2}
 %	\end{subfigure}
@@
 %\end{figure}
-Using ROMs with the specifications given in the previous section, the absolute relative error in the predicted powers are computed as shown in Fig.~\ref{fig:deim power error}.
+The absolute relative error in the predicted core powers are computed as shown in Fig.~\ref{fig:deim power error}.
+
 \begin{figure}[H]
 	\includegraphics[width=1.0\linewidth]{../figures/LRA_power_deim_relative_error.pdf}
-	\caption{Relative error of the power predicted by MDEIM ROM}
+	\caption{Relative error of the power predicted by MDEIM-ROM}
 	\label{fig:deim power error}
 \end{figure}
-The maximum flux errors for both groups are shown in Table \ref{tab:lra flux errors}.
-
-\begin{table*}[H]
-	\centering
-	\begin{tabular}{c|c|c}  
-		grid &	fast flux  &  thermal flux \\
-		\hline
-		$22\times 22$ &    &  1     \\
-		$44\times 44$ &    &       \\
-		$55\times 55$ &    &       \\
-		\hline
-	\end{tabular}
-	\caption{\bf maximum flux error of the fast and thermal flux (\%)}
-	\label{tab:lra flux errors}
-\end{table*}
-It was interesting to compare the power error with that of a ROM without MDEIM, i.e, with performing the operator projection at each time step.
-The power error is shown in Fig.~\ref{fig:rom power error} and apparently, the accuracy is comparable to that in Fig.~\ref{fig:deim power error}, implying an accurate approximation of the problem operator via the MDEIM.
+
+To understand the impact of employing the MDEIM on the error; the results are compared with these of a ROM without using the MDEIM, i.e., with performing direct operator projection at each time step.
+The relative difference of the power between both models is shown in Fig.~\ref{fig:rom-deim power error}.
+The shown errors implies that MDEIM accurately approximates the problem operator.
+
 \begin{figure}[H]
-	\includegraphics[width=1.0\linewidth]{../figures/LRA_power_rom_relative_error.pdf}
-	\caption{Relative error of the power predicted by ROM.}
-	\label{fig:rom power error}
+	\centering
+	\includegraphics[width=1.0\linewidth]{../figures/LRA_mdeim_relative_error.pdf}
+	\caption{Relative difference in the predicted power between the ROM and the MDEIM-ROM.}
+	\label{fig:rom-deim power error}
 \end{figure}
 Also, the spatial-averaged relative error in the approximated temperature was computed and is shown in Fig.~\ref{fig:deim tempearture error}.
+
 \begin{figure}[H]
+	\centering
 	\includegraphics[width=1.0\linewidth]{../figures/temperature_relative_error.pdf}
@@
 \end{figure}
-
-As mentioned earlier, the non-linearity of the fast absorption cross section was approximated using DEIM of rank 10.
-Shown in Fig.~\ref{fig:cross-section deim indices} are the 10 selected interpolation points on the absorption cross section map at the last time step. i.e, $t=3$ s.
-Thus, the temperature is constructed only at these locations from which the cross section is evaluated using Eq.~\ref{eq:doppler}.
+%As mentioned earlier, the non-linearity of the fast absorption cross section was approximated using DEIM of rank 10.
+%Shown in Fig.~\ref{fig:cross section deim indices} are the ten selected interpolation points onto the absorption cross section map at the end of transient, i.e., at $t=3$ s.
+%The temperature was constructed only at these locations from which the cross section is evaluated using Eq.~\ref{eq:doppler}.
+%\begin{figure}[H]
+%	\centering
+%	\includegraphics[scale=1.2]{../figures/LRA_XS_interpolation_points_XS_map.pdf}
+%	\caption{The fast cross section at t=3 s with the selected interpolation indices in red color.}
+%	\label{fig:cross section deim indices}
+%\end{figure} 
+To further assess the performance of the ROM, the relative error in a local quantity such as the assembly power at the peak is computed and is shown in Fig.~\ref{fig:assembly power error fm=5} for the $55\times 55$ grid from which it can be seen that the maximum error is in the order of $1\times 10^{-5}\%$.
 
 \begin{figure}[H]
-	\includegraphics[width=1.0\linewidth]{../figures/LRA_XS_interpolation_points_XS_map.pdf}
-	\caption{The fast cross section at t=3 with the selected interpolation indices in red color.}
-	\label{fig:cross section deim indices}
-\end{figure}
-
-The power assembly relative errors are computed and shown in Fig.~\ref{fig:assembly power error fm=5} for the $55\times 55$ grid.
-The same errors for the other two grids are given in appendix?.
-\begin{figure}[H]
-	\includegraphics[width=0.9\linewidth]{../figures/lra_assemb_fm=5.pdf}
-	\caption{Assembley power relative error for the $55\times 55$ grid}
+	\centering
+	\includegraphics[width=0.7\linewidth]{../figures/lra_assemb_fm=5.pdf} 
+	\caption{Assembly-averaged power relative error for the $55\times 55$ grid}
 	\label{fig:assembly power error fm=5}
@@
 
-The computational time for the FOM and the ROMS are given in Table~\ref{table:cpu time}.
+Moreover, the computational times of the FOM and the ROMs are given in Table~\ref{table:cpu time}.
 
@@
 	\centering
-	\caption{\bf computational time of the FOM and the ROMs}
+	\caption{Computational time of the FOM and the ROMs for the LRA benchmark.}
 	\label{table:cpu time}
 	\begin{tabular}{c|c|c|c}  
-		grid &	FOM (s)   &  ROM (s) & MDEIM-ROM (s)    \\
-		\hline
-		$22\times 22$ & 426   & 140   & 101   \\
-		$44\times 44$ &  1652  &   283 &  106  \\
-		$55\times 55$ &  2539  & 398   & 110   \\
+		Grid &	FOM (s)   &  ROM (s) & MDEIM-ROM (s)    \\
+		\hline
+		$22\times 22$ &  243   & 76   & 38   \\
+		$44\times 44$ &  1269  & 226   & 46   \\
+		$55\times 55$ &  2195  & 341   & 50   \\
 		\hline
@@
 
-\section{Using the \texttt{interact} class file}
-
-For convenience, simply copy the \texttt{interact.cls} file into the same directory as your manuscript files (you do not need to install it in your \TeX\ distribution).
-In order to use the \texttt{interact} document class, replace the command \verb"\documentclass{article}" at the beginning of your document with the command \verb"\documentclass{interact}".
-
-The following document-class options should \emph{not} be used with the \texttt{interact} class file:
-\begin{itemize}
-  \item \texttt{10pt}, \texttt{11pt}, \texttt{12pt} -- unavailable;
-  \item \texttt{oneside}, \texttt{twoside} -- not necessary, \texttt{oneside} is the default;
-  \item \texttt{leqno}, \texttt{titlepage} -- should not be used;
-  \item \texttt{twocolumn} -- should not be used (see Subsection~\ref{class});
-  \item \texttt{onecolumn} -- not necessary as it is the default style.
-\end{itemize}
-To prepare a manuscript for a journal that is printed in A4 (two column) format, use the \verb"largeformat" document-class option provided by \texttt{interact.cls}; otherwise the class file produces pages sized for B5 (single column) format by default.
-The \texttt{geometry} package should not be used to make any further adjustments to the page dimensions.
-
-%If your manuscript has supplementary content you can also use the \verb"interact" class file to prepare all or part of it using the \verb"suppldata" document-class option, which will suppress the `article history' date.
-This option \emph{must not} be used on any primary content.
-Note that authors are solely responsible for the preparation of all supplemental material.
-
-\section{Additional features of the \texttt{interact} class file}
-
-\subsection{Title, authors' names and affiliations, abstracts and article types}
-
-The title should be generated at the beginning of your article using the \verb"\maketitle" command.
-In the final version the author name(s) and affiliation(s) must be followed immediately by \verb"\maketitle" as shown below in order for them to be displayed in your PDF document.
-To prepare an anonymous version for double-blind peer review, you can put the \verb"\maketitle" between the \verb"\title" and the \verb"\author" in order to hide the author name(s) and affiliation(s) temporarily.
-Next you should include the abstract if your article has one, enclosed within an \texttt{abstract} environment.
-The \verb"\articletype" command is also provided as an \emph{optional} element which should \emph{only} be included if your article actually needs it.
-For example, the titles for this document begin as follows:
-\begin{verbatim}
-\articletype{ARTICLE TEMPLATE}
-
-\title{Taylor \& Francis \LaTeX\ template for authors (\textsf{Interact}
-layout + NLM reference style)}
-
-\author{
-\name{A.~N. Author\textsuperscript{a}\thanks{CONTACT A.~N. Author.
-Email: latex.helpdesk@tandf.co.uk} and John Smith\textsuperscript{b}}
-\affil{\textsuperscript{a}Taylor \& Francis, 4 Park Square, Milton
-Park, Abingdon, UK; \textsuperscript{b}Institut f\"{u}r Informatik,
-Albert-Ludwigs-Universit\"{a}t, Freiburg, Germany} }
-
-\maketitle
-
-\begin{abstract}
-This template is for authors who are preparing a manuscript for a
-Taylor \& Francis journal using the \LaTeX\ document preparation system
-and the \texttt{interact} class file, which is available via selected
-journals' home pages on the Taylor \& Francis website.
-\end{abstract}
-\end{verbatim}
-
-An additional abstract in another language (preceded by a translation of the article title) may be included within the \verb"abstract" environment if required.
-
-A graphical abstract may also be included if required. Within the \verb"abstract" environment you can include the code
-\begin{verbatim}
-\\\resizebox{25pc}{!}{\includegraphics{abstract.eps}}
-\end{verbatim}
-where the graphical abstract is to appear, where \verb"abstract.eps" is the name of the file containing the graphic (note that \verb"25pc" is the recommended maximum width, expressed in pica, for the graphical abstract in your manuscript).
-
-\subsection{Abbreviations}
-
-A list of abbreviations may be included if required, enclosed within an \texttt{abbreviations} environment, i.e.\ \verb"\begin{abbreviations}"\ldots\verb"\end{abbreviations}", immediately following the \verb"abstract" environment.
-
-\subsection{Keywords}
-
-A list of keywords may be included if required, enclosed within a \texttt{keywords} environment, i.e.\ \verb"\begin{keywords}"\ldots\verb"\end{keywords}".
-Additional keywords in other languages (preceded by a translation of the word `keywords') may also be included within the \verb"keywords" environment if required.
-
-\subsection{Subject classification codes}
-
-AMS, JEL or PACS classification codes may be included if required.
-The \texttt{interact} class file provides an \texttt{amscode} environment, i.e.\ \verb"\begin{amscode}"\ldots\verb"\end{amscode}", a \texttt{jelcode} environment, i.e.\ \verb"\begin{jelcode}"\ldots\verb"\end{jelcode}", and a \texttt{pacscode} environment, i.e.\ \verb"\begin{pacscode}"\ldots\verb"\end{pacscode}" to assist with this.
-
-\subsection{Additional footnotes to the title or authors' names}
-
-The \verb"\thanks" command may be used to create additional footnotes to the title or authors' names if required. Footnote symbols for this purpose should be used in the order
-$^\ast$~(coded as \verb"$^\ast$"), $\dagger$~(\verb"$\dagger$"), $\ddagger$~(\verb"$\ddagger$"), $\S$~(\verb"$\S$"), $\P$~(\verb"$\P$"), $\|$~(\verb"$\|$"),
-$\dagger\dagger$~(\verb"$\dagger\dagger$"), $\ddagger\ddagger$~(\verb"$\ddagger\ddagger$"), $\S\S$~(\verb"$\S\S$"), $\P\P$~(\verb"$\P\P$").
-
-Note that any \verb"footnote"s to the main text will automatically be assigned the superscript symbols 1, 2, 3, etc.
-by the class file.\footnote{If preferred, the \texttt{endnotes} package may be used to set the notes at the end of your text, before the bibliography.
-The symbols will be changed to match the style of the journal if necessary by the typesetter.}
-
-\section{Some guidelines for using the standard features of \LaTeX}
-
-\subsection{Sections}
-
-The \textsf{Interact} layout style allows for five levels of section heading, all of which are provided in the \texttt{interact} class file using the standard \LaTeX\ commands \verb"\section", \verb"\subsection", \verb"\subsubsection", \verb"\paragraph" and \verb"\subparagraph".
-Numbering will be automatically generated for all these headings by default.
-
-\subsection{Lists}
-
-Numbered lists are produced using the \texttt{enumerate} environment, which will number each list item with arabic numerals by default. For example,
-\begin{enumerate}
-  \item first item
-  \item second item
-  \item third item
-\end{enumerate}
-was produced by
-\begin{verbatim}
-\begin{enumerate}
-  \item first item
-  \item second item
-  \item third item
-\end{enumerate}
-\end{verbatim}
-Alternative numbering styles can be achieved by inserting an optional argument in square brackets to each \verb"item", e.g.\ \verb"\item[(i)] first item"\, to create a list numbered with roman numerals at level one.
-
-Bulleted lists are produced using the \texttt{itemize} environment. For example,
-\begin{itemize}
-  \item First bulleted item
-  \item Second bulleted item
-  \item Third bulleted item
-\end{itemize}
-was produced by
-\begin{verbatim}
-\begin{itemize}
-  \item First bulleted item
-  \item Second bulleted item
-  \item Third bulleted item
-\end{itemize}
-\end{verbatim}
-
-\subsection{Figures}
-
-The \texttt{interact} class file will deal with positioning your figures in the same way as standard \LaTeX.
-It should not normally be necessary to use the optional \texttt{[htb]} location specifiers of the \texttt{figure} environment in your manuscript; you may, however, find the \verb"[p]" placement option or the \verb"endfloat" package useful if a journal insists on the need to separate figures from the text.
-
-Figure captions appear below the figures themselves, therefore the \verb"\caption" command should appear after the body of the figure.
-For example, Figure~\ref{sample-figure} with caption and sub-captions is produced using the following commands:
-\begin{verbatim}
-\begin{figure}
-\centering
-\subfloat[An example of an individual figure sub-caption.]{%
-\resizebox*{5cm}{!}{\includegraphics{graph1.eps}}}\hspace{5pt}
-\subfloat[A slightly shorter sub-caption.]{%
-\resizebox*{5cm}{!}{\includegraphics{graph2.eps}}}
-\caption{Example of a two-part figure with individual sub-captions
- showing that captions are flush left and justified if greater
- than one line of text.} \label{sample-figure}
-\end{figure}
-\end{verbatim}
-\begin{figure}
-\centering
-\subfloat[An example of an individual figure sub-caption.]{%
-\resizebox*{5cm}{!}{\includegraphics{graph1.eps}}}\hspace{5pt}
-\subfloat[A slightly shorter sub-caption.]{%
-\resizebox*{5cm}{!}{\includegraphics{graph2.eps}}}
-\caption{Example of a two-part figure with individual sub-captions
- showing that captions are flush left and justified if greater
- than one line of text.} \label{sample-figure}
-\end{figure}
-
-To ensure that figures are correctly numbered automatically, the \verb"\label" command should be included just after the \verb"\caption" command, or in its argument.
-
-The \verb"\subfloat" command requires \verb"subfig.sty", which is called in the preamble of the \texttt{interactnlmsample.tex} file (to allow your choice of an alternative package if preferred) and included in the \textsf{Interact} \LaTeX\ bundle for convenience.
-Please supply any additional figure macros used with your article in the preamble of your .tex file.
-
-The source files of any figures will be required when the final, revised version of a manuscript is submitted.
-Authors should ensure that these are suitable (in terms of lettering size, etc.) for the reductions they envisage.
-
-The \texttt{epstopdf} package can be used to incorporate encapsulated PostScript (.eps) illustrations when using PDF\LaTeX, etc.
-Please provide the original .eps source files rather than the generated PDF images of those illustrations for production purposes.
-
-\subsection{Tables}
-
-The \texttt{interact} class file will deal with positioning your tables in the same way as standard \LaTeX.
-It should not normally be necessary to use the optional \texttt{[htb]} location specifiers of the \texttt{table} environment in your manuscript; you may, however, find the \verb"[p]" placement option or the \verb"endfloat" package useful if a journal insists on the need to separate tables from the text.
-
-The \texttt{tabular} environment can be used as shown to create tables with single horizontal rules at the head, foot and elsewhere as appropriate.
-The captions appear above the tables in the \textsf{Interact} style, therefore the \verb"\tbl" command should be used before the body of the table.
-For example, Table~\ref{sample-table} is produced using the following commands:
-\begin{table}
-\tbl{Example of a table showing that its caption is as wide as
- the table itself and justified.}
-{\begin{tabular}{lcccccc} \toprule
- & \multicolumn{2}{l}{Type} \\ \cmidrule{2-7}
- Class & One & Two & Three & Four & Five & Six \\ \midrule
- Alpha\textsuperscript{a} & A1 & A2 & A3 & A4 & A5 & A6 \\
- Beta & B2 & B2 & B3 & B4 & B5 & B6 \\
- Gamma & C2 & C2 & C3 & C4 & C5 & C6 \\ \bottomrule
-\end{tabular}}
-\tabnote{\textsuperscript{a}This footnote shows how to include
- footnotes to a table if required.}
-\label{sample-table}
+Notably, the MDEIM-ROM is cheaper than the direct projection ROM with a speed-up that depends on the original model size.
+More importantly, the MDEIM-ROM cost is slightly dependent on the problem dimension while the ROM time increases with the grid size because the operator projection is performed at each time step.
+The shown MEDIM-ROM time includes the offline cost which involves the operator $\mathbf{L}$ decomposition and the projection of the decomposed matrices.
+Also, both the ROM and MDEIM-ROM times include the time to reconstruct of the full-order solution.
+
+%------------------------------------------------------------------------------------------------%
+\subsubsection{Parametric ROM Results}
+
+In the previous section, the developed ROM was used to reconstruct the solution using a POD subspace obtained from snapshots generated using the same parameter point at which the solution is sought.
+Here, our purpose is to extend the capability of the developed ROM to perform parametric studies.
+However, it is important to clarify that it is not our goal in this study to quantify output uncertainties or perform statistical analysis.
+Instead, we merely aim to measure the prediction error of the ROM at new parameter points using a POD subspace sampled from a parameter domain of interest.
+A case study was performed in which the parameters of interest are assumed to be the kinetic data, i.e., the delayed neutron fractions and the decay constants.
+A POD greedy sampling was used to construct a global POD subspace.
+Although the original benchmark employs two precursor groups, it was more convenient in this study to use six groups to enlarge the parameter space.
+Shown in Table \ref{tab: 6 groups precursor data} are the parameters normal distributions data adopted from Refs.~\cite{keepin1957delayed, tuttle1975delayed}.
+A POD greedy sampling is used for which a set of 50 parameters points were generated to obtain a global POD space, where at each iteration, three POD basis vectors are added to the space.
+A grid of $22\times 22$ is used throughout this study.
+A greedy algorithm stopping criteria was used such that the iteration terminates if the relative norm of the flux error is $1\times10^{-4}$ or the POD space has a size of 6 (i.e., 20 parameters points are selected).
+As noted earlier, there are no general prior criteria for selecting these parameters.
+
+\begin{table}[h!]
+	\centering
+	\begin{tabular}{c|l|l}
+		group i& $\beta_i \pm \sigma_{\beta_i}$  & $\lambda_i\pm \sigma_{\lambda_i} (s)^{-1}$)  \\
+		\hline
+		1    &  $0.038\pm 0.004$ & $0.0127 \pm 0.0003$ \\
+		2    &  $0.213 \pm 0.007$  & $0.0317 \pm 0.0012$ \\
+		3    &  $0.188 \pm 0.024$ & $0.1150 \pm 0.0040$ \\
+		4    &  $0.407 \pm 0.010$ & $0.3110 \pm 0.0120$ \\
+		5    &  $0.128 \pm 0.012$ & $1.4000\pm0.1200$ \\
+		6    &  $0.026\pm0.004$ & $3.8700\pm0.5500$ \\
+	\end{tabular}
+	\caption{6 groups delayed neutron precursor data.}
+	\label{tab: 6 groups precursor data}
 \end{table}
-\begin{verbatim}
-\begin{table}
-\tbl{Example of a table showing that its caption is as wide as
- the table itself and justified.}
-{\begin{tabular}{lcccccc} \toprule
- & \multicolumn{2}{l}{Type} \\ \cmidrule{2-7}
- Class & One & Two & Three & Four & Five & Six \\ \midrule
- Alpha\textsuperscript{a} & A1 & A2 & A3 & A4 & A5 & A6 \\
- Beta & B2 & B2 & B3 & B4 & B5 & B6 \\
- Gamma & C2 & C2 & C3 & C4 & C5 & C6 \\ \bottomrule
-\end{tabular}}
-\tabnote{\textsuperscript{a}This footnote shows how to include
- footnotes to a table if required.}
-\label{sample-table}
-\end{table}
-\end{verbatim}
-
-To ensure that tables are correctly numbered automatically, the \verb"\label" command should be included just before \verb"\end{table}".
-
-The \verb"\toprule", \verb"\midrule", \verb"\bottomrule" and \verb"\cmidrule" commands are those used by \verb"booktabs.sty", which is called by the \texttt{interact} class file and included in the \textsf{Interact} \LaTeX\ bundle for convenience.
-Tables produced using the standard commands of the \texttt{tabular} environment are also compatible with the \texttt{interact} class file.
-
-\subsection{Landscape pages}
-
-If a figure or table is too wide to fit the page it will need to be rotated, along with its caption, through 90$^{\circ}$ anticlockwise.
-Landscape figures and tables can be produced using the \verb"rotating" package, which is called by the \texttt{interact} class file.
-The following commands (for example) can be used to produce such pages.
-\begin{verbatim}
-\setcounter{figure}{1}
-\begin{sidewaysfigure}
-\centerline{\epsfbox{figname.eps}}
-\caption{Example landscape figure caption.}
-\label{landfig}
-\end{sidewaysfigure}
-\end{verbatim}
-\begin{verbatim}
-\setcounter{table}{1}
-\begin{sidewaystable}
- \tbl{Example landscape table caption.}
-  {\begin{tabular}{@{}llllcll}
-    .
-    .
-    .
-  \end{tabular}}\label{landtab}
-\end{sidewaystable}
-\end{verbatim}
-Before any such float environment, use the \verb"\setcounter" command as above to fix the numbering of the caption (the value of the counter being the number given to the preceding figure or table).
-Subsequent captions will then be automatically renumbered accordingly.
-The \verb"\epsfbox" command requires \verb"epsfig.sty", which is called by the \texttt{interact} class file and is also included in the \textsf{Interact} \LaTeX\ bundle for convenience.
-
-Note that if the \verb"endfloat" package is used, one or both of the commands
-\begin{verbatim}
-\DeclareDelayedFloatFlavor{sidewaysfigure}{figure}
-\DeclareDelayedFloatFlavor{sidewaystable}{table}
-\end{verbatim}
-will need to be included in the preamble of your .tex file, after the \verb"endfloat" package is loaded, in order to process any landscape figures and/or tables correctly.
-
-\subsection{Theorem-like structures}
-
-A predefined \verb"proof" environment is provided by the \texttt{amsthm} package (which is called by the \texttt{interact} class file), as follows:
-\begin{proof}
-More recent algorithms for solving the semidefinite programming relaxation are particularly efficient, because they explore the structure of the MAX-CUT problem.
-\end{proof}
-\noindent This was produced by simply typing:
-\begin{verbatim}
-\begin{proof}
-More recent algorithms for solving the semidefinite programming
-relaxation are particularly efficient, because they explore the
-structure of the MAX-CUT problem.
-\end{proof}
-\end{verbatim}
-Other theorem-like environments (theorem, definition, remark, etc.) need to be defined as required, e.g.\ using \verb"\newtheorem{theorem}{Theorem}" in the preamble of your .tex file (see the preamble of \verb"interactnlmsample.tex" for more examples).
-You can define the numbering scheme for these structures however suits your article best.
-Please note that the format of the text in these environments may be changed if necessary to match the style of individual journals by the typesetter during preparation of the proofs.
-
-\subsection{Mathematics}
-
-\subsubsection{Displayed mathematics}
-
-The \texttt{interact} class file will set displayed mathematical formulas centred on the page without equation numbers if you use the \texttt{displaymath} environment or the equivalent \verb"\[...\]" construction.
-For example, the equation
-\[
- \hat{\theta}_{w_i} = \hat{\theta}(s(t,\mathcal{U}_{w_i}))
-\]
-was typeset using the commands
-\begin{verbatim}
-\[
- \hat{\theta}_{w_i} = \hat{\theta}(s(t,\mathcal{U}_{w_i}))
-\]
-\end{verbatim}
-
-For those of your equations that you wish to be automatically numbered sequentially throughout the text for future reference, use the \texttt{equation} environment, e.g.
-\begin{equation}
- \hat{\theta}_{w_i} = \hat{\theta}(s(t,\mathcal{U}_{w_i}))
-\end{equation}
-was typeset using the commands
-\begin{verbatim}
-\begin{equation}
- \hat{\theta}_{w_i} = \hat{\theta}(s(t,\mathcal{U}_{w_i}))
-\end{equation}
-\end{verbatim}
-
-Part numbers for sets of equations may be generated using the \texttt{subequations} environment, e.g.
-\begin{subequations} \label{subeqnexample}
-\begin{equation}
-     \varepsilon \rho w_{tt}(s,t) = N[w_{s}(s,t),w_{st}(s,t)]_{s},
-     \label{subeqnparta}
-\end{equation}
-\begin{equation}
-     w_{tt}(1,t)+N[w_{s}(1,t),w_{st}(1,t)] = 0,   \label{subeqnpartb}
-\end{equation}
-\end{subequations}
-which was typeset using the commands
-\begin{verbatim}
-\begin{subequations} \label{subeqnexample}
-\begin{equation}
-     \varepsilon \rho w_{tt}(s,t) = N[w_{s}(s,t),w_{st}(s,t)]_{s},
-     \label{subeqnparta}
-\end{equation}
-\begin{equation}
-     w_{tt}(1,t)+N[w_{s}(1,t),w_{st}(1,t)] = 0,   \label{subeqnpartb}
-\end{equation}
-\end{subequations}
-\end{verbatim}
-This is made possible by the \texttt{amsmath} package, which is called by the class file.
-If you put a \verb"\label" just after the \verb"\begin{subequations}" command, references can be made to the collection of equations, i.e.\ `(\ref{subeqnexample})' in the example above.
-Or, as the example also shows, you can label and refer to each equation individually -- i.e.\ `(\ref{subeqnparta})' and `(\ref{subeqnpartb})'.
-
-Displayed mathematics should be given end-of-line punctuation appropriate to the running text sentence of which it forms a part, if required.
-
-\subsubsection{Math fonts}
-
-\paragraph{Superscripts and subscripts}
-Superscripts and subscripts will automatically come out in the correct size in a math environment (i.e.\ enclosed within \verb"\(...\)" or \verb"$...$" commands in running text, or within \verb"\[...\]" or the \texttt{equation} environment for displayed equations).
-Sub/superscripts that are physical variables should be italic, whereas those that are labels should be roman (e.g.\ $C_p$, $T_\mathrm{eff}$).
-If the subscripts or superscripts need to be other than italic, they must be coded individually.
-
-\paragraph{Upright Greek characters and the upright partial derivative sign}
-Upright lowercase Greek characters can be obtained by inserting the letter `u' in the control code for the character, e.g.\ \verb"\umu" and \verb"\upi" produce $\umu$ (used, for example, in the symbol for the unit microns -- $\umu\mathrm{m}$) and $\upi$ (the ratio of the circumference of a circle to its diameter).
-Similarly, the control code for the upright partial derivative $\upartial$ is \verb"\upartial".
-Bold lowercase as well as uppercase Greek characters can be obtained by \verb"{\bm \gamma}", for example, which gives ${\bm \gamma}$, and \verb"{\bm \Gamma}", which gives ${\bm \Gamma}$.
-
-\section*{Acknowledgement(s)}
-
-An unnumbered section, e.g.\ \verb"\section*{Acknowledgements}", may be used for thanks, etc.\ if required and included \emph{in the non-anonymous version} before any Notes or References.
-
-\section*{Disclosure statement}
-
-An unnumbered section, e.g.\ \verb"\section*{Disclosure statement}", may be used to declare any potential conflict of interest and included \emph{in the non-anonymous version} before any Notes or References, after any Acknowledgements and before any Funding information.
-
-\section*{Funding}
-
-An unnumbered section, e.g.\ \verb"\section*{Funding}", may be used for grant details, etc.\ if required and included \emph{in the non-anonymous version} before any Notes or References.
-
-\section*{Notes on contributor(s)}
-
-An unnumbered section, e.g.\ \verb"\section*{Notes on contributors}", may be included \emph{in the non-anonymous version} if required. A photograph may be added if requested.
-
-\section*{Nomenclature/Notation}
-
-An unnumbered section, e.g.\ \verb"\section*{Nomenclature}" (or \verb"\section*{Notation}"), may be included if required, before any Notes or References.
-
-\section*{Notes}
-
-An unnumbered `Notes' section may be included before the References (if using the \verb"endnotes" package, use the command \verb"\theendnotes" where the notes are to appear, instead of creating a \verb"\section*").
-
-\section{References}
-
-\subsection{References cited in the text}
-
-References should be cited in accordance with US National Library of Medicine (NLM) style.
-References are cited in the text by a number in square brackets (e.g.
-[1], [2,4,10], [11--15], \emph{not} [11]--[15]), in the order in which they first appear.
-For further details on this reference style, see the Instructions for Authors on the Taylor \& Francis website.
-
-Each bibliographic entry has a key, which is assigned by the author and is used to refer to that entry in the text.
-In this document, the key \verb"Jen05" in the citation form \verb"\cite{Jen05}" produces `\cite{Jen05}', and the keys \verb"{Sch02,Wen95}" in the citation form \verb"\cite{Sch02,Wen95}" produce `\cite{Sch02,Wen95}'.
-The citation for a range of bibliographic entries (e.g.\ `\cite{Sha78,AG98,Smi75,Men05,DCK03,Hor98,Ant03,Zha05,Rog05,SRW05}') will automatically be produced by  \verb"\cite{Sha78,AG98,Smi75,Men05,DCK03,Hor98,Ant03,Zha05,Rog05,SRW05}".
-Optional notes may be included at the beginning and/or end of a citation by the use of square brackets, e.g.\ \verb"\cite[cf.][]{Gau05}" produces `\cite[cf.][]{Gau05}', \verb"\cite[p.356]{BGC04}" produces `\cite[p.356]{BGC04}', and \verb"\cite[see][p.73-–77]{PI51}" produces `\cite[see][p.73--77]{PI51}'.
-
-%\subsection{The list of references}
-%
-%References should be listed at the end of the main text in the order in which they are first cited in the text.
-The following list shows some sample references prepared in the Taylor \& Francis NLM style.
-%
-%\bibliography{references}
-%
-%\begin{thebibliography}{99}
-%
-%\bibitem{Jen05}%1
-%Jenkins~PF. Making sense of the chest x-ray: a hands-on guide. New York (NY):
-%  Oxford University Press; 2005.
-%
-%\bibitem{Sch02}%2
-%Schott~J, Priest~J. Leading antenatal classes: a practical guide. 2nd ed.
-%  Boston (MA): Books for Midwives; 2002.
-%
-%\bibitem{Wen95}%3
-%Wenger~NK, Sivarajan~Froelicher~E, Smith~LK, et~al. Cardiac rehabilitation.
-%  Rockville (MD): Agency for Health Care Policy and Research (US); 1995.
-%
-%\bibitem{Sha78}%4
-%Shakelford~RT. Surgery of the alimentary tract. Philadelphia (PA): W.B.
-%  Saunders; 1978. Chapter 2, Esophagoscopy; p. 29--40.
-%
-%\bibitem{AG98}%5
-%Ambudkar~SV, Gottesman~MM, editors. {ABC} transporters: biomedical, cellular,
-%  and molecular aspects. San Diego (CA): Academic Press; 1998. (Methods in
-%  enzymology; vol. 292).
-%
-%\bibitem{Smi75}%6
-%Smith~CE. The significance of mosquito longevity and blood-feeding behaviour in
-%  the dynamics of arbovirus infections. Med Biol. 1975;53:288--294.
-%
-%\bibitem{Men05}%7
-%Meneton~P, Jeunemaitre~X, de~Wardener~HE, et~al. Links between dietary salt
-%  intake, renal salt handling, blood pressure, and cardiovascular diseases.
-%  Physiol Rev. 2005 Apr;85:679--715.
-%
-%\bibitem{DCK03}%8
-%Dostorovsky~JO, Carr~DB, Koltzenburg~M, editors. Proceedings of the 10th World
-%  Congress on Pain; 2002 Aug~17--22; San Diego, CA. Seattle: IASP Press; c2003.
-%
-%\bibitem{Hor98}%9
-%Horrobin~DF, Lampinskas~P. The commercial development of food plants used as
-%  medicines. In: Prendergast~HD, Etkin~NL, Harris~DR, et~al., editors. Plants
-%  for food and medicine. Proceedings of the Joint Conference of the Society for
-%  Economic Botany and the International Society for Ethnopharmacology; 1996
-%  Jul~1--6; London. Kew (UK): Royal Botanic Gardens; 1998. p. 75--81.
-%
-%\bibitem{Ant03}%10
-%Antani~S, Long~LR, Thoma~GR, et~al. Anatomical shape representation in spine
-%  x-ray images. Paper presented at: VIIP 2003. Proceedings of the 3rd IASTED
-%  International Conference on Visualization, Imaging and Image Processing;
-%  2003 Sep~8--10; Benalmadena, Spain.
-%
-%\bibitem{Zha05}%11
-%Zhao~C. Development of nanoelectrospray and application to protein research and
-%  drug discovery [dissertation]. Buffalo (NY): State University of New York at
-%  Buffalo; 2005.
-%
-%\bibitem{Rog05}%12
-%Roguskie~JM. The role of \emph{Pseudomonas aeruginosa} 1244 pilin glycan in
-%  virulence [master's thesis]. [Pittsburgh (PA)]: Duquesne University; 2005.
-%
-%\bibitem{SRW05}%13
-%Savage~E, Ramsay~M, White~J, et~al. Mumps outbreaks across England and Wales
-%  in 2004: Observational study. BMJ. 2005;330(7500):1119--1120 [cited 2005
-%  May~31]; Available from: http://bmj.bmjjournals.com/cgi/reprint/330/7500/1119.
-%
-%\bibitem{Gau05}%14
-%Gaul~G. When geography influences treament options. Washington Post (Maryland
-%  Ed.). 2005 Jul~24;Sect.~A:12 (col.~1).
-%
-%\bibitem{BGC04}%15
-%Berrino~F, Gatta~G, Crosignani~P. [Case-control evaluation of screening
-%  efficacy]. Epidemiol Prev. 2004 Nov--Dec;28:354--359. Italian.
-%
-%\bibitem{PI51}%16
-%Piaget~J, Inhelder~B. La gen{\`e}se de l'id{\'e}e de hasard chez l'enfant
-%  [The origin of the idea of chance in the child]. Paris: Presses
-%  Universitaires de France; 1951.
-%  
-% \bibitem{elzohery-greedyPOD}
-% Elzohery, Rabab and Roberts, Jeremy [Modeling neutronic transients with Galerkin projection onto a greedy-sampled, POD subspace]. Annals of Nuclear Energy; 2021.
-
-%\end{thebibliography}
-%\bigskip
-%\noindent This was produced by typing:
-%\begin{verbatim}
-%\begin{thebibliography}{99}
-%
-%\bibitem{Jen05}%1
-%Jenkins~PF. Making sense of the chest x-ray: a hands-on guide. New York
-% (NY): Oxford University Press; 2005.
-%
-%\bibitem{Sch02}%2
-%Schott~J, Priest~J. Leading antenatal classes: a practical guide. 2nd
-% ed. Boston (MA): Books for Midwives; 2002.
-%
-%\bibitem{Wen95}%3
-%Wenger~NK, Sivarajan~Froelicher~E, Smith~LK, et~al. Cardiac
-% rehabilitation. Rockville (MD): Agency for Health Care Policy and
-% Research (US); 1995.
-%
-%\bibitem{Sha78}%4
-%Shakelford~RT. Surgery of the alimentary tract. Philadelphia (PA):
-% W.B. Saunders; 1978. Chapter 2, Esophagoscopy; p. 29--40.
-%
-%\bibitem{AG98}%5
-%Ambudkar~SV, Gottesman~MM, editors. {ABC} transporters: biomedical,
-% cellular, and molecular aspects. San Diego (CA): Academic Press; 1998.
-% (Methods in enzymology; vol. 292).
-%
-%\bibitem{Smi75}%6
-%Smith~CE. The significance of mosquito longevity and blood-feeding
-% behaviour in the dynamics of arbovirus infections. Med Biol.
-% 1975;53:288--294.
-%
-%\bibitem{Men05}%7
-%Meneton~P, Jeunemaitre~X, de~Wardener~HE, et~al. Links between dietary
-% salt intake, renal salt handling, blood pressure, and cardiovascular
-% diseases. Physiol Rev. 2005 Apr;85:679--715.
-%
-%\bibitem{DCK03}%8
-%Dostorovsky~JO, Carr~DB, Koltzenburg~M, editors. Proceedings of the
-% 10th World Congress on Pain; 2002 Aug~17--22; San Diego, CA. Seattle:
-% IASP Press; c2003.
-%
-%\bibitem{Hor98}%9
-%Horrobin~DF, Lampinskas~P. The commercial development of food plants
-% used as medicines. In: Prendergast~HD, Etkin~NL, Harris~DR, et~al.,
-% editors. Plants for food and medicine. Proceedings of the Joint
-% Conference of the Society for Economic Botany and the International
-% Society for Ethnopharmacology; 1996 Jul~1--6; London. Kew (UK): Royal
-% Botanic Gardens; 1998. p. 75--81.
-%
-%\bibitem{Ant03}%10
-%Antani~S, Long~LR, Thoma~GR, et~al. Anatomical shape representation in
-% spine x-ray images. Paper presented at: VIIP 2003. Proceedings of the
-% 3rd IASTED International Conference on Visualization, Imaging and
-% Image Processing; 2003 Sep~8--10; Benalmadena, Spain.
-%
-%\bibitem{Zha05}%11
-%Zhao~C. Development of nanoelectrospray and application to protein
-% research and drug discovery [dissertation]. Buffalo (NY): State
-% University of New York at Buffalo; 2005.
-%
-%\bibitem{Rog05}%12
-%Roguskie~JM. The role of \emph{Pseudomonas aeruginosa} 1244 pilin
-% glycan in virulence [master's thesis]. [Pittsburgh (PA)]: Duquesne
-% University; 2005.
-%
-%\bibitem{SRW05}%13
-%Savage~E, Ramsay~M, White~J, et~al. Mumps outbreaks across England and
-% Wales in 2004: Observational study. BMJ. 2005;330(7500):1119--1120
-% [cited 2005 May 31]; Available from:
-% http://bmj.bmjjournals.com/cgi/reprint/330/7500/1119.
-%
-%\bibitem{Gau05}%14
-%Gaul~G. When geography influences treament options. Washington Post
-% (Maryland Ed.). 2005 Jul~24;Sect.~A:12 (col.~1).
-%
-%\bibitem{BGC04}%15
-%Berrino~F, Gatta~G, Crosignani~P. [Case-control evaluation of screening
-% efficacy]. Epidemiol Prev. 2004 Nov--Dec;28:354--359. Italian.
-%
-%\bibitem{PI51}%16
-%Piaget~J, Inhelder~B. La gen{\`e}se de l'id{\'e}e de hasard chez
-% l'enfant [The origin of the idea of chance in the child]. Paris:
-% Presses Universitaires de France; 1951.
-%
-%\end{thebibliography}
-%\end{verbatim}
-%\bigskip
-%\noindent Each entry takes the form:
-%\begin{verbatim}
-%\bibitem{key}%n Bibliography entry
-%\end{verbatim}
-%where `\texttt{key}' is the tag that is to be used as an argument for the \verb"\cite{}" commands in the text of the article and `\texttt{Bibliography entry}' is the material that is to appear in the list of references, suitably formatted.
-The commands
-%\begin{verbatim}
-%\usepackage[numbers,sort&compress]{natbib}
-%\bibpunct[, ]{[}{]}{,}{n}{,}{,}
-%\renewcommand\bibfont{\fontsize{10}{12}\selectfont}
-%\makeatletter
-%\def\NAT@def@citea{\def\@citea{\NAT@separator}}
-%\makeatother
-%\end{verbatim}
-%need to be included in the preamble of your .tex file in order to generate the citations and bibliography as described above.
-%
-%Instead of typing the bibliography by hand, you may prefer to create the list of references using a \textsc{Bib}\TeX\ database.
-The \texttt{tfnlm.bst} file needs to be in your working folder or an appropriate directory, and the lines
-%\begin{verbatim}
-%\bibliographystyle{tfnlm}
-%\bibliography{interactnlmsample}
-%\end{verbatim}
-%included where the list of references is to appear, where \texttt{tfnlm.bst} is the name of the \textsc{Bib}\TeX\ bibliography style file for Taylor \& Francis' NLM reference style and \texttt{interactnlmsample.bib} is the bibliographic database included with the \textsf{Interact}-NLM \LaTeX\ bundle (to be replaced with the name of your own .bib file).
-\LaTeX/\textsc{Bib}\TeX\ will extract from your .bib file only those references that are cited in your .tex file and list them in the References section.
-%
-%Please include a copy of your .bib file and/or the final generated .bbl file among your source files if your .tex file does not contain a reference list in a \texttt{thebibliography} environment.
-
-\section{Appendices}
-
-Any appendices should be placed after the list of references, beginning with the command \verb"\appendix" followed by the command \verb"\section" for each appendix title, e.g.
-\begin{verbatim}
-\appendix
-\section{This is the title of the first appendix}
-\section{This is the title of the second appendix}
-\end{verbatim}
-produces:\medskip
-
-\noindent\textbf{Appendix A. This is the title of the first appendix}\medskip
-
-\noindent\textbf{Appendix B. This is the title of the second appendix}\medskip
-
-\noindent Subsections, equations, figures, tables, etc.\ within appendices will then be automatically numbered as appropriate.
-Some theorem-like environments may need to have their counters reset manually (e.g.\ if they are not numbered within sections in the main text).
-You can achieve this by using \verb"\numberwithin{remark}{section}" (for example) just after the \verb"\appendix" command.
-
-Note that if the \verb"endfloat" package is used on a document containing any appendices, the \verb"\processdelayedfloats" command must be included immediately before the \verb"\appendix" command in order to ensure that the floats belonging to the main body of the text are numbered as such.
-
-%\processdelayedfloats %%% See above for an explanation of why this command might be needed here.
-
-\appendix
-
-\section{Troubleshooting}
-
-Authors may occasionally encounter problems with the preparation of a manuscript using \LaTeX. The appropriate action to take will depend on the nature of the problem:
-\begin{enumerate}
-\item[(i)] If the problem is with \LaTeX\ itself, rather than with the actual macros, please consult an appropriate \LaTeXe\ manual for initial advice.
-If the solution cannot be found, or if you suspect that the problem does lie with the macros, then please contact Taylor \& Francis for assistance (\texttt{latex.helpdesk@tandf.co.uk}), clearly stating the title of the journal to which you are submitting.
-\item[(ii)] Problems with page make-up (e.g.\ occasional overlong lines of text; figures or tables appearing out of order): please do not try to fix these using `hard' page make-up commands -- the typesetter will deal with such problems.
-(You may, if you wish, draw attention to particular problems when submitting the final version of your manuscript.)
-\item[(iii)] If a required font is not available on your system, allow \TeX\ to substitute the font and specify which font is required in a covering letter accompanying your files.
-\end{enumerate}
-
-\section{Obtaining the template and class file}
-
-\subsection{Via the Taylor \& Francis website}
-
-This article template and the \texttt{interact} class file may be obtained via the `Instructions for Authors' pages of selected Taylor \& Francis journals.
-
-Please note that the class file calls up the open-source \LaTeX\ packages booktabs.sty, epsfig.sty and rotating.sty, which will, for convenience, unpack with the downloaded template and class file.
-The template calls for natbib.sty and subfig.sty, which are also supplied for convenience.
-
-\subsection{Via e-mail}
-
-This article template, the \texttt{interact} class file and the associated open-source \LaTeX\ packages are also available via e-mail.
-Requests should be addressed to \texttt{latex.helpdesk@tandf.co.uk}, clearly stating for which journal you require the template and class file.
-
+
+The MDEIM-ROM is sought to predict the power at every $0.001$ s during the transient, however, a time step of $0.005$ s was used in the greedy procedures.
+Shown in Fig.~\ref{fig:lra greedy error} is the flux error convergence with the greedy iterations.
+As shown, the maximum size of the POD space, i.e., 60, is reached before the error approaches the specified tolerance.
+The resulting POD basis was stored and used for testing the ROM.
+
+\begin{figure}[H]
+	\centering
+	\includegraphics[width=0.9\linewidth]{../figures/greedy_convergance.pdf}
+	\caption{Greedy error convergance}
+	\label{fig:lra greedy error}
+\end{figure}
+
+Thus, 50 new parameter samples were generated, and the ROM was executed with the resultant greedy basis.
+Moreover, the FOM was run at these testing parameter points, and the error between both models was computed.
+The quantities of interest were the assembly power at the peak and the maximum core temperature, i.e., the end-of-transient temperature.
+Note that the time to peak is different from sample to sample.
+Shown in Fig.~ \ref{fig:peak power mean error}, the sample mean of the assembly power error, at the peak, where the mean core maximum temperature error is shown in Fig.~\ref{fig:T mean error}.
+
+\begin{figure}[H]
+	\centering
+	\includegraphics[scale=1]{../figures/LRA_power_mean_err.pdf}
+	\caption{Sample mean of the core peak power}
+	\label{fig:peak power mean error}
+\end{figure}
+
+\begin{figure}[H]
+	\centering
+	\includegraphics[scale=1]{../figures/LRA_T_mean_err_peak.pdf}
+	\caption{Sample mean of the core maximum temperature}
+	\label{fig:T mean error}
+\end{figure}
+Among all samples, the maximum assembly power peak was $0.00111\%$, and the maximum temperature error was $2.9\times10^{-5}\%$.
+The resulting errors imply that the greedy-sampled POD subspace is rich with information from the whole parameters domain,
+and accordingly, resulted in a good approximation even for parameters not among the training sample.
+
+%------------------------------------------------------------------------------------------------------%
+\section{Conclusion}
+
+In this work, we developed a ROM to approximate neutronic transients with a lower computational cost.
+The main focus was treating non-linear models since they pose a challenge in terms of the computational cost even with using reduced-order models.
+The computational complexity associated with the ROM arises from requiring the problem operator to be projected at each iteration within the time step.
+In particular, performing the projection entails a number of FLOPs that depend on the original system dimension.
+Consequently, for high dimensional problems, the projection step could add significant cost to the ROM, reducing its efficiency.
+The ROM was built using the POD-Galerkin projection method to reduce the number of equations to be solved, and combined with the matrix version of DEIM to alleviate the burden associated with projecting the problem operator.
+The LRA benchmark representing a simplified multi-physics problem was the application used to illustrate the method.
+Using the MDEIM introduced FOMs speeds up that range from 4 to 50 depending on the numerical fidelity, with a maximum power relative error in the order of $1\times 10^{-5}$\%.
+More importantly, the computational saving gained from using the MDEIM-ROM is more than that of the direct projection ROM.
+
+In general, the use of ROMs becomes more appreciable with multi-run applications that need running the model with varying input parameters.
+Hence, the developed ROM was parameterized by means of POD-greedy sampling to generate a POD subspace global to a parameter domain of interest.
+The parameterized ROM in which the parameters of interest were the kinetic data, resulted in a maximum assembly power relative error across all testing parameter points that is in the order of $1\times 10^{-3}$\%.
+
+In terms of the practical implementation, an important concluding remark is that although the POD-Galerkin method is considered as an intrusive ROM technique, the implemented ROM did not require any major changes to the existing code, i.e, Detran,  making it a {\it trivially intrusive} technique.
+Rather, access only to the system operator, which represents all of the underlying system discretizations, was needed.
+This means that the presented ROM can be implemented in the many modern diffusion codes without making invasive changes to the working code.
+%------------------------------------------------------------------------------------------------------%
+
+\bibliography{interactnlmsample}
+
+%%----------------------------------------------
 \end{document}

### 2022-03-16 paper/interactnlmsample.tex
Jeremy's comments

@@
 \usepackage{booktabs,tabularx}
-\usepackage{subcaption}
+%\usepackage{subcaption}
 \DeclareMathOperator{\argmaxH}{argmax} 
@@
 \maketitle
-
 \begin{abstract}
-Presented here is an application of model-order reduction to non-linear neutronic transients, where reduced-order models (ROMs) are generally sought to provide a rapid and accurate approximation of a particular simulation solution.
-The ROM was built with the use of the POD-Galerkin projection method, where the main contribution of this work is the employment of the matrix version of the Discrete Empirical Interpolation Method (MDEIM) to improve the ROM efficiency.
-The MDEIM is used to approximate the projection of the problem operator that otherwise is required to be computed at each non-linear iteration within each time step, increasing the ROM cost.
+Presented here is an application of model-order reduction to non-linear neutronic transients.
+% where reduced-order models (ROMs) are generally sought to provide a rapid, yet accurate, approximation of a particular simulation response.
+The effort described extends previous work\cite{elzohery2021modeling} aimed to develop and assess a ROM framework that can be used for different purposes, such as design optimization and propagating input parameter uncertainties like nuclear data.
+Here, the target applications here is non-linear.
+The ROM was built with the use of the POD-Galerkin projection method and the matrix version of the Discrete Empirical Interpolation Method (MDEIM) for improved efficiency.
+The MDEIM is used to approximate the projection of the problem operator that otherwise must be computed at each non-linear iteration within each time step, which increases the ROM cost.
 By using the MDEIM, an offline-online ROM decomposition was obtained, which is favored from a computational perspective since the expensive projection operation can take place only once in the offline stage.
 The online stage, which involves solving a linear system  at each time step, depends only on the reduced dimension and is therefore cheap, making it possible to increase the solution time resolution, and accordingly accuracy, without introducing significant cost.
-By applying the method to the LRA benchmark, speeds up that range from 6 to 40 was achieved depending on the full-order model (FOM) spatial fidelity.
+By applying the method to the LRA benchmark, speed ups from 6 to 40 were achieved depending on the full-order model (FOM) spatial fidelity.
 The maximum relative error in the assemblies power was in the order of $1\times10^{-5}$\%.
-Moreover, the ROM was parameterized by using a POD-greedy sampling and a case study was tested where the kinetic data.
-i.e, the precursors decay constant and delayed neutron fraction, are assumed to be the parameters of interest.
-For the parameterized ROM, the maximum relative error in the assembly power was  \% ., which indicates that the developed ROM can be reliably used in parametric and uncertainty quantification studies.
-The computational gain from the MDEIM-ROM was compared with that of a direct projection ROM and showed that employing the MDEIM is computationally advantageous and becomes even more appreciable with higher-dimensional problems.
-The method was implemented in the open-source deterministic transport code Detran where only access to the system operator was needed to construct the ROM, and hence the method is considered trivially invasive and could be implemented in modern deterministic transport codes.
+Moreover, the ROM was parameterized by POD-greedy sampling, and a case study was performed where the kinetic data, i.e, the precursor decay constants and delayed-neutron fraction were assumed to be the model parameters of interest.
+For the parameterized ROM, the maximum relative error in the assembly power was $1\times 10^{-3}$\%, which implies that the developed ROM can be reliably used to accelerate parametric and uncertainty quantification studies involving non-linear problems.
+The computational gain from the MDEIM-ROM was compared with that of a direct projection ROM and showed that employing the MDEIM is computationally advantageous, and the advantage grows with dimension of the problem.
+The method was implemented in the open-source deterministic transport code Detran\cite{roberts2014advanced} where only access to the system operator was needed to construct the ROM, and; hence, the method is trivially invasive and could easily be implemented in many modern deterministic diffusion codes.
 
@@
 \section{Introduction}
-
-Modeling and simulation of reactor physics is crucial to understand nuclear reactors behavior under different conditions and scenarios and hence ensure reliable design and well established safety limits.
-The mathematical models governing the reactor physics are described by a set of equations that is challenging to solve analytically due to the geometric complexity of nuclear reactors except for simplified cases.
-Alternatively, these systems are solved by employing numerical discretization that rely on discretizing the system along each independent variable and the solution is provided only on these discrete points.
+Modeling and simulation of reactor physics is crucial to understanding nuclear reactors' behavior under different conditions and scenarios and hence ensure reliable designs and well-established safety limits.
+The mathematical models governing reactor physics are described by a set of equations that are challenging to solve analytically due to the geometric complexity of nuclear reactors except for simplified cases.
+Alternatively, these systems are solved by employing numerical discretization that relies on discretizing the system along each independent variable and the solution is provided only on these discrete points.
 To improve the method accuracy, the system needs to be solved over a very fine mesh.
@@
 Another popular approach is to use fixed-point iteration, with an implicit time scheme to iterate between difference physics within a time step until convergence is satisfied, which is computationally taxing.
-The aim of this work is to use a reduce-order model to overcome the high computational expense of these non-linear models.
+The aim of this work is to use a reduced-order model to overcome the high computational expense of these non-linear models.
 In particular, the ROM was developed using the POD-Galerkin projection.
-The method belongs to the projection-based family, and can be described as a physics-driven method since it requires knowledge of the original governing equation as will be shown in Sec.\ref{sec:POD}.
-In a previous work \cite{elzohery2021modeling}, we applied the method to time dependent diffusion equation where there was no coupling with other models and hence the application was linear.
+The method belongs to the projection-based family and can be described as a physics-driven method since it requires knowledge of the original governing equation as will be shown in Sec.\ref{sec:POD}.
+In a previous work \cite{elzohery2021modeling}, we applied the method to the time-dependent diffusion equation where there was no coupling with other models and hence the application was linear.
 In this study, the developed ROM was extended to treat the non-linearity induced by multi-physics modeling.
-To improve the computational efficiency of the developed ROM, a hyper-reduction technique known as the Discrete Empirical Interpolation Method (DEIM) was used in conjunction of the POD-Galerkin projection.
+To improve the computational efficiency of the developed ROM, a hyper-reduction technique known as the Discrete Empirical Interpolation Method (DEIM) was used in conjunction with the POD-Galerkin projection.
 The primary purpose of using the DEIM is to obtain an offline-online decomposition of the ROM to avoid repetitive projection of the problem operator at each iteration within the time step.
-The offline stage occurs only once and it comprises the expensive step of the ROM, where the online stage is cheaper and involves solving a reduced number of equation at each time step.
+The offline stage occurs only once and comprises the expensive step of the ROM.
+On the other hand, the online stage involves solving a reduced number of equations at each time step with a computational cost independent of the FOM dimension and hence cheaper.
 The LRA benchmark was used as a demonstrative application where the diffusion equation is coupled with a simplified thermal feedback model.
@@
 
-Consider the following dynamic system that results from discretizing a partial differential equation using a numerical scheme such as the finite difference method:
+Consider the following dynamic system that results from the discretization a partial differential equation using, e.g, the finite-difference method:
 \begin{equation}
@@
 In general, this method involves two main steps.
-First, a subspace is obtained using the proper orthogonal decomposition, i.e, POD \cite{}, a widely used reduction technique.
-Commonly, the POD subspace is generated using the snapshots method \cite{} by constructing a data matrix $\mathbf{Y}$ containing the system solutions at different time instances, then the singular value decomposition (SVD) is computed, i.e $\mathbf{Y} = \mathbf{U}\mathbf{\Sigma}\mathbf{V}$.
+First, a subspace is obtained using proper orthogonal decomposition (POD)\cite{volkwein2011model}.
+Commonly, the POD subspace is generated using the snapshots method \cite{sirovich1987turbulence} by constructing a data matrix $\mathbf{Y}$ containing the system solutions at different times of which the singular value decomposition (SVD) is computed, i.e, $\mathbf{Y} = \mathbf{U}\mathbf{\Sigma}\mathbf{V}^T$.
 The POD subspace is the one spanned by the first $r$ vectors of $\mathbf{U}$, where $r \ll n$.
-There is no general \textit{a priori} rule based on which the rank $r$ is chosen; however one can set a threshold $\epsilon$  such that
+There is no general \textit{a priori} rule based on which the rank $r$ is chosen; however, one can set a threshold $\epsilon$  such that
 \begin{equation}
@@
 \end{equation}
-where S$i$ is the $i$th singular value.
+where S$_i$ is the $i$th singular value and the singular values are the elements of the diagonal matrix $\mathbf{\Sigma}$.
 Upon obtaining the reduced space, the state variable $\mathbf{y}$ is expanded in terms of its basis
@@
 where $\mathbf{\hat{y}(t)} \in \mathbb{R}^{r}$ is a vector of the temporal coefficients.
-Second, the system is projected onto a POD subspace by multiplying the system on the left by $\mathbf{U}^T$ and making use of the orthogonality of the POD basis (i.e, $\mathbf{U}^T\mathbf{U} = \mathbf{I}$), we end up with
+Second, the system is projected onto a POD subspace by multiplying the system on the left by $\mathbf{U}^T$ and making use of the orthogonality of the POD basis (i.e, $\mathbf{U}^T\mathbf{U} = \mathbf{I}$), which leads to
 \begin{equation}
-	\frac{d\mathbf{\hat{y}}}{dt} = \mathbf{A}_r\mathbf{\hat{y}} + \mathbf{U}^T\mathbf{f}(\mathbf{U}\mathbf{\hat{y}}) \qquad \mathbf{\hat{y}}(0) = \mathbf{U}^T\mathbf{y}_0 \, ,
+	\frac{d\mathbf{\hat{y}}}{dt} = \mathbf{A}_r\mathbf{\hat{y}} + \mathbf{U}^T\mathbf{f}(\mathbf{U}\mathbf{\hat{y}})\, ,  \qquad \mathbf{\hat{y}}(0) = \mathbf{U}^T\mathbf{y}_0 \, ,
 	\label{eq:ROM}
@@
 Recently, the DEIM \cite{chaturantabut2010nonlinear} was proposed to approximate the non-linearity in the context of model-order reduction and to facilitate the online/offline decomposition of ROMs.
-The method is a discrete variant of the Empirical Interpolation Method (EIM) \cite{barrault2004empirical} that was originally proposed to approximate
-non-affine coefficient functions using a reduced-basis expansion to facilitate the online/offline decomposition in finite element methods.
+The method is a discrete variant of the Empirical Interpolation Method (EIM) \cite{barrault2004empirical} that was originally proposed to approximate non-affine coefficient functions using a reduced-basis expansion to facilitate the online/offline decomposition in finite-element methods.
 To illustrate the method, consider the model in Eq.\ref{eq:FOM} for which we seek an approximate ROM.
 The non-linear term $\mathbf{f}(\textbf{y}(t))$ introduces computational complexity to the ROM since computing the projected term $\mathbf{U}^T\mathbf{f}(\textbf{y}(t))$ requires reconstructing the full-order  solution first.
-The reconstruction and the projection steps have cost dependent on the dimension of the system, i.e $n$.
-The goal of using the DEIM is to avoid performing these operations at each time step and split the cost of the ROM into two steps,
-offline step where the expensive operations dependent on $n$ take place, and online step that depends only on the reduced dimension.
-The method relies on two main ingredients: (1) a reduced space that approximates the nonlinear function, and (2) a set of spatial interpolation indices.
+The reconstruction and the projection steps have costs dependent on the dimension of the system $n$.
+The goal of using the DEIM is to avoid performing these operations at each time step by splitting the ROM into two steps: an offline step in which the expensive operations dependent on $n$ are performed, and an online step in which operations depend only on the reduced dimension.
+The method relies on two main ingredients: (1) a reduced space in which nonlinear function can be approximated, and (2) a set of spatial interpolation indices.
 The nonlinear function $\mathbf{f}(\textbf{y}(t))$ is approximated by projecting it onto a subspace that approximates the function space
@@
 \end{equation}
-and the final function approximation is given by
+and the final approximation is given by
 \begin{equation}
@@
 \end{equation}
-A key point relevant to the computational efficiency of the method is that the matrix $\mathbf{P}$ does not need to be constructed explicitly, since the term $\mathbf{P}^T\mathbf{f}$ extracts only the elements of $\mathbf{f}$ that correspond to the interpolation indices.
+A key point relevant to the computational efficiency of the method is that the matrix $\mathbf{P}$ does not need to be constructed explicitly since the term $\mathbf{P}^T\mathbf{f}$ extracts only the elements of $\mathbf{f}$ that correspond to the interpolation indices.
 Thus, at each time step, only $k$ elements $\mathbf{f}$ need to be evaluated.
@@
 Now, the projection can be performed by computing the term $\mathbf{U}^T \mathbf{\Psi}$ once in an offline stage, while in the online stage, the vector $\boldsymbol{\theta}$ is computed by solving the linear system of dimension $k$ in Eq.~\ref{eq:DEIM coefficients}.
-Thus, the cost of the online computation depends on the reduced dimension $k$, not the original, high dimension $n$.
+Thus, the cost of the online computation depends on the reduced dimension $k$, not the original, larger dimension $n$.
 
@@
 The DEIM procedures can be used to approximate the operator by a summation of few time independent matrices, each weighted by a temporal coefficient.
-First, the matrix can be cast in a vector form by stacking all of its nonzero elements in one vector $\mathbf{a}(t) \in \mathbb{R}^{n^2}$.
+First, the matrix can be cast in a vector form by stacking its elements in one vector $\mathbf{a}(t) \in \mathbb{R}^{n^2}$.
 This vector can be treated in the same exact way as the function $\mathbf{f}(t)$ in the previous section, i.e, $\mathbf{a}(\mu) = \mathbf{\Psi}\boldsymbol{\theta}(t)$.
@@
 
-In the practical implementations, the method efficiency can be improved, as suggested in Ref. \cite{negri2015efficient}.
+In practical implementations, the method efficiency can be improved, as suggested in Ref. \cite{negri2015efficient}.
 First, the matrix $\mathbf{A}$ is, generally, largely sparse, which leads to a snapshots matrix that is sparse, too.
@@
 which should be appreciably more efficient in terms of memory and computational expense.
-In addition, to obtain the expansion coefficients ($\boldsymbol{\theta}$), the term $\mathbf{P}^T\mathbf{a(t)}$ needs to be computed at each new parameter value.
+In addition, to obtain the expansion coefficients ($\boldsymbol{\theta}$), the term $\mathbf{P}^T\mathbf{a(t)}$ needs to be computed at each new time step.
 In fact, this term only extracts the elements of $\mathbf{a(t)}$ that corresponds to the selected  interpolation indices.
@@
 When the matrix is formed in the online stage, only these entries are evaluated by restricting a \textit{for loop} over these row-column pairs, leading to more reduction in the computational cost.
+
+For the rest of this paper, we will refer to the ROM with MDEIM as the MDEIM-ROM, while we refer to the model in Sec.~\ref{sec:POD} as the direct projection ROM.
 
@@
 			\ENSURE A reduced space $\mathbf{\Psi}$, set of indices $\mathcal{I}$
-			\STATE $[\mathbf{\Psi}_1, \mathbf{\Psi}_2, ..., \mathbf{\Psi}_k ]$ = POD(${\mathbf{X}}, \epsilon$)\footnote{POD refers to Algorithm \ref{alg:pod}}
+			\STATE $[\mathbf{\Psi}_1, \mathbf{\Psi}_2, ..., \mathbf{\Psi}_k ]$ = POD(${\mathbf{X}}, \epsilon$)\footnote{POD refers to the POD procedures in Sec.~\ref{sec:POD}}
 			\STATE $\mathcal{I}_1 = \argmaxH(\abs{\mathbf{\Psi}_1})$, $\mathcal{I}$ = $\{\mathcal{I}_1\}$
@@
 The greedy subspace is initialized with the first $r_1$ POD basis computed from a randomly selected sample of the training data.
-Next, this subspace is used to compute the ROM prediction error of the state variable for the rest of the training samples.
+Using this subspace, the ROM prediction error of the state variable for the rest of the training samples is computed.
 The sample at which the error is worst is selected, and the subspace is enriched by adding the first $r_1$ POD basis computed from the selected sample snapshots.
@@
 Note that each time a new basis vector is added, the subspace is orthonormalized.
+
 Regarding the error criteria based on which a new sample is selected, there are two approaches. 
@@
 
-		\STATE set n=0
-
+		\STATE Set n=0; randomly choose $\boldsymbol{\mu}\in P_{train}$
+		\STATE Evaluate the FOM at $\boldsymbol{\mu}$, $\textbf Y(\boldsymbol{\mu})$:= $\{\textbf{y}^1, \textbf{y}^2, ..... \textbf{y}^k\}$
+		\STATE $\mathbf{U} := \{\zeta_1, \zeta_2, ......,\zeta_{r1}\} := \text{POD}(\textbf{Y}(\boldsymbol{\mu}))$
 		\WHILE {$\epsilon:= \Delta(\textbf{U}, \boldsymbol{\mu}_\text{ref}) > \epsilon_{tol}$ or $n < r$}
@@
 
-		\STATE evaluate the FOM at $\boldsymbol{\mu}$, $\textbf Y(\boldsymbol{\mu})$:= $\{\textbf{y}^1, \textbf{y}^2, ..... \textbf{y}^k\}$
+		\STATE Evaluate the FOM at $\boldsymbol{\mu}$, $\textbf Y(\boldsymbol{\mu})$:= $\{\textbf{y}^1, \textbf{y}^2, ..... \textbf{y}^k\}$
 
-		\STATE compute the POD modes of the FOM snapshots, $\{\zeta_1, \zeta_2, ......,\zeta_{r1}\} := \text{POD}(\textbf{Y}(\boldsymbol{\mu}), r_1)$
+		\STATE Compute the POD modes of the FOM snapshots, $\{\zeta_1, \zeta_2, ......,\zeta_{r1}\} := \text{POD}(\textbf{Y}(\boldsymbol{\mu}), r_1)$
 
-		\STATE Compute the SVD of $\textbf Y(\mu)$ and keep the first $r_1$ POD modes:$\{\zeta_1, \zeta_2, ......,\zeta_{r1}\}= \text{POD}(\textbf{y}^1, \textbf{y}^2, ..... \textbf{y}^k\}, r_1) $
-
-		\STATE $Z = \{Z, \{\zeta_1, \zeta_2, ....,\zeta_{r1}\}\}$ \text{and set} $n = n+r_1$
-
+%		\STATE Compute the SVD of $\textbf Y(\mu)$ and keep the first $r_1$ POD modes:$\{\zeta_1, \zeta_2, ......,\zeta_{r1}\}= \text{POD}(\textbf{y}^1, \textbf{y}^2, ..... \textbf{y}^k\}, r_1) $
+%%		
+%		\STATE $Z = \{Z, \{\zeta_1, \zeta_2, ....,\zeta_{r1}\}\}$ \text{and set} $n = n+r_1$
+%		
 		\STATE update the reduced space, $\textbf{U} := \textbf{U} \cup \{\zeta_1, \zeta_2, ..,\zeta_{r1}\} $ and orthonormalize
@@
 
-\subsection{Time Dependent Diffusion Equation}
+\subsection{The time-dependent diffusion equation}
 \label{sec:fom}
@@
 The control rod movement is represented by changing the thermal absorption cross section of the control rod material.
-In this application, the two-group diffusion equation represented in sec.\ref{sec:fom}, is coupled with thermal feedback through adiabatic fuel heat-up defined by
+In this application, the two-group diffusion equation represented in Sec.~\ref{sec:fom}, is coupled with thermal feedback through adiabatic fuel heat-up defined by
 \begin{equation}
@@
 
-Using the POD-Galerkin projection procedures described in Sec.~\ref{sec:POD}, a ROM was constructed to approximate the group flux and the core power of the LRA benchmark with increasing the spatial fidelity, i.e, spatial grids of $22\times 22$, $44\times44$ and $55 \times 55$ were used.\\
+The POD-Galerkin projection procedures described in Sec.~\ref{sec:POD} were applied to the system in Eq.~\ref{eq:transient fom} to approximate the group flux and the core power of the LRA benchmark with increasing the spatial fidelity, i.e, spatial grids of $22\times 22$, $44\times44$ and $55 \times 55$ were used.\\
 POD basis set was generated for each group flux while one basis set was generated for both precursors groups, i.e, 
@@
 
-For POD rank selection, the ROM was solved with different flux ranks and the relative L$_2$ norm of the flux errors are computed and are shown in Fig.~\ref{fig:POD flux rank}.
+For POD rank selection, the ROM was solved with different flux ranks and the mean relative L$_2$ flux errors are computed and are shown in Fig.~\ref{fig:POD flux rank}.
 \begin{figure}[h!]
@@
 \end{figure}
-A POD rank of 30 was selected fore each group flux since it results in an error less than   \% and the same rank was used for approximating the precursors concentration.
+A POD rank of 30 was selected fore each group flux since it results in a reasonably good error, i.e, less than 0.001\% and the same rank was used for approximating the precursors concentration.
 Higher ranks can be selected if a better ROM accuracy is desired.
-
 Furthermore, a ROM was constructed for the coupled thermal feedback model and the temperature field was approximated by projecting it onto a lower dimensional POD space
@@
 For selecting the temperature rank, i.e, $r_T$, the ROM was solved with different temperature ranks and the selected flux and precursors ranks.
-The core power relative error was computed in each case and is shown in Fig.~\ref{fig:temperature rank} based on which a POD of rank $10$ was selected for approximating the temperature.
+The mean core power relative error was computed in each case and is shown in Fig.~\ref{fig:temperature rank} based on which a POD of rank $10$ was selected for approximating the temperature since there was no improvement in the error for the higher ranks.
 
@@
 Shown in Fig.~\ref{fig:lra L singular values} are the singular values resulting from the SVD of the serialized operator snapshots. 
-Based on the shown plot, a MDEIM of order $15$ was used.
+A MDEIM of order $15$ was used since the singular-values decay by large magnitude around this value, however, higher orders can be chosen for higher accuracy.
 
@@
 Using the selected ranks in the previous subsection, MDEIM-ROMs were developed for full-order models of spatial grids $22\times 22$, $44\times44$ and $55 \times 55$.
-For brevity, we show the first four POD modes with their temporal coefficients of only the $55 \times 55$ grid in Fig.~\ref{fig:lra flux modes}.
+%For brevity, we show the first four POD modes with their temporal coefficients of only the $55 \times 55$ grid in Fig.~\ref{fig:lra flux modes}.
 %\begin{figure}[H]
@@
 %\end{figure}
-The absolute relative error in the predicted core powers are computed as shown in Fig.~\ref{fig:deim power error}.
+The ROMs were solved for the group flux from which the core power was computed.
+The absolute relative error in the predicted core powers are shown in Fig.~\ref{fig:deim power error}.
 
@@
 
-To understand the impact of employing the MDEIM on the error; the results are compared with these of a ROM without using the MDEIM, i.e., with performing direct operator projection at each time step.
+To understand the impact of employing the MDEIM on the error; the results are compared with these of a direct projection ROM, i.e., with performing direct operator projection at each time step.
 The relative difference of the power between both models is shown in Fig.~\ref{fig:rom-deim power error}.
@@
 	\includegraphics[width=1.0\linewidth]{../figures/LRA_mdeim_relative_error.pdf}
-	\caption{Relative difference in the predicted power between the ROM and the MDEIM-ROM.}
+	\caption{Relative difference in the predicted power between the direct projection ROM and the MDEIM-ROM.}
 	\label{fig:rom-deim power error}
@@
 	\begin{tabular}{c|c|c|c}  
-		Grid &	FOM (s)   &  ROM (s) & MDEIM-ROM (s)    \\
+		Grid &	FOM (s)   &  direct projection ROM (s) & MDEIM-ROM (s)    \\
 		\hline
@@
 Notably, the MDEIM-ROM is cheaper than the direct projection ROM with a speed-up that depends on the original model size.
-More importantly, the MDEIM-ROM cost is slightly dependent on the problem dimension while the ROM time increases with the grid size because the operator projection is performed at each time step.
+More importantly, the MDEIM-ROM cost is slightly dependent on the problem dimension while the other ROM time increases with the grid size because the operator projection is performed at each time step.
 The shown MEDIM-ROM time includes the offline cost which involves the operator $\mathbf{L}$ decomposition and the projection of the decomposed matrices.
-Also, both the ROM and MDEIM-ROM times include the time to reconstruct of the full-order solution.
+Also, both the ROMs times include the time to reconstruct of the full-order solution.
 

### 2022-03-28 paper/interactnlmsample.tex
more changes

@@
 
-\subsection{POD-Galerkin Projection}\label{class}
+\subsection{POD-Galerkin Projection}
+\label{sec:POD}
 
@@
 \subsection{Greedy POD}
-\label{sec:POD}
+\label{sec:greedy}
 
@@
 
-\section{ROM }
+\section{ROM}
 \subsection{ROM Implementation}
@@
 The POD-Galerkin projection procedures described in Sec.~\ref{sec:POD} were applied to the system in Eq.~\ref{eq:transient fom} to approximate the group flux and the core power of the LRA benchmark with increasing the spatial fidelity, i.e, spatial grids of $22\times 22$, $44\times44$ and $55 \times 55$ were used.\\
-POD basis set was generated for each group flux while one basis set was generated for both precursors groups, i.e, 
-$\mathbf{\Phi}_1(t) = \mathbf{U}_1\mathbf{a}_1(t)$, $\mathbf{\Phi}(t)_2 = \mathbf{U}_2\mathbf{a}_2(t)$ and $\mathbf{C}(t) = \mathbf{U}_c\mathbf{a}_c(t)$, where the $\mathbf{U}_1$, $\mathbf{U}_2$  and $\mathbf{U}_c$ are the POD bases of the fast group, thermal group and precursor concentration respectively, and $\mathbf{a}_1$, $\mathbf{a}_2$ and $\mathbf{a}_c$ are their respective temporal coefficients.
+POD basis set was generated for each group flux, 
+while one basis set was generated for both precursors groups, i.e, 
+$\mathbf{\Phi}_1(t) = \mathbf{U}_1\mathbf{a}_1(t)$, $\mathbf{\Phi}(t)_2 = \mathbf{U}_2\mathbf{a}_2(t)$ and $\mathbf{C}(t) = \mathbf{U}_c\mathbf{a}_c(t)$, where $\mathbf{U}_1$, $\mathbf{U}_2$  and $\mathbf{U}_c$ are the POD bases of the fast group, thermal group and precursor concentration respectively, and $\mathbf{a}_1$, $\mathbf{a}_2$ and $\mathbf{a}_c$ are their respective temporal coefficients.
 The resulting ROM can be represented as 
@@
 %The first 100 normalized singular values \footnote{The normalization is done be dividing each singular value by the sum of all singular values.} of the group flux are shown in Fig.~\ref{fig:lra singular values}.
-
-For POD rank selection, the ROM was solved with different flux ranks and the mean relative L$_2$ flux errors are computed and are shown in Fig.~\ref{fig:POD flux rank}.
+For POD rank selection, the ROM was solved with different flux ranks, and the mean relative L$_2$ flux errors are computed and are shown in Fig.~\ref{fig:POD flux rank}.
 \begin{figure}[h!]
@@
 \end{figure}
-A POD rank of 30 was selected fore each group flux since it results in a reasonably good error, i.e, less than 0.001\% and the same rank was used for approximating the precursors concentration.
+A POD rank of 30 was selected for each group flux since it results in a reasonably good error, i.e, less than 0.001\%, and the same rank was used for approximating the precursors concentration.
 Higher ranks can be selected if a better ROM accuracy is desired.
-Furthermore, a ROM was constructed for the coupled thermal feedback model and the temperature field was approximated by projecting it onto a lower dimensional POD space
+Furthermore, a ROM was constructed for the coupled thermal feedback model, and the temperature field was approximated by projecting it onto a lower dimensional POD space
 \begin{equation}
@@
 \end{equation}
-where $\mathbf{U}_{\text{temp}}\in\mathbb{R}^{n \times r_T} $ is the POD subspace of rank $r_T$ and $\mathbf{a}_T\in \mathbb{R}^{r_T}$ is a vector of the corresponding temporal coefficients. 
+where $\mathbf{U}_{\text{temp}}\in\mathbb{R}^{n \times r_T} $ is the POD subspace of rank $r_T$, and $\mathbf{a}_T\in \mathbb{R}^{r_T}$ is a vector of the corresponding temporal coefficients. 
 %To obtain the subspace, snapshots of the temperature were collected at different times for which the SVD was computed.
@@
 For selecting the temperature rank, i.e, $r_T$, the ROM was solved with different temperature ranks and the selected flux and precursors ranks.
-The mean core power relative error was computed in each case and is shown in Fig.~\ref{fig:temperature rank} based on which a POD of rank $10$ was selected for approximating the temperature since there was no improvement in the error for the higher ranks.
-
+The mean of the core power relative error was computed in each case and is shown in Fig.~\ref{fig:temperature rank}.
+Based on the shown error, a POD of rank $10$ was selected for approximating the temperature since there was no improvement in the error by using higher ranks.
+Note that the error cannot decrease below the error introduced by the group flux approximation.
 \begin{figure}[H]
@@
 	\includegraphics[width=1.0\linewidth]{../figures/temperature_rank_convergence.pdf}
-	\caption{temperature normalized singular value.}
+	\caption{Temperature normalized singular value.}
 	\label{fig:temperature rank}
 \end{figure}
-
-Now to solve for the quantities of interest, the flux temporal coefficients (i.e, $\mathbf{a_1}(t)$ and $\mathbf{a_2}(t)$) are computed at each time step by solving the reduced system in Eq.~\ref{eq:ROM} and then used to compute the temperature coefficients by employing a first-order, backward-difference scheme to Eq.~\ref{eq:reduced temp}.
+Now to solve for the quantities of interest, the flux temporal coefficients (i.e, $\mathbf{a_1}(t)$ and $\mathbf{a_2}(t)$) are computed at each time step by solving the reduced system in Eq.~\ref{eq:ROM} and then used to compute the temperature coefficients by solving Eq.~\ref{eq:reduced temp}.
+A first-order, backward-difference scheme was employed for solving the two systems.
 Similar to the full-order model, a fixed point iteration is used to treat the flux non-linearity.
@@
 \begin{equation}
-	\frac{\|\mathbf{a}^{i-1} - \mathbf{a}^{i}\|}{\|\mathbf{a}_i \|} \le 1\times 10^{-6}  \, , 
+	\frac{\|\mathbf{a}^{i-1} - \mathbf{a}^{i}\|}{\|\mathbf{a}_i \|} \le 1\times 10^{-6}  \, .
 \end{equation}
@@
 Shown in Fig.~\ref{fig:lra L singular values} are the singular values resulting from the SVD of the serialized operator snapshots. 
-A MDEIM of order $15$ was used since the singular-values decay by large magnitude around this value, however, higher orders can be chosen for higher accuracy.
+A MDEIM of order $15$ was used since the singular-values decay by large magnitude around this value; however, higher orders can be chosen for better accuracy.
 
@@
 \end{figure}
+
 %----------------------------------------------------------------------------------------------------%
 
-\subsection{ROM results}
+\subsection{ROM Results}
 
-Using the selected ranks in the previous subsection, MDEIM-ROMs were developed for full-order models of spatial grids $22\times 22$, $44\times44$ and $55 \times 55$.
+Using the selected POD ranks, MDEIM-ROMs were developed for full-order models of spatial grids $22\times 22$, $44\times44$, and $55 \times 55$.
 %For brevity, we show the first four POD modes with their temporal coefficients of only the $55 \times 55$ grid in Fig.~\ref{fig:lra flux modes}.
@@
 \end{figure}
-
-To understand the impact of employing the MDEIM on the error; the results are compared with these of a direct projection ROM, i.e., with performing direct operator projection at each time step.
+To understand the impact of employing the MDEIM on the error, the results are compared with these of a direct-projection ROM, i.e., with performing direct operator projection at each time step.
 The relative difference of the power between both models is shown in Fig.~\ref{fig:rom-deim power error}.
@@
 	\includegraphics[width=1.0\linewidth]{../figures/LRA_mdeim_relative_error.pdf}
-	\caption{Relative difference in the predicted power between the direct projection ROM and the MDEIM-ROM.}
+	\caption{Relative difference in the predicted power between the direct-projection ROM and the MDEIM-ROM.}
 	\label{fig:rom-deim power error}
@@
 Also, the spatial-averaged relative error in the approximated temperature was computed and is shown in Fig.~\ref{fig:deim tempearture error}.
-
 \begin{figure}[H]
@@
 
-Moreover, the computational times of the FOM and the ROMs are given in Table~\ref{table:cpu time}.
-
 \begin{table*}[h!]
@@
 \end{table*}
-
-Notably, the MDEIM-ROM is cheaper than the direct projection ROM with a speed-up that depends on the original model size.
+Moreover, the computational times of the FOM and the ROMs are given in Table~\ref{table:cpu time}.
+Notably, the MDEIM-ROM is cheaper than the direct-projection ROM with a speed-up that depends on the original model size.
 More importantly, the MDEIM-ROM cost is slightly dependent on the problem dimension while the other ROM time increases with the grid size because the operator projection is performed at each time step.
@@
 Shown in Table \ref{tab: 6 groups precursor data} are the parameters normal distributions data adopted from Refs.~\cite{keepin1957delayed, tuttle1975delayed}.
-A POD greedy sampling is used for which a set of 50 parameters points were generated to obtain a global POD space, where at each iteration, three POD basis vectors are added to the space.
+The POD greedy sampling presented in Sec.\ref{sec:greedy} is used for which a set of 50 parameters points were generated to obtain a global POD space, where at each iteration, three POD basis vectors are added to the space.
 A grid of $22\times 22$ is used throughout this study.
@@
 	\end{tabular}
-	\caption{6 groups delayed neutron precursor data.}
+	\caption{six groups delayed neutron precursor data.}
 	\label{tab: 6 groups precursor data}
@@
 and accordingly, resulted in a good approximation even for parameters not among the training sample.
+This means that using the POD-greedy sampling, POD basis sets can be pre-generated for different transient scenarios and used to run the ROM in multi-run applications that require running the same model but with changing the input parameters.
 
@@
 The LRA benchmark representing a simplified multi-physics problem was the application used to illustrate the method.
-Using the MDEIM introduced FOMs speeds up that range from 4 to 50 depending on the numerical fidelity, with a maximum power relative error in the order of $1\times 10^{-5}$\%.
-More importantly, the computational saving gained from using the MDEIM-ROM is more than that of the direct projection ROM.
+Using the MDEIM introduced FOMs speeds up that range from 6 to 40 depending on the numerical fidelity, with a maximum power relative error in the order of $1\times 10^{-5}$\%.
+More importantly, using the MDEIM-ROM proved to be more computationally efficient over the direct-projection ROM, and it becomes even more efficient with higher-dimensional problems.
 
@@
 Hence, the developed ROM was parameterized by means of POD-greedy sampling to generate a POD subspace global to a parameter domain of interest.
-The parameterized ROM in which the parameters of interest were the kinetic data, resulted in a maximum assembly power relative error across all testing parameter points that is in the order of $1\times 10^{-3}$\%.
+The parameterized ROM in which the parameters of interest were the kinetic data, resulted in a maximum assembly averaged power relative error across all testing parameter points that is in the order of $1\times 10^{-3}$\%.
 

### 2022-03-30 paper_/main.tex
added annals version

--- 2022-03-28 paper/interactnlmsample.tex
@@
-% interactnlmsample.tex
-% v1.05 - August 2017
+\newif\ifDRAFT
+\DRAFTtrue
+%\DRAFTfalse
 
-\documentclass[]{interact}
-
-\usepackage{epstopdf}% To incorporate .eps illustrations using PDFLaTeX, etc.
-\usepackage[caption=false]{subfig}% Support for small, `sub' figures and tables
-%\usepackage[nolists,tablesfirst]{endfloat}% To `separate' figures and tables from text if required
-%\usepackage[doublespacing]{setspace}% To produce a `double spaced' document if required
-%\setlength\parindent{24pt}% To increase paragraph indentation when line spacing is doubled
+\ifDRAFT
+\documentclass[review,number,sort&compress,12pt]{elsarticle}
+%% The lineno packages adds line numbers. Start line numbering with
+%% \begin{linenumbers}, end it with \end{linenumbers}. Or switch it on
+%% for the whole article with \linenumbers.
+%% \usepackage{lineno}
+\usepackage{lineno}
+\modulolinenumbers[5]
+\newcommand{\picwidth}{0.9\textwidth}
+\linenumbers
+\else 
+\documentclass[final,5p,11pt,twocolumn]{elsarticle}
+\newcommand{\picwidth}{0.48\textwidth}
+\fi
 
@@
 \usepackage{caption}
-\usepackage{threeparttable}
+\usepackage{subcaption}
 \usepackage{tikz}
@@
 \usepackage{booktabs,tabularx}
-%\usepackage{subcaption}
+\usepackage{threeparttable}
+
 \DeclareMathOperator{\argmaxH}{argmax} 
@@
 
-\usepackage[numbers,sort&compress]{natbib}% Citation support using natbib.sty
-\bibpunct[, ]{[}{]}{,}{n}{,}{,}% Citation support using natbib.sty
-\renewcommand\bibfont{\fontsize{10}{12}\selectfont}% Bibliography support using natbib.sty
-\makeatletter% @ becomes a letter
-\def\NAT@def@citea{\def\@citea{\NAT@separator}}% Suppress spaces between citations using natbib.sty
-\makeatother% @ becomes a symbol again
+%% `Elsevier LaTeX' style
+\bibliographystyle{elsarticle-num}
+%%%%%%%%%%%%%%%%%%%%%%%
+\journal{Annals of Nuclear Energy}
+\begin{document}
+\setcitestyle{square}
+%------------------------------------------------------------------------------
+% 
+%------------------------------------------------------------------------------
+\begin{frontmatter}
 
-\theoremstyle{plain}% Theorem-like structures provided by amsthm.sty
-\newtheorem{theorem}{Theorem}[section]
-\newtheorem{lemma}[theorem]{Lemma}
-\newtheorem{corollary}[theorem]{Corollary}
-\newtheorem{proposition}[theorem]{Proposition}
+%% Title, authors and addresses
 
-\theoremstyle{definition}
-\newtheorem{definition}[theorem]{Definition}
-\newtheorem{example}[theorem]{Example}
+%% use the tnoteref command within \title for footnotes;
+%% use the tnotetext command for the associated footnote;
+%% use the fnref command within \author or \address for footnotes;
+%% use the fntext command for the associated footnote;
+%% use the corref command within \author for corresponding author footnotes;
+%% use the cortext command for the associated footnote;
+%% use the ead command for the email address,
+%% and the form \ead[url] for the home page:
+%%
 
-\theoremstyle{remark}
-\newtheorem{remark}{Remark}
-\newtheorem{notation}{Notation}
-\bibliographystyle{plain}
-
-\begin{document}
-
-\articletype{Journal of Nuclear Science and Technology}% Specify the article type or omit as appropriate
-
-\title{Model-order reduction of non-linear time dependent neutronics via POD-Galerkin projection and DEIM}
-\author{
-\name{Rabab Elzohery\thanks{CONTACT A.~N. Author. Email: rababelzohery@ksu.edu} and Jeremy Roberts}
-\affil{Department of Mechanical and Nuclear Engineering,
+\title{Model-order reduction of non-linear time-dependent neutronics via POD-Galerkin projection and DEIM}
+%% \tnotetext[label1]{}
+\author[focal]{Rabab Elzohery\corref{cor}}
+\ead{Rababelzohery@ksu.edu}
+%\ead{http://www.rine.u-fukui.ac.jp}
+\author{Jeremy Roberts}
+%% \fntext[label2]{}
+\cortext[cor1]{Corresponding author}
+\address {The Alan Levin Department of Mechanical and Nuclear Engineering,
 	Kansas State University \\
 	3002 Rathbone Hall, Manhattan, KS 66506, US \\ rababelzohery@ksu.edu, jaroberts@ksu.edu}
-}
 
-\maketitle
+%% use optional labels to link authors explicitly to addresses:
+%% \author[label1,label2]{<author name>}
+%% \address[label1]{<address>}
+%% \address[label2]{<address>}
+
+%------------------------------------------------------------------------------
+% 
+%------------------------------------------------------------------------------
 \begin{abstract}
 Presented here is an application of model-order reduction to non-linear neutronic transients.
-% where reduced-order models (ROMs) are generally sought to provide a rapid, yet accurate, approximation of a particular simulation response.
-The effort described extends previous work\cite{elzohery2021modeling} aimed to develop and assess a ROM framework that can be used for different purposes, such as design optimization and propagating input parameter uncertainties like nuclear data.
-Here, the target applications here is non-linear.
+The effort described extends previous work\cite{elzohery2021exploring} aimed to develop and assess a ROM framework that can be used for different purposes, such as design optimization and propagating input parameter uncertainties like nuclear data.
+Here, the target applications is non-linear.
 The ROM was built with the use of the POD-Galerkin projection method and the matrix version of the Discrete Empirical Interpolation Method (MDEIM) for improved efficiency.
 The MDEIM is used to approximate the projection of the problem operator that otherwise must be computed at each non-linear iteration within each time step, which increases the ROM cost.
-By using the MDEIM, an offline-online ROM decomposition was obtained, which is favored from a computational perspective since the expensive projection operation can take place only once in the offline stage.
-The online stage, which involves solving a linear system  at each time step, depends only on the reduced dimension and is therefore cheap, making it possible to increase the solution time resolution, and accordingly accuracy, without introducing significant cost.
 By applying the method to the LRA benchmark, speed ups from 6 to 40 were achieved depending on the full-order model (FOM) spatial fidelity.
@@
 Moreover, the ROM was parameterized by POD-greedy sampling, and a case study was performed where the kinetic data, i.e, the precursor decay constants and delayed-neutron fraction were assumed to be the model parameters of interest.
-For the parameterized ROM, the maximum relative error in the assembly power was $1\times 10^{-3}$\%, which implies that the developed ROM can be reliably used to accelerate parametric and uncertainty quantification studies involving non-linear problems.
+For the parameterized ROM, the maximum relative error in the assembly power was $1\times 10^{-3}$\%, 
 The computational gain from the MDEIM-ROM was compared with that of a direct projection ROM and showed that employing the MDEIM is computationally advantageous, and the advantage grows with dimension of the problem.
@@
 
-\begin{keywords}
-Galerkin projection; POD; Non-linear reduced-order models; Neutronic Transient; Discrete Empirical Interpolation Method
-\end{keywords}
+%------------------------------------------------------------------------------
+% 
+%------------------------------------------------------------------------------
+\begin{keyword}
+	Reduced-Order Models; POD-Galerkin Projection; Discrete Empirical Interpolation Method; Non-linear Neutronic Transients
+\end{keyword}
 
-\section{Introduction}
+\end{frontmatter}
+
+%%
+%% Start line numbering here if you want
+%%
+%------------------------------------------------------------------------------
+% 
+%------------------------------------------------------------------------------
+%\linenumbers
+
+%------------------------------------------------------------------------------
+%% main text
+%------------------------------------------------------------------------------
+\section{Introduction\label{sect::intro}}
+
 Modeling and simulation of reactor physics is crucial to understanding nuclear reactors' behavior under different conditions and scenarios and hence ensure reliable designs and well-established safety limits.
@@
 Moreover, the neutron transport (or diffusion) equation is no longer a linear one due to the indirect dependence of the cross section on the neutron flux.
-Two approaches are used to solve such systems.
+several approaches are used to solve such systems.
 The most commonly used one is a serial coupling of two or more separate codes in such a way that the output of one at a given time step, such as the flux distribution, is used as an input to the other, e.g., the temperature (which can be used then to update the cross section and so on).
@@
 The method belongs to the projection-based family and can be described as a physics-driven method since it requires knowledge of the original governing equation as will be shown in Sec.\ref{sec:POD}.
-In a previous work \cite{elzohery2021modeling}, we applied the method to the time-dependent diffusion equation where there was no coupling with other models and hence the application was linear.
+In a previous work \cite{elzohery2021exploring}, we applied the method to the time-dependent diffusion equation where there was no coupling with other models and hence the application was linear.
 In this study, the developed ROM was extended to treat the non-linearity induced by multi-physics modeling.
@@
 The LRA benchmark was used as a demonstrative application where the diffusion equation is coupled with a simplified thermal feedback model.
-
-%The following discussion include a general overview of the methods and algorithms, then the specific application was described after which its results are presented.
 
@@
 Although the problem tackled here does not include a non-linear term, the DEIM idea is exploited to approximate time-dependent operators to avoid computing the projected operator $\mathbf{A}_r(t)$ at each time step, which requires number of FLOPS dependent on $n$.
-This is known as the matrix version of the DEIM, i.e, MDEIM and it was suggested in \cite{carlberg2012efficient, benner2015survey}.
+This is known as the matrix version of the DEIM, i.e, MDEIM and it was suggested in \cite{carlberg2012efficient},\cite{benner2015survey}.
 To illustrate, consider the operator $\mathbf{A}(\boldsymbol{t}) \in \mathbb{R}^{n\times n}$.
@@
 %-----------------------------------------------------------------------------------------------------%
-\section{Application}
-
-\subsection{The time-dependent diffusion equation}
+\section{The time-dependent diffusion equation}
 \label{sec:fom}
@@
 $C_i$ is the $i$th precursor concentration, $\beta_i$ is the fraction of delayed neutrons in group $i$, $\lambda_i$ is the $i$th group decay constant.
-%The system can be represented compactly in a matrix form as 
-%\begin{equation}
-%\frac{\partial{y}(r, t)}{\partial{t}} = \mathcal{A}{y}(r, t) \, ,
-%\end{equation}
-%where the stacked unknowns are
-%\begin{equation*}
-%	{y} = 
-%	\begin{pmatrix}
-%	\phi_1(r, t) \\
-%	\vdots \\
-%	\phi_G(r, t)  \\
-%	{C}_1(r, t) \\
-%	\vdots \\
-%	{C}_I(r, t) \\
-%	\end{pmatrix} \, .
-%\end{equation*}
-
-%\begin{equation*}
-%\mathcal{A} = \left(\begin{array}{@{}c|c@{}}
-%\begin{matrix}
-%v_1(\nabla \cdot D_1\nabla +\Sigma_{11}) & v_1\Sigma_{12} & \hdots  &v_1\Sigma_{1G} \\
-%v_2\Sigma_{21}        &    v_2(\nabla\cdot D_2\nabla +\Sigma_{22})            & \hdots  &v_2\Sigma_{2G} \\
-%\vdots   &   \vdots   &  \ddots  &\vdots  \\
-%v_G\Sigma_{G1}        &  v_G\Sigma_{G2} & \hdots &  v_G(\nabla \cdot D_G\nabla +\Sigma_{GG})     \\
-%\end{matrix}
-%&\begin{matrix}
-%v_1 f_{11} & \hdots &   v_1 f_{1I} \\
-%\vdots   & \ddots & \vdots \\
-%v_G f_{G1} & \hdots &   v_G f_{GI}
-%\end{matrix}
-%\\
-%\hline
-%\begin{matrix}
-%p_{11} &  &  & p_{12} & & & & \hdots  &   & p_{1G} \\
-%\vdots &  &  & & \ddots & & & \vdots&   & \vdots \\
-%p_{I1} &  &  & p_{I2} &  &   & & \hdots&  & p_{IG} 
-%\end{matrix}
-%&
-%\begin{matrix}
-%-\lambda_1 & \hdots & 0 \\
-%\vdots & \ddots  &  \vdots \\
-%0  &  \hdots  & -\lambda_I
-%\end{matrix}
-%\end{array}\right)
-%\end{equation*}
-%where 
-%\begin{subequations}
-%	\begin{equation*}
-%	\Sigma{gg^\prime} = (1 -\beta)\chi_g\nu\Sigma{fg^\prime} + \Sigma_{s_{gg^\prime}} \, ,
-%	\end{equation*}
-%	\begin{equation*}
-%	f_{ig^\prime} = \chi_g\lambda_i \, ,
-%	\end{equation*}
-%\end{subequations}
-%\vspace{-2 pt}
-%and
-%\vspace{-2 pt}
-%\begin{equation*}
-%p_{ig} = \beta_i \nu\Sigma_{fg} \, .
-%\end{equation*}
 Upon spatial discretization, the resulting system of ODEs can be compactly represented in a matrix form as  
@@
 %--------------------------------------------------------------------------------------%
+\section{Application}
 \subsection{Problem Description}
@@
 
-\section{ROM}
 \subsection{ROM Implementation}
 
-The POD-Galerkin projection procedures described in Sec.~\ref{sec:POD} were applied to the system in Eq.~\ref{eq:transient fom} to approximate the group flux and the core power of the LRA benchmark with increasing the spatial fidelity, i.e, spatial grids of $22\times 22$, $44\times44$ and $55 \times 55$ were used.\\
+The POD-Galerkin projection procedures described in Sec.~\ref{sec:POD} were applied to the system in Eq.~\ref{eq:transient fom} to approximate the group flux and the core power of the LRA benchmark with increasing the spatial fidelity, i.e, spatial grids of $22\times 22$, $44\times44$, and $55 \times 55$ were used.\\
 POD basis set was generated for each group flux, 
@@
 
-\subsection{ROM Results}
+\subsubsection{ROM Results}
 
@@
 \begin{figure}[H]
-	\includegraphics[width=1.0\linewidth]{../figures/LRA_power_deim_relative_error.pdf}
+	\includegraphics[width=1.0\linewidth]{../figures/_.pdf}
 	\caption{Relative error of the power predicted by MDEIM-ROM}
@@
 
+Moreover, the computational times of the FOM and the ROMs are given in Table~\ref{table:cpu time}.
+Notably, the MDEIM-ROM is cheaper than the direct-projection ROM with a speed-up that depends on the original model size.
+More importantly, the MDEIM-ROM cost is slightly dependent on the problem dimension while the other ROM time increases with the grid size because the operator projection is performed at each time step.
+The shown MEDIM-ROM time includes the offline cost which involves the operator $\mathbf{L}$ decomposition and the projection of the decomposed matrices.
+Also, both the ROMs times include the time to reconstruct the full-order solution.
 \begin{table*}[h!]
@@
 \end{table*}
-Moreover, the computational times of the FOM and the ROMs are given in Table~\ref{table:cpu time}.
-Notably, the MDEIM-ROM is cheaper than the direct-projection ROM with a speed-up that depends on the original model size.
-More importantly, the MDEIM-ROM cost is slightly dependent on the problem dimension while the other ROM time increases with the grid size because the operator projection is performed at each time step.
-The shown MEDIM-ROM time includes the offline cost which involves the operator $\mathbf{L}$ decomposition and the projection of the decomposed matrices.
-Also, both the ROMs times include the time to reconstruct of the full-order solution.
 
@@
 Although the original benchmark employs two precursor groups, it was more convenient in this study to use six groups to enlarge the parameter space.
-Shown in Table \ref{tab: 6 groups precursor data} are the parameters normal distributions data adopted from Refs.~\cite{keepin1957delayed, tuttle1975delayed}.
+Shown in Table \ref{tab: 6 groups precursor data} are the parameters normal distributions data adopted from Refs.~\cite{keepin1957delayed}, \cite{tuttle1975delayed}.
 The POD greedy sampling presented in Sec.\ref{sec:greedy} is used for which a set of 50 parameters points were generated to obtain a global POD space, where at each iteration, three POD basis vectors are added to the space.
@@
 
-The MDEIM-ROM is sought to predict the power at every $0.001$ s during the transient, however, a time step of $0.005$ s was used in the greedy procedures.
+The MDEIM-ROM is sought to predict the power at every $0.001$ s during the transient.
+However, a time step of $0.005$ s was used in the greedy procedures, since, as shown in \cite{elzohery2021exploring}, using a smaller time step in the generation of the greedy POD basis leads to faster error convergence.
 Shown in Fig.~\ref{fig:lra greedy error} is the flux error convergence with the greedy iterations.
@@
 Using the MDEIM introduced FOMs speeds up that range from 6 to 40 depending on the numerical fidelity, with a maximum power relative error in the order of $1\times 10^{-5}$\%.
-More importantly, using the MDEIM-ROM proved to be more computationally efficient over the direct-projection ROM, and it becomes even more efficient with higher-dimensional problems.
+More importantly, using the MDEIM-ROM proved to be more computationally efficient over the direct-projection ROM, and its efficiency increases with higher-dimensional problems.
 
@@
 
-\bibliography{interactnlmsample}
+\section*{References}
+
+\bibliography{mybibfile}
 

### 2022-06-07 paper_/main.tex
1st reviewer comment about steady state vs eigenvalue

@@
 A mesh-centered, finite-difference discretization was used in space, while a first-order, backward-difference temporal discretization was used with a fixed 0.001 s step size.  
-The initial condition for the transient was computed by solving the steady-state equation, for which $k_{\text{eff}}$ was found to be 0.9975.
+The initial condition for the transient was computed by solving the eigenvalue problem, for which $k_{\text{eff}}$ was found to be 0.9975.
 Note that at each time step the fast absorption cross section is a function of the solution itself.
@@
 
-\begin{figure}[H]
-	\includegraphics[width=1.0\linewidth]{../figures/_.pdf}
-	\caption{Relative error of the power predicted by MDEIM-ROM}
-	\label{fig:deim power error}
-\end{figure}
+%\begin{figure}[H]
+%	\includegraphics[width=1.0\linewidth]{../figures/_.pdf}
+%	\caption{Relative error of the power predicted by MDEIM-ROM}
+%	\label{fig:deim power error}
+%\end{figure}
 To understand the impact of employing the MDEIM on the error, the results are compared with these of a direct-projection ROM, i.e., with performing direct operator projection at each time step.

### 2022-07-10 paper_/main.tex
addressed reviewer comments

@@
 Presented here is an application of model-order reduction to non-linear neutronic transients.
-The effort described extends previous work\cite{elzohery2021exploring} aimed to develop and assess a ROM framework that can be used for different purposes, such as design optimization and propagating input parameter uncertainties like nuclear data.
+The effort described extends previous work\cite{elzohery2021exploring} aimed to develop and assess a Reduced-order model(ROM) framework that can be used for different purposes, such as design optimization and propagating input parameter uncertainties like nuclear data.
 Here, the target applications is non-linear.
 The ROM was built with the use of the POD-Galerkin projection method and the matrix version of the Discrete Empirical Interpolation Method (MDEIM) for improved efficiency.
-The MDEIM is used to approximate the projection of the problem operator that otherwise must be computed at each non-linear iteration within each time step, which increases the ROM cost.
+Where applications of the ROM to the diffusion equation have been introduced before \cite{}, this work focuses on treating the non-linearity induced by coupling with different physics.
+Previous work has used the DEIM to approximate non-linear fielsa such as the temperature \cite{german2019application}.
+Here, the MDEIM is used to approximate the projection of the problem operator that otherwise must be computed at each non-linear iteration within each time step, which increases the ROM cost.
 By applying the method to the LRA benchmark, speed ups from 6 to 40 were achieved depending on the full-order model (FOM) spatial fidelity.
@@
 In this study, the developed ROM was extended to treat the non-linearity induced by multi-physics modeling.
-To improve the computational efficiency of the developed ROM, a hyper-reduction technique known as the Discrete Empirical Interpolation Method (DEIM) was used in conjunction with the POD-Galerkin projection.
-The primary purpose of using the DEIM is to obtain an offline-online decomposition of the ROM to avoid repetitive projection of the problem operator at each iteration within the time step.
+At this point, we must emphysize that the method used here, i.e; POD Galerkin projection has been used in previous works to approximate the diffusion equation \cite{} for different problems and codes where it showed promising results.
+Moreover, the  Discrete Empirical Interpolation Method, DEIM, has been used in conjunction with the POD-Galerkin projection to approximate non-linear fields such as the temperature and the flow fields  ....
+\cite{}.
+Here, we are presenting another variant of the DEIM algorithm, known as the matrix version of DEIM, i,e; MDEIM, in order to improve the computational efficiency of the developed ROM.
+The primary purpose of using the MDEIM is to obtain an offline-online decomposition of the ROM to avoid repetitive projection of the problem operator at each iteration within the time step.
 The offline stage occurs only once and comprises the expensive step of the ROM.
@@
 &+ \chi_g(1-\beta)\sum_{g^\prime = 1}^{G}\nu\Sigma_{fg^\prime}\phi_{g^\prime}  
-+ \chi_g\sum_{i=1}^{P} \lambda_i C_i \, ,
++ \chi_g\sum_{i=1}^{I} \lambda_i C_i \, ,
 \end{split}
@@
 while one basis set was generated for both precursors groups, i.e, 
-$\mathbf{\Phi}_1(t) = \mathbf{U}_1\mathbf{a}_1(t)$, $\mathbf{\Phi}(t)_2 = \mathbf{U}_2\mathbf{a}_2(t)$ and $\mathbf{C}(t) = \mathbf{U}_c\mathbf{a}_c(t)$, where $\mathbf{U}_1$, $\mathbf{U}_2$  and $\mathbf{U}_c$ are the POD bases of the fast group, thermal group and precursor concentration respectively, and $\mathbf{a}_1$, $\mathbf{a}_2$ and $\mathbf{a}_c$ are their respective temporal coefficients.
+$\mathbf{\Phi}_1(t) = \mathbf{U}_1\mathbf{a}_1(t)$, $\mathbf{\Phi}_2(t) = \mathbf{U}_2\mathbf{a}_2(t)$ and $\mathbf{C}(t) = \mathbf{U}_c\mathbf{a}_c(t)$, where $\mathbf{U}_1$, $\mathbf{U}_2$  and $\mathbf{U}_c$ are the POD bases of the fast group, thermal group and precursor concentration respectively, and $\mathbf{a}_1$, $\mathbf{a}_2$ and $\mathbf{a}_c$ are their respective temporal coefficients.
 The resulting ROM can be represented as 

### 2022-07-10 response_to_reviewers.tex
started responding to reviewers

% Title:    A LaTeX Template For Responses To a Referees' Reports
% Author:   Petr Zemek <s3rvac@gmail.com>
% Homepage: https://blog.petrzemek.net/2016/07/17/latex-template-for-responses-to-referees-reports/
% License:  CC BY 4.0 (https://creativecommons.org/licenses/by/4.0/)
\documentclass[10pt]{article}

% Allow Unicode input (alternatively, you can use XeLaTeX or LuaLaTeX)
\usepackage[utf8]{inputenc}
\usepackage{xcolor}

\usepackage{microtype,xparse,tcolorbox}
\newenvironment{reviewer-comment }{}{}
\tcbuselibrary{skins}
\tcolorboxenvironment{reviewer-comment }{empty,
  left = 1em, top = 1ex, bottom = 1ex,
  borderline west = {2pt} {0pt} {black!20},
}
\ExplSyntaxOn
\NewDocumentEnvironment {response} { +m O{black!20} } {
  \IfValueT {#1} {
    \begin{reviewer-comment~}
      \setlength\parindent{2em}
      \noindent
      \ttfamily #1
    \end{reviewer-comment~}
  }
  \par\noindent\ignorespaces
} { \bigskip\par }

\NewDocumentCommand \Reviewer { m } {
  \section*{Comments~by~Reviewer~#1}
}
\ExplSyntaxOff
\AtBeginDocument{\maketitle\thispagestyle{empty}\noindent}

\title{Statement on the Revision of ANUCENE-D-22-00268 \\
  Based on the Referees' Report}
\author{Rabab Elzohery \and Jeremy A. Roberts}
\date{\today}

\begin{document}
This statement concerns our revision of the ANUCENE-D-21-00065, entitled ``Modeling Neutronic Transients with Galerkin Projection onto a Greedy-Sampled, POD Subspace'', based on the referees' report.

\Reviewer{\#1}

\begin{response}{
   The novelty of the paper is then restricted to the implementation of the model in a specific code, and to its application to a specific problem. I believe this may still make it worth publishing, but the authors are requested to rewrite abstract, introduction and conclusions in order to:
   - acknowledge the work of other authors on the subject
   - adapt their claims to the fact that the methodology has already been proposed and tested.
   They should also change the title, as it gives the idea that this is a first-of-a-kind paper using a POD-Galerkin and DEIM for neutronics, while this is not the case. The title should focus on elements of actual novelty (implementation in a specific code and application to a benchmark).
}
  These are all great and valid questions. Here are the answers and some clarifications:
  \begin{itemize}
  \item{The greedy sampling can treat high-dimensional input spaces,  but we expect that this will lead to an increase in the number of selected samples that contribute to the POD-greedy space.}

 \item{The unscented transform and the POD-greedy sampling are fundamentally different in scope.
  In the context of uncertainty quantification, the unscented transform can be used to select parameter samples that could represent the entire parameter space.
  As presented in the suggested paper,  the method seems to be promising and efficient when input  parameters are correlated and their covariance matrix is available or computable.
  On the other hand, the greedy-POD sampling is used to construct a parametric ROM by building  a global POD space that can capture variation in the parameters domain. These  parameters do not have to be correlated or follow a specific distribution. 
  In this work, our main goal  was to develop a parametric ROM based on the Galerkin projection method. The same framework implemented here can be used to perform design optimization or sensitivity study where  there is only one parameter that is perturbed,  e.g, control rod position and  initial condition.

  We agree that this was not clear in the paper, accordingly we have emphasized this in the introduction section.}

  \item{Regarding the training data size, note that out of the 50 samples, only 20 were chosen since the algorithm was terminated based on the set criteria.
  It is true that the ROM was evaluated 50 times to obtain the reference solution and to compute the error based on which a new sample is selected.  
  However, as mentioned in our concluding remarks, work is ongoing to develop a posterior error indicator. This posterior error (estimate) won’t require running the FOM for the entire parameter training set.

  Using this error indicator, the worst sample will be selected and the FOM will be evaluated for this sample only. 
  Also, we expect that this might lead to faster convergence of the greedy space since it will be more convienent to generate larger parameter sample size.
  For more details, you may look at Remark-2.47 in Ref.[12].}
  \item{We agree that 100 samples are not enough but our goal here is to illustrate the method not to quantify the real uncertainty. So, we think that as long as the same number of samples is used in the two models, the comparison is fair.
  \item To conclude, the goal here is to develop an efficient parametric ROM not an efficient UQ method.}
  \end{itemize}

\end{response}

\begin{response}{ would not define JFNK as a modern method. I have found publications from the eighties on it, and I guess it may be older than that. I also would avoid passing the message that block-matrix coupling is faster than operator-splitting. Very often, this is not the case, as operator splitting allows a very well targeted preconditioning, and selective solution of non-converged fields
   }

\end{response}

\begin{response}{
 In the sentence "The initial condition for the transient was computed by solving the steady-state equation", I believe it would be more accurate to speak about "eigenvalue problem" instead of " steady-state equation".}

We agree with the reviewer and this has beem modified.

\end{response}

\begin{response}{The authors mention "Note that at each time step the fast absorption cross section is a function of the solution itself". Is this an assumption, a statement, or a feature of the benchmark? Is this the only XS that is parametrized?.}

This a feature of the benchmark. The fast corss section is defined as a function of the temerature at each time step. And the temperature changes as a function of the neutron flux, i.e, the solution.
\end{response}

\begin{response}
  {What do you mean by "This reference solution is not necessarily numerically converged in either space or time". If it is not converged, it may not be a meaningful solution and should probably not be used in a numerical benchmark, since it may not be representative of the problem at hand. Please clarify.}
  ----------------------------------------

\end{response}

\begin{response}
	{ I am not sure I understand how the snapshots are taken. Are they the time dependent fluxes taken from the FOM solution? If that is the case, results in fig. 6 are essentially a sanity check, since reaching that level of accuracy would always require precomputing the transient with the FOM model. Please clarify}

	Yes, the snapshots are FOM time-dependent flux. In Fig.6 shows the error between two ROMs.
	One with using a direct-projection of the operator, and the other with approximating the operator with MDEIM (i.e, no direct projection). The former model is considered as the reference in this case.

------------------------------------
\end{response}

\begin{response}
 {How are the parameters points sampled in section 4.2.2}

 They are sampled from the normal distribution shown in table~4. No correlation was assumed between the six parameters.

\end{response}

\begin{response}
{I find it very difficult to interpret the results of section 4.2.2. The authors compare the predictions of ROM and FOM, but what is the impact of the parameters on the FOM itself? Without this information, it is impossible to assess the goodness of the ROM approximation. The error made by the ROM model should be small with respect to the differences expected in the FOM when changing the selected parameters.}

We mentioned that the time-to-peak differs from sample to another in the FOM solution, 
because the value of beta differs between samples.
On the other hand, the time-to-peak of the ROM solution is in exact agreement with the FOM solution,
We view each parameter point as a different problem with a different solution, and we are comparing this solution to the one obtained from the ROM.
------------------------------------
\end{response}

\Reviewer{\#2}
\begin{response}
	{
		Equations (14)-(15), (18)-(20):
		In my understanding, the non-linear operator L is calculated with the MDEIM, and the authors also applied the POD for Equation (14) to treat the temperature distribution with fewer DOFs.
		However, I could not clearly understand how the authors calculate Equation (15) before applying MDEIM from the expansion coefficients $(a_T)$ for the temperature distribution. A few more descriptions of the procedure will help a better understanding for readers.
		( I mean the relationship between the non-linear operator L and f(y(t)) in section 2.2 is not clear. The description of Equation (12) also makes it difficult to clearly understand because Equation (12) can be seen as a linear equation but the actual operator L is a non-linear function due to the feedback effect.)
	}

f(y(t)) was mentioned in section 2 to motivate the use of DEIM in general. In the problem tackled here, there is no such f(y(t)). MDEIM was used to approximate the problem non-linear operator.
The At each time step, MDEIM is used and the eq solved for the flux coefficients. Theses flux coefficient are then used in eq. 20 to update the temperature coefficients $a-T$, which is the ROM approximation of eq. 14.
Using this computed temperature, the fast cross-section is updated using eq. 15.
But we agree with reviewer that eq.12, as presented, is linear

\end{response}

-------------------------------

\begin{response}
{ pages 15 and Table 1:
	The Doppler feedback coefficient, $3.034x10^-3 K^-0.5$, seems not identical to the benchmark specification in the reference [15]. In the original benchmark specification, it would be $2.034x10^-3 K^-0.5$.
	In addition, the axial bucking $(B^2)$ is specified in the original LRA 2D benchmark problem in my understanding. If the authors are using axial buckling, it should be described in Table 1. "nu" value is also missing in Table 1.
	(You can also find the LRA benchmark results calculated with the conventional codes in the following reference:
	T.M. Sutton, and B. N. Aviles, "Diffusion Theory Methods for Spatial Kinetics Calculations", Prog. Nucl. Energy, 30(2), 119-182, 1996.
	Since the initial keff = 0.9975 is a little higher than their results, I wonder whether the axial buckling is taken into account or not.)
	Off course, the above inconsistency in the FOM calculation condition does not affect the validity of the methodology presented in this work.}

-------------------------------------
\end{response}

\begin{response}
{
 page 1, line 11 : "ROM" --> reduced order model (ROM)
 page 12, Equation (11) : P --> I (Authors are using "I" for the number of precursor groups in page 13.)}
% page 15 : kappa = $3.204 x 10^-11 W/fission --> kappa = 3.204 x 10^-11 J/fission$
% page 18, line 2 : $fai(t)2 --> fai_2(t)}$

\end{response}
These have been corrected. Thanks for the catch.

\end{document}

### 2022-07-12 response_to_reviewers.tex
More on the reviewers response

@@
 
+The doppler coefficient .....
+The axial buckling was accounted for as given on the benchmark documentation. We have commented on that in the paper and added it value in table 1 along with the value of $\nu$. Thanks for the catch.
+Regarding to the value of initial keff, it is sensitive to the spatial discretization, the numerical solver and the convergence criteria, and this might be the cause of this little bias that you observed.
+We agree with the reviewer that any inconsistency resulting from a change in the problem data from that in the original benchmark does not affect the presented results, as long the problem parameters are consistent in both the FOM and the ROM.
+
 -------------------------------------

### 2022-07-16 response_to_reviewers.tex
more on the reviewers comments

@@
 \begin{document}
-This statement concerns our revision of the ANUCENE-D-21-00065, entitled ``Modeling Neutronic Transients with Galerkin Projection onto a Greedy-Sampled, POD Subspace'', based on the referees' report.
+This statement concerns our revision of the ANUCENE-D-22-00268, entitled ``Modeling Neutronic Transients with Galerkin Projection onto a Greedy-Sampled, POD Subspace'', based on the referees' report.
 
@@
 \begin{response}{
+   The paper is clear and relatively well written but has limited novelty.
+Use of ROM for neutron diffusion problems has already been widely investigated at the Politecnico di Milano (see the work of Stefano Lorenzi and Alberto Sartori), with co-authoring from world-leading experts from SISSA (Professor Rozza), as well as at TAMU (see the work of Peter German and Jean Ragusa).
+In particular, use of ROM with DEIM for non-linear neutronics is described in:
+
+  "Application of multiphysics model order reduction to doppler/neutronic feedback"
+  P German, JC Ragusa, C Fiorina
+  EPJ Nuclear Sciences & Technologies 5 (ARTICLE), 17
+
+  or
+
+  Péter German, Mauricio Tano, Carlo Fiorina, Jean C. Ragusa,
+  GeN-ROM—An OpenFOAM®-based multiphysics reduced-order modeling framework for the analysis of Molten Salt Reactors,
+  Progress in Nuclear Energy,
+  Volume 146,
+  2022,
+  104148,
+  ISSN 0149-1970,
+  https://doi.org/10.1016/j.pnucene.2022.104148.
+
   The novelty of the paper is then restricted to the implementation of the model in a specific code, and to its application to a specific problem.
@@
 The title should focus on elements of actual novelty (implementation in a specific code and application to a benchmark).
-}
-  These are all great and valid questions. Here are the answers and some clarifications:
-  \begin{itemize}
-  \item{The greedy sampling can treat high-dimensional input spaces,  but we expect that this will lead to an increase in the number of selected samples that contribute to the POD-greedy space.}
 
- \item{The unscented transform and the POD-greedy sampling are fundamentally different in scope.
-  In the context of uncertainty quantification, the unscented transform can be used to select parameter samples that could represent the entire parameter space.
-  As presented in the suggested paper,  the method seems to be promising and efficient when input  parameters are correlated and their covariance matrix is available or computable.
-  On the other hand, the greedy-POD sampling is used to construct a parametric ROM by building  a global POD space that can capture variation in the parameters domain.
-These  parameters do not have to be correlated or follow a specific distribution.
-  In this work, our main goal  was to develop a parametric ROM based on the Galerkin projection method.
-The same framework implemented here can be used to perform design optimization or sensitivity study where  there is only one parameter that is perturbed,  e.g, control rod position and  initial condition.
-
-  We agree that this was not clear in the paper, accordingly we have emphasized this in the introduction section.}
-
-  \item{Regarding the training data size, note that out of the 50 samples, only 20 were chosen since the algorithm was terminated based on the set criteria.
-  It is true that the ROM was evaluated 50 times to obtain the reference solution and to compute the error based on which a new sample is selected.  
-  However, as mentioned in our concluding remarks, work is ongoing to develop a posterior error indicator.
-This posterior error (estimate) won’t require running the FOM for the entire parameter training set.
-
-  Using this error indicator, the worst sample will be selected and the FOM will be evaluated for this sample only. 
-  Also, we expect that this might lead to faster convergence of the greedy space since it will be more convienent to generate larger parameter sample size.
-  For more details, you may look at Remark-2.47 in Ref.[12].}
-  \item{We agree that 100 samples are not enough but our goal here is to illustrate the method not to quantify the real uncertainty.
-So, we think that as long as the same number of samples is used in the two models, the comparison is fair.
-  \item To conclude, the goal here is to develop an efficient parametric ROM not an efficient UQ method.}
-  \end{itemize}
-
+We agree with reviewer that the DEIM was used before and we have acknowledged their work in the introduction and cited their paper.
+However, it is important to clarify that in this work, we used a different variant of the DEIM algorithm, which it is matrix version.
+Moreover, where DEIM we used previously to approximate non-linear function such as the temperature or the flow filed, we have used MDEIM to approximate the problem operator in case an affine decomposition is not readily obtainable.
+And to the author knowledge the Matrix version of DEIM was not used before in the nuclear community.
+As the reviewer suggested, we have modified the title to reflect this goal
 \end{response}
 
-\begin{response}{ would not define JFNK as a modern method.
+\begin{response}{I would not define JFNK as a modern method.
 I have found publications from the eighties on it, and I guess it may be older than that.
@@
 
-We agree with the reviewer and this has beem modified.
+We agree with the reviewer. The initial condition is computed by solving an eigenvalue problem, and this has been modified.
 
@@
 
-This a feature of the benchmark. The fast corss section is defined as a function of the temerature at each time step. And the temperature changes as a function of the neutron flux, i.e, the solution.
+This a feature of the benchmark. The fast cross section is defined as a function of the temperature at each time step, and the temperature changes as a function of the neutron flux, i.e, the solution.
 \end{response}
@@
 
-	Yes, the snapshots are FOM time-dependent flux. In Fig.6 shows the error between two ROMs.
-	One with using a direct-projection of the operator, and the other with approximating the operator with MDEIM (i.e, no direct projection). The former model is considered as the reference in this case.
+	Yes, the snapshots are FOM time-dependent flux. We have added a sentence to clarify this in the paper.
 
@@
 
-We mentioned that the time-to-peak differs from sample to another in the FOM solution, 
-because the value of beta differs between samples.
-On the other hand, the time-to-peak of the ROM solution is in exact agreement with the FOM solution,
-We view each parameter point as a different problem with a different solution, and we are comparing this solution to the one obtained from the ROM.
+We mentioned in the paper that the time-to-peak differs from FOM sample to another, 
+because the value of beta is different between samples. 
+On the other hand, the time-to-peak of the ROM solution is exactly the same as in the FOM solution.
+That is why it was not convenient to compute point-by-point difference between the FOM samples, 
+but the computed the relative standard deviation of the FOM samples is 0.6 \%, which indicates a much bigger error compared to the ROM error.
+we elaborated on this more in the paper.
 ------------------------------------
@@
 
-f(y(t)) was mentioned in section 2 to motivate the use of DEIM in general. In the problem tackled here, there is no such f(y(t)). MDEIM was used to approximate the problem non-linear operator.
-The At each time step, MDEIM is used and the eq solved for the flux coefficients.
-Theses flux coefficient are then used in eq.
-20 to update the temperature coefficients $a-T$, which is the ROM approximation of eq.
-14.
-Using this computed temperature, the fast cross-section is updated using eq. 15.
-But we agree with reviewer that eq.12, as presented, is linear
+It is more accurate to say that the operator L is approximated (not calculated) by MDEIM.
+For clarity, at each time step, MDEIM is first applied to approximate the operator, and Eq~18 is solved for the flux coefficients.
+Theses flux coefficient are then used in Eq.~20 to update the temperature coefficients $a-T$.
+Using this computed temperature, the fast cross-section is updated using Eq.~15.
+But we agree with reviewer that Eq.~12, as presented, is linear, since was a general represention of the diffusion equation and this has been clarified in the paper.
+In particular, we clarified that in the problem studied here, coupling with TH model lead to A be a function of the solution, i.e, A(y(t)).
+Also, it is mentioned that vectorized form of the operator corresponds to the function f(y(t)) mentioned in section 2.2.
 

### 2022-07-16 paper_/main.tex
more on the reviewers comments

@@
 %% and the form \ead[url] for the home page:
-%%
-
+%%POD-Galerkin projection
+%\title{Application of the Matrix version of DEIM and POD-Galerkin projection 
 \title{Model-order reduction of non-linear time-dependent neutronics via POD-Galerkin projection and DEIM}
@@
 It employs two energy groups and two delayed precursor groups and represents a 2-D quarter-core, BWR model subject to a control-rod ejection with adiabatic heating \cite{anl}.
+The two groups data are given in Table~\ref{tab:two group data}, where $\text{B}^2$ is the axial buckling for both energy groups as given in the benchmark specification.
 A schematic layout of the problem is shown in Fig.~\ref{fig:lra core}, where region numbers indicate different materials and region R is the ejected rod.
@@
 \end{equation}
-where $\kappa = 3.204\times 10^{-11}~ \text{W/fission}$.
+where $\kappa = 3.204\times 10^{-11}~ \text{J/fission}$.
 The model was implemented in the deterministic transport code Detran~\cite{roberts2014advanced}.
@@
 The initial condition for the transient was computed by solving the eigenvalue problem, for which $k_{\text{eff}}$ was found to be 0.9975.
-Note that at each time step the fast absorption cross section is a function of the solution itself.
+Note that at each time step the fast absorption cross section is a function of the solution itself, in which case Eq.~\ref{eq:transient fom} becomes a non-linear one, since the operator $\mathbf{A}$ changes with the solution at each time step, i.e, $\mathbf{A}(\mathbf{y}(t))$.
 The convergence criterion used to reduce the $\text{L}_2$ norm  of the relative flux error between two consecutive iterations to less than $1\times 10^{-6}$, or
@@
 \end{figure}
-
-%\begin{figure}[H]
-%	\centering
-%	\begin{subfigure}[b]{0.7\textwidth}
-%		\includegraphics[width=1.0\linewidth]{../figures/ss_fom_fast_flux_image.pdf}
-%		\caption{Steady state fast flux.}
-%		\label{fig:ss fast flux}
-%	\end{subfigure}
-%	\begin{subfigure}[b]{0.7\textwidth}
-%		\includegraphics[width=1.0\linewidth]{../figures/ss_fom_thermal_flux_image.pdf}
-%		\caption{Steady state thermal flux.}
-%		\label{fig:ss thermal flux}
-%	\end{subfigure}
-%	\caption{Steady state group flux $(\text{neutrons} ~\text{cm}^2/s)$}
-%	\label{fig:lra ss flux}
-%\end{figure}
 
@@
 		\end{tabular}
+
 		\begin{tablenotes}
-			\item $v_1 = 3\times10^{7} ~\text{cm/s} $,  $v_2 = ~3\times10^{5} \text{cm/s}.$.
+			\item $v_1 = 3\times10^{7} ~\text{cm/s} $,  $v_2 = ~3\times10^{5} \text{cm/s}$, $\nu=2.34$, $B^2=1\times{10}^{-4}$.
 		\end{tablenotes}
@@
 	\caption{Two group constants of the LRA benchmark.}
+	\label{tab:two group data}
 \end{table}
@@
 The POD-Galerkin projection procedures described in Sec.~\ref{sec:POD} were applied to the system in Eq.~\ref{eq:transient fom} to approximate the group flux and the core power of the LRA benchmark with increasing the spatial fidelity, i.e, spatial grids of $22\times 22$, $44\times44$, and $55 \times 55$ were used.\\
-POD basis set was generated for each group flux, 
+POD basis set was generated for each group flux, using snapshot of the FOM time dependent solution, 
 while one basis set was generated for both precursors groups, i.e, 
@@
 
-%Note that the fast absorption cross section needs to be updated at each time step using Eq.~\ref{eq:doppler} in which the core temperature distribution is required.
-%In order to avoid reconstructing the full order temperature, 
-%the DEIM was used to approximate the absorption cross section.
-%For this purpose, snapshots of which were collected in order to generate a POD subspace that is used to approximate its space and to find a set of interpolation indices as illustrated in Algorithm~\ref{alg:DEIM}.
-%DEIM of order $10$ was used and hence, the cross section was reconstructed at each time step at only 10 points in the spatial space.
 Since the reactivity insertion was simulated by changing the absorption cross section, the operator $\mathbf{A}$ in Eq.~\ref{eq:transient fom} exhibits time dependence.
@@
 Thus, to avoid performing the expensive projection at each time step, 
-The MDEIM was used to decompose the matrix $\mathbf{L}$.
+The MDEIM was used to decompose the matrix $\mathbf{L}$, and Eq.~\eqref{eq:ROM} was solved for the flux and precursors coefficient.
+Using the flux coefficients, the temperature coefficients were computed with Eq.~\ref{eq:reduced temp} from which the cross section in Eq.~\ref{eq:doppler} was updated.
 Shown in Fig.~\ref{fig:lra L singular values} are the singular values resulting from the SVD of the serialized operator snapshots.
@@
 
-%\begin{figure}[H]
-%	\includegraphics[width=1.0\linewidth]{../figures/_.pdf}
-%	\caption{Relative error of the power predicted by MDEIM-ROM}
-%	\label{fig:deim power error}
-%\end{figure}
+\begin{figure}[H]
+	\includegraphics[width=1.0\linewidth]{../figures/LRA_power_deim_relative_error.pdf}
+	\caption{Relative error of the power predicted by MDEIM-ROM}
+	\label{fig:deim power error}
+\end{figure}
 To understand the impact of employing the MDEIM on the error, the results are compared with these of a direct-projection ROM, i.e., with performing direct operator projection at each time step.

### 2022-07-19 response_to_reviewers.tex
add more reviews

@@
   P German, JC Ragusa, C Fiorina
-  EPJ Nuclear Sciences & Technologies 5 (ARTICLE), 17
+  EPJ Nuclear Sciences \& Technologies 5 (ARTICLE), 17
 
@@
   They should also change the title, as it gives the idea that this is a first-of-a-kind paper using a POD-Galerkin and DEIM for neutronics, while this is not the case.
-The title should focus on elements of actual novelty (implementation in a specific code and application to a benchmark).
+The title should focus on elements of actual novelty (implementation in a specific code and application to a benchmark).}
 
-We agree with reviewer that the DEIM was used before and we have acknowledged their work in the introduction and cited their paper.
-However, it is important to clarify that in this work, we used a different variant of the DEIM algorithm, which it is matrix version.
-Moreover, where DEIM we used previously to approximate non-linear function such as the temperature or the flow filed, we have used MDEIM to approximate the problem operator in case an affine decomposition is not readily obtainable.
-And to the author knowledge the Matrix version of DEIM was not used before in the nuclear community.
+We agree with reviewer that ROM with DEIM was successfully used before and we have acknowledged this in the introduction section and cited these papers.
+However, it is important to clarify that in our work, we used a different variant of the DEIM algorithm, which is its matrix version.
+Moreover, where DEIM was used previously to approximate non-linear functions such as the temperature and the velocity filed, we have used MDEIM to approximate the problem operator in case an affine decomposition is not readily obtainable.
+To the author knowledge the matrix version of DEIM was not used before in the nuclear community.
 As the reviewer suggested, we have modified the title to reflect this goal
@@
 }
+
+we agree with author. Our intention was that the algorithm is implemented in modern codes, but we have removed the word `modern' to avoid confusion.
 
@@
 
-This a feature of the benchmark. The fast cross section is defined as a function of the temperature at each time step, and the temperature changes as a function of the neutron flux, i.e, the solution.
+This a feature of the benchmark.
+The fast cross section is defined as a function of the temperature at each time step, and the temperature changes as a function of the neutron flux, i.e, the solution.
+And yes, this the only cross section that is parametrized
 \end{response}
@@
 
-We mentioned in the paper that the time-to-peak differs from FOM sample to another, 
-because the value of beta is different between samples. 
+We mentioned in the paper that the time-to-peak differs from FOM sample to another.
 On the other hand, the time-to-peak of the ROM solution is exactly the same as in the FOM solution.
-That is why it was not convenient to compute point-by-point difference between the FOM samples, 
-but the computed the relative standard deviation of the FOM samples is 0.6 \%, which indicates a much bigger error compared to the ROM error.
-we elaborated on this more in the paper.
+That is why it was not convenient to compute point-by-point difference between the FOM solutions. 
+The difference between the FOM peak power at different parameters points varies between 0.1 to 1\%,  which indicates a significantly larger difference between the FOM solution peak powers compared to the ROM error.
+we have clarified this in the paper.
 ------------------------------------
@@
 Using this computed temperature, the fast cross-section is updated using Eq.~15.
-But we agree with reviewer that Eq.~12, as presented, is linear, since was a general represention of the diffusion equation and this has been clarified in the paper.
-In particular, we clarified that in the problem studied here, coupling with TH model lead to A be a function of the solution, i.e, A(y(t)).
-Also, it is mentioned that vectorized form of the operator corresponds to the function f(y(t)) mentioned in section 2.2.
+But we agree with reviewer that Eq.~12, as presented, is linear, since was a general representation of the diffusion equation, and this has been clarified in the paper.
+In particular, we clarified that in the problem studied here, coupling with TH model leads to $\textbf{A}$ be a function of the solution, i.e, $\textbf{A}(\textbf{y}(t))$.
+Also, it is mentioned that vectorized form of the operator corresponds to the function f(y(t)) given in section 2.2.
 
@@
 The doppler coefficient .....
-The axial buckling was accounted for as given on the benchmark documentation. We have commented on that in the paper and added it value in table 1 along with the value of $\nu$. Thanks for the catch.
+The axial buckling was accounted for as given on the benchmark documentation. We have commented on that in the paper and added its value in table~1 along with the value of $\nu$. Thanks for the catch.
 Regarding to the value of initial keff, it is sensitive to the spatial discretization, the numerical solver and the convergence criteria, and this might be the cause of this little bias that you observed.
@@
 \end{response}
-These have been corrected. Thanks for the catch.
+These have been corrected. Thanks catching these errors.
 

### 2022-07-19 response_to_reviewers.tex
fixed title

@@
 \begin{document}
-This statement concerns our revision of the ANUCENE-D-22-00268, entitled ``Modeling Neutronic Transients with Galerkin Projection onto a Greedy-Sampled, POD Subspace'', based on the referees' report.
+This statement concerns our revision of the ANUCENE-D-22-00268, entitled ``Model-order reduction of non-linear time-dependent neutronics via POD-Galerkin projection and DEIM'', based on the referees' report.
 
@@
 
-The doppler coefficient .....
+The doppler coefficient ????????????
 The axial buckling was accounted for as given on the benchmark documentation. We have commented on that in the paper and added its value in table~1 along with the value of $\nu$. Thanks for the catch.

### 2022-07-19 paper/main.tex

--- 2022-07-16 paper_/main.tex
@@
 %%POD-Galerkin projection
-%\title{Application of the Matrix version of DEIM and POD-Galerkin projection 
-\title{Model-order reduction of non-linear time-dependent neutronics via POD-Galerkin projection and DEIM}
+\title{Application of Model-order reduction of non-linear time-dependent neutronics via POD-Galerkin projection and matrix discrete empirical interpolation}
+%\title{Model-order reduction of non-linear time-dependent neutronics via POD-Galerkin projection and DEIM}
 %% \tnotetext[label1]{}
@@
 Presented here is an application of model-order reduction to non-linear neutronic transients.
-The effort described extends previous work\cite{elzohery2021exploring} aimed to develop and assess a Reduced-order model(ROM) framework that can be used for different purposes, such as design optimization and propagating input parameter uncertainties like nuclear data.
+The effort described extends previous work\cite{elzohery2021exploring} aimed to develop and assess a Reduced-order model (ROM) framework that can be used for different purposes, such as design optimization and propagating input parameter uncertainties like nuclear data.
 Here, the target applications is non-linear.
 The ROM was built with the use of the POD-Galerkin projection method and the matrix version of the Discrete Empirical Interpolation Method (MDEIM) for improved efficiency.
-Where applications of the ROM to the diffusion equation have been introduced before \cite{}, this work focuses on treating the non-linearity induced by coupling with different physics.
-Previous work has used the DEIM to approximate non-linear fielsa such as the temperature \cite{german2019application}.
+Where applications of the ROM to the diffusion equation have been introduced before \cite{sartori2014comparison, sartori2014reduced, tsujita2021fast}, this work focuses on treating the non-linearity induced by coupling with different physics.
+Previous work has used DEIM to approximate non-linear functions resulting from multiphysics coupling such as the temperature and the velocity field \cite{german2019application, german2022gen}.
 Here, the MDEIM is used to approximate the projection of the problem operator that otherwise must be computed at each non-linear iteration within each time step, which increases the ROM cost.
@@
 Alternatively, tight coupling in time between the physics can be maintained by using an implicit scheme that solves a non-linear iteration in each time step, also increasing the computational time.
-A modern algorithm such as Jacobian free Newton-Krylov (JFNK) \cite{gaston2009parallel} can be used to perform this implicit coupling.
+An algorithm such as Jacobian free Newton-Krylov (JFNK) \cite{gaston2009parallel} can be used to perform this implicit coupling.
 Another popular approach is to use fixed-point iteration, with an implicit time scheme to iterate between difference physics within a time step until convergence is satisfied, which is computationally taxing.
@@
 In a previous work \cite{elzohery2021exploring}, we applied the method to the time-dependent diffusion equation where there was no coupling with other models and hence the application was linear.
-In this study, the developed ROM was extended to treat the non-linearity induced by multi-physics modeling.
-At this point, we must emphysize that the method used here, i.e; POD Galerkin projection has been used in previous works to approximate the diffusion equation \cite{} for different problems and codes where it showed promising results.
-Moreover, the  Discrete Empirical Interpolation Method, DEIM, has been used in conjunction with the POD-Galerkin projection to approximate non-linear fields such as the temperature and the flow fields  ....
-\cite{}.
+In this study, the developed ROM was extended to treat the non-linearity induced by multi-physics modeling, using the matrix version of the  Discrete Empirical Interpolation Method (DEIM).
+To this point, we must emphasize that the method used here, i.e; POD Galerkin projection has been used in previous works to approximate the diffusion equation \cite{sartori2014comparison, sartori2014reduced} for other problems using different codes where it showed promising results.
+Moreover, DEIM has been used in conjunction with the POD-Galerkin projection to approximate non-linear fields such as the temperature and the velocity field \cite{german2019application, german2022gen}.
 Here, we are presenting another variant of the DEIM algorithm, known as the matrix version of DEIM, i,e; MDEIM, in order to improve the computational efficiency of the developed ROM.
-The primary purpose of using the MDEIM is to obtain an offline-online decomposition of the ROM to avoid repetitive projection of the problem operator at each iteration within the time step.
+The primary purpose of using the MDEIM is to obtain an offline-online decomposition of the ROM to avoid repetitive projection of the problem operator at each iteration within the time step, in cases that an affine decomposition of the operator is not readily obtainable.
 The offline stage occurs only once and comprises the expensive step of the ROM.
@@
 The quantities of interest were the assembly power at the peak and the maximum core temperature, i.e., the end-of-transient temperature.
-Note that the time to peak is different from sample to sample.
+Note that the time to peak is different from sample to sample, with the relative difference between the FOM peak power at the parameter vary between 0.1 to 1\%.
 Shown in Fig.~ \ref{fig:peak power mean error}, the sample mean of the assembly power error, at the peak, where the mean core maximum temperature error is shown in Fig.~\ref{fig:T mean error}.
